---
title: "1000-wa"
output: html_document
date: "2024-05-07"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(tidyverse)
library(raster)
library(ozmaps)
library(ggrepel)
```



Al Harry notes:
The fish from Cone Bay are mostly the (presumed) escapees based on their high density in areas adjacent to sea pens. Morphologically they look a little different and their size at sex change seems to be much smaller than elsewhere. I’ve heard a few theories as to why, but nobody has given me a definitive answer yet!


```{r}
d<-read_csv("~/Dropbox/Australian-fishes/wa-barra/240506-barramundi-mac-edit.csv")
# Some NA individuals bugger up this. I suppose replace missing with mean
# https://stackoverflow.com/questions/9322773/how-to-replace-na-with-mean-by-group-subset
impute.mean <- function(x) replace(x, is.na(x), mean(x, na.rm = TRUE))

dg<-d %>% filter(gene==TRUE) %>% group_by(site_1, site_2) %>% 
      mutate(
        Latitude = impute.mean(lat),
        Longitude = impute.mean(lon)  
    ) %>%
  summarize(Latitude=mean(Latitude), Longitude=mean(Longitude), Count=n()) %>%
  mutate(`Sample Size`=ifelse(Count > 100, 100, Count))

dg  %>% arrange(Latitude)

site2<-dg %>% group_by(site_2) %>% summarize(Latitude=mean(Latitude), Longitude=mean(Longitude), `Total Samples`=sum(Count))
```


## Get WA
```{r}
oz <- ozmap_data("states")
ggplot(oz) +
  geom_sf()
```

```{r}
# here eric implements something and I copy it
tidy_subset <- function(x, longlat) {
  x@data$id <- rownames(x@data)
  x.f <- broom::tidy(x) %>%
    dplyr::left_join(., x@data, by = "id") %>%
    dplyr::tbl_df() %>%
    filter(long > longlat[1],
           long < longlat[2],
           lat > longlat[3],
           lat < longlat[4])
}

```

```{r}
domain <- c(min(dg$Longitude)-9, max(dg$Longitude)+5, min(dg$Latitude)-6, max(dg$Latitude)+2)
```


```{r, eval=FALSE}
nat.earth<-stack("~/github/fish-lake/data/earth/NE2_HR_LC_SR_W_DR/NE2_HR_LC_SR_W_DR.tif")

nat.crop <- crop(nat.earth, y=extent(domain))

rast.table <- data.frame(xyFromCell(nat.crop, 1:ncell(nat.crop)),
                         getValues(nat.crop/255))


rast.table$rgb <- with(rast.table, rgb(NE2_HR_LC_SR_W_DR_1,
                                       NE2_HR_LC_SR_W_DR_2,
                                       NE2_HR_LC_SR_W_DR_3,
                                       1))

save(rast.table, file="data/earth/rast.rda")
```

```{r}
load("data/earth/rast.rda")
ggplot() +
  geom_raster(data = rast.table, mapping = aes(x = x, y = y), fill = rast.table$rgb, interpolate = TRUE)  +
  geom_sf(data=oz, fill=NA) +
  geom_jitter(data=dg, aes(x=Longitude, y=Latitude, size=`Sample Size`, fill=`Sample Size`), pch=21, alpha=0.75) +
  coord_sf(xlim = c(domain[1]+1,domain[2]-1), ylim=c(domain[3]+1, domain[4]-1)) +
  ylab("Latitude\n") +
  xlab("\nLongitude") +
  theme_bw() +
  theme(panel.grid=element_blank()) +
  scale_fill_viridis_c(option="magma")

ggsave("outputs/1000/samples-052024.jpeg")
```



## Pilbara Rivers and Kimberley Locs

```{r}
pbr<-read_tsv("meta/pilbara-rivers.tsv")
locs<-read_tsv("meta/kimberley-locs.tsv")
locs
```


```{r}
ggplot() +
  geom_raster(data = rast.table, mapping = aes(x = x, y = y), fill = rast.table$rgb, interpolate = TRUE)  +
  geom_sf(data=oz, fill=NA) +
  geom_jitter(data=dg, aes(x=Longitude, y=Latitude, size=`Sample Size`, fill=`Sample Size`), pch=21, alpha=0.75) +
  geom_point(data=pbr, aes(x=Longitude, y=Latitude), pch=23, fill="red", alpha=0.75, size=4) +
  geom_point(data=locs, aes(x=Longitude, y=Latitude), pch=22, fill="blue", alpha=0.75, size=4) +
  geom_text_repel(data=pbr, aes(x=Longitude, y=Latitude, label=River)) +
  geom_text_repel(data=locs, aes(x=Longitude, y=Latitude, label=Location)) +
 # geom_text_repel(data=site2, aes(x=Longitude, y=Latitude, label=site_2), max.overlaps = Inf) +
  coord_sf(xlim = c(domain[1]+1,domain[2]-1), ylim=c(domain[3]+1, domain[4]-1)) +
  ylab("Latitude\n") +
  xlab("\nLongitude") +
  theme_bw() +
  theme(panel.grid=element_blank()) +
  scale_fill_viridis_c(option="magma")

ggsave("outputs/1000/samples-052024-pbr.jpeg")
ggsave("outputs/1000/samples-052024-pbr.pdf")

```



# Rough estimate of sampling

```{r}
dg %>% arrange(-Latitude)
```

Cone Bay should sample all. N=18+82

Others, let's downsample to 30.    


```{r}
conebay<-dg %>% filter(site_2=="Cone Bay") %>% mutate(ToSequence=Count) %>% select(-Count, -`Sample Size`)
others<-dg %>% filter(site_2!="Cone Bay")  %>% mutate(ToSequence=ifelse(Count > 30, 30, Count)) %>% select(-Count, -`Sample Size`)
toseq<-others %>% bind_rows(conebay)
toseq %>% ungroup() %>% summarize(Sum=sum(ToSequence))
```

860 fish