---
title: "101-all-chroms"
output: html_document
date: "2023-06-12"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(tidyverse)
library(ggrepel)
library(ggpubr)
library(ape)
``` 

```{r}
m2<-read_csv("meta/58.csv")
m2$Region<-factor(m2$Region, levels=c("Northern Territory","Queensland","Papua New Guinea",
                                              "Indonesia","Philippines","Vietnam","Cambodia","Thailand",
                                              "India Eastern Coast","India Western Coast"))
m2 <-m2 %>% mutate(Lineage=ifelse(Region %in% c("Northern Territory","Queensland","Papua New Guinea"),"AUS+PNG",
                                                ifelse(Region %in% c("India Eastern Coast","India Western Coast"),"IND","SEA")))
m2 %>% group_by(Region) %>% summarize(Count=n(), Cov=mean(Coverage))
```

## 58 sample, all chroms

Takes about 1/2 hour for chrom one, can do in parallel, but, doing this today:     

```{sh, eval=FALSE}
srun -p high -t 16:00:00 --mem=32G --nodes=1 $HOME/angsd/angsd -P 12  \
-bam bamlists/58.bamlist -rf genome/lates-lgs.txt \
-ref  genome/GCF_001640805.2_TLL_Latcal_v3_genomic.fna \
-minInd 53 -minMapQ 10 -minQ 20 -GL 2 -doGLF 2 \
-doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 \
-doIBS 1 -doCounts 1 -doCov 1 -makeMatrix 1 -minMaf 0.05 \
-out outputs/101/58-ibs-90 > outputs/101/58-ibs-90.out 2> outputs/101/58-ibs-90.err &

#ngs admix    
srun -p high -t 04:00:00 --mem=32G --nodes=1 $HOME/angsd/misc/NGSadmix -P 12 -likes outputs/101/58-ibs-90.beagle.gz -K 2 -o outputs/101/58-K2 &
srun -p high -t 05:00:00 --mem=32G --nodes=1 $HOME/angsd/misc/NGSadmix -P 12 -likes outputs/101/58-ibs-90.beagle.gz -K 3 -o outputs/101/58-K3 &
srun -p high -t 06:00:00 --mem=32G --nodes=1 $HOME/angsd/misc/NGSadmix -P 12 -likes outputs/101/58-ibs-90.beagle.gz -K 4 -o outputs/101/58-K4 &
srun -p high -t 07:00:00 --mem=32G --nodes=1 $HOME/angsd/misc/NGSadmix -P 12 -likes outputs/101/58-ibs-90.beagle.gz -K 5 -o outputs/101/58-K5 &

```

	-> Number of sites retained after filtering: 7437516     

     
### Visualize covMat     


```{r}
meta<-m2
m <- as.matrix(read.table("outputs/101/58-ibs-90.covMat"))
eig <- eigen(m)
var<-eig$values/sum(eig$values)
cumvar<-cumsum(eig$values)/sum(eig$values)

head(var)
head(cumvar)
```


```{r}
covs<-eig$vectors[,1:3] %>% as_tibble() %>% bind_cols(meta)

text12<-covs %>% select(Run, Region, V1, V2) %>%
  group_by(Region) %>% summarize(Count=n(), x=mean(V1), y=mean(V2))

ggplot(covs) +
  geom_point(aes(x=V1, y=V2, fill=Region), pch=21, alpha=0.75) +
  geom_text_repel(data=text12, aes(x=x, y=y, label=Region), max.overlaps = Inf) +
  xlab(paste("PC1", " ", round((100*var[1]),2), "%", sep = "")) +
  ylab(paste("PC2", " ", round((100*var[2]),2), "%", sep = "")) +
  theme_bw() +
  theme(panel.grid=element_blank()) +
  scale_fill_viridis_d(option="turbo") +
  ggtitle("Genome-Wide PCA of L. calcarifer WGS Data") +
  theme(plot.title = element_text(hjust=0.5, face="bold"))

ggsave("outputs/101/lates-c-genome-wide-pca-12.jpeg")
```
For figure  

```{r}
covs<-eig$vectors[,1:3] %>% as_tibble() %>% bind_cols(meta) 

text12<-covs %>% select(Run, Region, V1, V2) %>%
  group_by(Region) %>% summarize(Count=n(), x=mean(V1), y=mean(V2))

pc12<-ggplot(covs) +
  geom_point(aes(x=V1, y=V2, fill=Region, shape=Lineage), size=2, alpha=0.75) +
#  geom_text_repel(data=text12, aes(x=x, y=y, label=Region), max.overlaps = Inf) +
  xlab(paste("PC1", " ", round((100*var[1]),2), "%", sep = "")) +
  ylab(paste("PC2", " ", round((100*var[2]),2), "%", sep = "")) +
  theme_bw() +
  theme(panel.grid=element_blank()) +
  scale_fill_viridis_d(option="turbo") +
  ggtitle("A") +
  theme(plot.title = element_text(size=14, face="bold")) +
  scale_shape_manual(values=c(21,23,24)) +
  guides(fill = guide_legend(override.aes = list(pch = 22))) +
  theme(legend.position = "none")

pc12
```
```{r}
text13<-covs  %>% select(Run, Region, V1, V3) %>%
  group_by(Region) %>% summarize(Count=n(), x=mean(V1), y=mean(V3))

pc13<-ggplot(covs) +
  geom_point(aes(x=V1, y=V3, fill=Region, shape=Lineage), size=2, alpha=0.75) +
 # geom_text_repel(data=text13, aes(x=x, y=y, label=Region), max.overlaps = Inf) +
  xlab(paste("PC1", " ", round((100*var[1]),2), "%", sep = "")) +
  ylab(paste("PC3", " ", round((100*var[3]),2), "%", sep = "")) +
  theme_bw() +
  theme(panel.grid = element_blank()) +
  scale_fill_viridis_d(option="turbo") +
  ggtitle("B") +
  theme(plot.title = element_text(size=14, face="bold")) +
  scale_shape_manual(values=c(21,23,24)) +
  guides(fill = guide_legend(override.aes = list(pch = 22))) 

pc13
```

```{r}
ggarrange(pc12,pc13,ncol=2,widths=c(1,1.45))
ggsave("outputs/101/combined-wgspcs.pdf", width=9, height=4)

```

Making 
### Visualize admixture plots

```{r, echo=FALSE}
PlotAdmix<- function(file, meta) {

q<-read_delim(file, delim=" ", col_names=FALSE)
#Make generic colnames

nums<-1:length(colnames(q))
mynames<-paste0("Q",nums)

qs<-length(colnames(q))-1

colnames(q)<-mynames

#Last col empty
q<-q[1:length(colnames(q))-1]

#Bind met and arrange 
df<-bind_cols(q, meta) %>% arrange(Region) %>% mutate(Index=1:n())
df$Region<-factor(df$Region, levels=unique(df$Region))

rdf<-df %>% dplyr::select(Region, Index, colnames(q) ) %>% gather(key=Ancestry, value=Q, 3:(3+length(colnames(q))-1))

#Make names for structure-like plot
labels<-rdf %>% group_by(Region) %>% mutate(Start=min(Index), Stop=max(Index)) %>% 
  select(Region,Start,Stop) %>% unique() %>% 
  mutate(Position=round((Start+Stop)/2)) %>% ungroup() %>% unique()

#Plot
ggplot(rdf) + 
  geom_col(aes(x=Index,y=Q, fill=Ancestry), color="NA", size = 0, width = 1) +
  geom_segment(data=labels, x = labels$Start - 0.5, y=0, xend = labels$Start-0.5, yend=1, alpha=0.9, size=0.25) +
  geom_segment(data=labels, x = labels$Stop[length(labels$Stop)]  + 0.5, y=0, 
               xend= labels$Stop[length(labels$Stop)] + 0.5, yend=1,  alpha=0.9,
               size=0.25) +
  geom_segment(x=0+0.5, xend= labels$Stop[length(labels$Stop)]+0.5, y=1, yend=1, alpha=0.9, size=0.25) +
  geom_segment(x=0+0.5, xend= labels$Stop[length(labels$Stop)]+0.5, y=0, yend=0, alpha=0.9, size=0.25) +
  ylim(-0.1,1.01) +
  xlim(-0.1, labels$Stop[length(labels$Stop)]+1) +
  theme(panel.background = element_blank()) +
  xlab("") +
  theme(legend.position = "") +
  scale_x_continuous(breaks=labels$Position, labels=labels$Region) +
  theme(axis.text.x = element_text(angle=45, hjust=1)) +
  scale_fill_viridis_d(option="magma")

}
```

```{r}
PlotAdmix("outputs/101/58-K2.qopt", m2)
```

```{r}
PlotAdmix("outputs/101/58-K3.qopt", m2)
```

### Dropping India

These guys are so far out there, let's drop and use one chrom.    

```{r}
m47<-m2 %>% filter(!Region %in% c("India Eastern Coast","India Western Coast"))
write_tsv(m47 %>% select(Path), col_names = FALSE, "bamlists/47.bamlist")
```

```{sh, eval=FALSE}
srun -p high -t 1:00:00 --mem=32G --nodes=1 $HOME/angsd/angsd -P 12  \
-bam bamlists/47.bamlist -r NC_066833.1 \
-ref  genome/GCF_001640805.2_TLL_Latcal_v3_genomic.fna \
-minInd 42 -minMapQ 10 -minQ 20 -GL 2 -doGLF 2 \
-doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 \
-doIBS 1 -doCounts 1 -doCov 1 -makeMatrix 1 -minMaf 0.05 \
-out outputs/101/47-ibs-90 > outputs/101/47-ibs-90.out 2> outputs/101/47-ibs-90.err &

srun -p high -t 01:00:00 --mem=32G --nodes=1 $HOME/angsd/misc/NGSadmix -P 12 -likes outputs/101/47-ibs-90.beagle.gz -K 2 -o outputs/101/47-K2 &
srun -p high -t 01:00:00 --mem=32G --nodes=1 $HOME/angsd/misc/NGSadmix -P 12 -likes outputs/101/47-ibs-90.beagle.gz -K 3 -o outputs/101/47-K3 &
srun -p high -t 01:00:00 --mem=32G --nodes=1 $HOME/angsd/misc/NGSadmix -P 12 -likes outputs/101/47-ibs-90.beagle.gz -K 4 -o outputs/101/47-K4 &
srun -p high -t 01:00:00 --mem=32G --nodes=1 $HOME/angsd/misc/NGSadmix -P 12 -likes outputs/101/47-ibs-90.beagle.gz -K 5 -o outputs/101/47-K5 &

# High maf
srun -p high -t 1:00:00 --mem=32G --nodes=1 $HOME/angsd/angsd -P 12  \
-bam bamlists/47.bamlist -r NC_066833.1 \
-ref  genome/GCF_001640805.2_TLL_Latcal_v3_genomic.fna \
-minInd 42 -minMapQ 10 -minQ 20 -GL 2 -doGLF 2 \
-doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 \
-doIBS 1 -doCounts 1 -doCov 1 -makeMatrix 1 -minMaf 0.20 \
-out outputs/101/47-ibs-90-2 > outputs/101/47-ibs-90-2.out 2> outputs/101/47-ibs-90-2.err &


srun -p high -t 01:00:00 --mem=32G --nodes=1 $HOME/angsd/misc/NGSadmix -P 12 -likes outputs/101/47-ibs-90-2.beagle.gz -K 2 -o outputs/101/47-K2-2 &
srun -p high -t 01:00:00 --mem=32G --nodes=1 $HOME/angsd/misc/NGSadmix -P 12 -likes outputs/101/47-ibs-90-2.beagle.gz -K 3 -o outputs/101/47-K3-2 &
srun -p high -t 01:00:00 --mem=32G --nodes=1 $HOME/angsd/misc/NGSadmix -P 12 -likes outputs/101/47-ibs-90-2.beagle.gz -K 4 -o outputs/101/47-K4-2 &
srun -p high -t 01:00:00 --mem=32G --nodes=1 $HOME/angsd/misc/NGSadmix -P 12 -likes outputs/101/47-ibs-90-2.beagle.gz -K 5 -o outputs/101/47-K5-2 &

```

	-> Number of sites retained after filtering: 231013 maf=0.05     
	-> Number of sites retained after filtering: 49319  maf=0.20     

```{r}
meta<-m47
m <- as.matrix(read.table("outputs/101/47-ibs-90-2.covMat"))
eig <- eigen(m)
var<-eig$values/sum(eig$values)
cumvar<-cumsum(eig$values)/sum(eig$values)

head(var)
head(cumvar)
```


```{r}
covs<-eig$vectors[,1:3] %>% as_tibble() %>% bind_cols(meta)

text12<-covs %>% select(Run, Region, V1, V2) %>%
  group_by(Region) %>% summarize(Count=n(), x=mean(V1), y=mean(V2))

ggplot(covs) +
  geom_point(aes(x=V1, y=V2, fill=Region), pch=21, alpha=0.75) +
  geom_text_repel(data=text12, aes(x=x, y=y, label=Region), max.overlaps = Inf) +
  xlab(paste("PC1", " ", round((100*var[1]),2), "%", sep = "")) +
  ylab(paste("PC2", " ", round((100*var[2]),2), "%", sep = "")) +
  theme_bw() +
  theme(panel.grid=element_blank()) +
  scale_fill_viridis_d(option="turbo") +
  ggtitle("Genome-Wide PCA of L. calcarifer WGS Data") +
  theme(plot.title = element_text(hjust=0.5, face="bold"))

ggsave("outputs/101/lates-c-genome-wide-pca-12-oz-png-asia-maf20.jpeg")
```
```{r}
ggplot(covs) +
  geom_point(aes(x=V1, y=V2, fill=Coverage), pch=21, alpha=0.75) +
  geom_text_repel(data=text12, aes(x=x, y=y, label=Region), max.overlaps = Inf) +
  xlab(paste("PC1", " ", round((100*var[1]),2), "%", sep = "")) +
  ylab(paste("PC2", " ", round((100*var[2]),2), "%", sep = "")) +
  theme_bw() +
  theme(panel.grid=element_blank()) +
  scale_fill_viridis_c () +
  ggtitle("Genome-Wide PCA of L. calcarifer WGS Data") +
  theme(plot.title = element_text(hjust=0.5, face="bold"))
```

```{r}
text13<-covs  %>% select(Run, Region, V1, V3) %>%
  group_by(Region) %>% summarize(Count=n(), x=mean(V1), y=mean(V3))

ggplot(covs) +
  geom_point(aes(x=V1, y=V3, fill=Region), pch=21, alpha=0.75) +
  geom_text_repel(data=text13, aes(x=x, y=y, label=Region), max.overlaps = Inf) +
  xlab(paste("PC1", " ", round((100*var[1]),2), "%", sep = "")) +
  ylab(paste("PC3", " ", round((100*var[3]),2), "%", sep = "")) +
  theme_bw() +
  theme(panel.grid = element_blank()) +
  scale_fill_viridis_d(option="turbo")
```



```{r}
PlotAdmix("outputs/101/47-K2-2.qopt", m47)
```


```{r}
PlotAdmix("outputs/101/47-K3-2.qopt", m47)
```

```{r}
PlotAdmix("outputs/101/47-K4-2.qopt", m47)
```

```{r}
PlotAdmix("outputs/101/47-K5-2.qopt", m47)
```
With GLs, no doIBS

```{sh, eval=FALSE}
srun -p high -t 1:00:00 --mem=32G --nodes=1 $HOME/angsd/angsd -P 12  \
-bam bamlists/47.bamlist -r NC_066833.1 \
-minInd 42 -GL 1 -ref genome/GCF_001640805.2_TLL_Latcal_v3_genomic.fna -minMaf 0.05 \
-doGLF 2 -doMajorMinor 1 -doMaf 2 -SNP_pval 1e-6 -minMapQ 10 -minQ 20 \
-out outputs/101/47-gl > outputs/101/47-gl.out 2> outputs/101/47-gl.err &

#srun -p high -t 1:00:00 python $HOME/pcangsd/pcangsd.py -beagle outputs/100/47-gl.beagle.gz -o outputs/100/47-gl -pca -threads 10

srun -p high -t 01:00:00 --mem=32G --nodes=1 $HOME/angsd/misc/NGSadmix -P 12 -likes outputs/101/47-gl.beagle.gz -K 2 -o outputs/101/47-gl-K2 &
srun -p high -t 01:00:00 --mem=32G --nodes=1 $HOME/angsd/misc/NGSadmix -P 12 -likes outputs/101/47-gl.beagle.gz -K 3 -o outputs/101/47-gl-K3 &
srun -p high -t 01:00:00 --mem=32G --nodes=1 $HOME/angsd/misc/NGSadmix -P 12 -likes outputs/101/47-gl.beagle.gz -K 4 -o outputs/101/47-gl-K4 &
srun -p high -t 01:00:00 --mem=32G --nodes=1 $HOME/angsd/misc/NGSadmix -P 12 -likes outputs/101/47-gl.beagle.gz -K 5 -o outputs/101/47-gl-K5 &


```
 166824 sites    

```{r}
PlotAdmix("outputs/101/47-gl-K2.qopt", m47)
```

## Tree version
```{r}
name <- "outputs/100/"
m <- as.matrix(read.table(name))

#heat map
pdf("outputs/101/clustering.pdf", width=8, height=8)
heatmap(m, labRow = m2$Region, labCol = m2$Region, cexRow = 0.5, cexCol = 0.5)
dev.off()
```

```{r}
library(gplots)
library(pheatmap)
```

```{r}
colnames(m)<-m2$Region
rownames(m)<-m2$Run
annot_rows = data.frame(
                Lineage = m2$Lineage, 
                Region = m2$Region,
        row.names = m2$Run
                )
pheatmap(m, clustering_distance_cols="manhattan", clustering_distance_rows="manhattan", annotation_row = annot_rows,
         show_rownames = FALSE, legend = F)
```

```{r}
plot(hclust(dist(m), "ave"))
```
