---
title: "101-mtDNA"
output: html_document
date: "2023-06-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(tidyverse)
```

Obtained bold data for Lates

grep -A 1 COI-5P bold.fas | perl -pe 's/--\n//g' > bold-COI.fas 
./shortenNamesBold.pl bold-COI.fas  > bold-renamed.fas
 mafft bold-renamed.fas > bold-renamed.afas     
682 seqs

Very divergent "Lates calcarifer", it is a mess.

Looking at data from Vi et al., Ward et al. and
(base) Macs-MacBook-Pro-2:mtdna mac$ grep uwisara bold_data.txt | cut -f 1 | while read line; do selectSeqs.pl -m $line bold.fas >> l-uwisara.fas; done;

no lakdiva data

(base) Macs-MacBook-Pro-2:mtdna mac$ cat ward-vi-renamed.fas l-uwisara.fas > ward-vi-uwisara.fas
(base) Macs-MacBook-Pro-2:mtdna mac$ mafft ward-vi-uwisara.fas > ward-vi-uwisara.afas
 iqtree -s ward-vi-uwisara.afas -bb 1000 -m GTR+G


darwiniensis, Lates Macleay [W.] 1878:345 [Proceedings of the Linnean Society of New South Wales v. 2 (pt 4); ref. 17573] Port Darwin, Northern Territory, Australia. Holotype (unique): AMS I.16319-001 [ex MAMU F442(b)]. Type catalog: Stanbury 1969:206 [ref. 19518]. •Synonym of Lates calcarifer (Bloch 1790) -- (Paxton et al. 1989:482 [ref. 12442], Larson & Williams 1997:354 [ref. 23967], Allen et al. 2006:967 [ref. 29081], Pethiyagoda & Gill 2012:11 [ref. 31984], Larson et al. 2013:93 [ref. 32988], Kottelat 2013:323 [ref. 32989]). Current status: Synonym of Lates calcarifer (Bloch 1790). Latidae. Habitat: freshwater, brackish, marine.


Can use mitogenomes for basic time calibrated tree....
EU189379.1 WA
DQ108026.1 QLD
KJ573921.1 Indonesia
KJ573937.1 Singapore
KJ573895.1 Andaman and Nicobar
KJ573901.1 Bangladesh


ANGBF15780-19	Lates japonicus
ISZA082-21	Lates microlepis
ANGBF15782-19	Lates niloticus
JQ841102.1 Centropomus undecimalis
KP112195.1 Channa maculata
KX245097.1 Nandus nandus


Centropomidae	48.6	1.0	1.0	Otero 2004	Centropomus undecimalis and Lates calcarifer
Channoidea	48	1.71	1.14	Santini et al. 2009	Channa maculata and Nandus nebulosus

iqtree -s for-mtdna-time.afas  -bb 1000 -m GTR+G --redo

Set up for MB

seqConverter.pl -dfor-mtdna-time.afas -on


Li et al. 16S

L04 100% identical to D32 Australia: Darwin Harbour, Darwin
L05 96.38% identical to D32, similar to Malaysian seq.
L07 99.85% similar to D32, see DQ010541