---
title: "106-separate-clusters"
output: html_document
date: "2023-07-28"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library("tidyverse")
library("viridis")
library("vcfR")
library("adegenet")
library("poppr")
library("ggrepel")
library("ggpubr")
```


Basic idea, set up a set of diagnostic loci to separate:

(1) Western Seabass from Eastern Seabass-> Note, nothing to test against here with WGS.
(2) Use RADseq data to come up with a set of 'diagnostic' loci to separate OZ+PNG from Everybody Else. Check against WGS data.
(3) Separate Oz+PNG with called loci (e.g. 105-existing-snps.Rmd).  Test against WGS data, calculate allelic frequencies.

Note to self, should think about multi-snp haplotypes to do this and call variants with something indel aware. Maybe FreeBayes      

Starting with (3), 102 I called snps:

```{sh, eval=FALSE}
srun -t 36:00:00 -p high --mem=32G --nodes=1 --ntasks-per-node=1 --cpus-per-task=12 $HOME/angsd/angsd -nthreads 24 \
-minInd 117 \
-bam bamlists/130.bamlist -ref genome/GCF_001640805.2_TLL_Latcal_v3_genomic.fna \
-rf genome/lates-lgs.txt -out outputs/102/snps-wang  \
-minMaf 0.05 -minMapQ 20 -minQ 20 -GL 1 -doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 \
-doGeno 2 -doPost 1 -postCutoff 0.9 -doPlink 2  > outputs/102/snps-wang.out 2> outputs/102/snps-wang.err &
```

retrieve meta.    


```{r}
meta<-read_csv("meta/wang.csv")
write_tsv(meta %>% select(Run), col_names=FALSE, file="bamlists/130-sample-names.txt")
write_tsv(meta %>% filter(Pop %in% c("AUW","AUE","PNG")) %>% select(Run), col_names=FALSE, file="bamlists/oz-png-names.txt")
ozpng<-meta %>% filter(Pop %in% c("AUW","AUE","PNG"))
meta
```

```{r}
meta$Pop<-factor(meta$Pop, levels=c("AUW","AUE","PNG","INA","MAL","THA"))
meta %>% group_by(Pop, Lat_Lon) %>% summarize(Count=n(), Reads=mean(Filtered))
```

Have .geno file and plink-formatted file. making .vcf 99040 snps in plink file.  Looks to have run through all chroms

```{sh, eval=FALSE}

plink --tped snps-wang.tped --tfam snps-wang.tfam  --out plink-binary --recode --allow-extra-chr --noweb
plink --ped plink-binary.ped --map plink-binary.map --recode vcf --allow-extra-chr -out plink
bgzip plink.vcf 
tabix plink.vcf.gz
bcftools view plink.vcf.gz --regions NC_066833.1  > chrom01.vcf

bcftools +prune -l 0.20 -w 10000 plink.vcf.gz > plink-pruned.vcf.gz
```

    

```{r, eval=FALSE}
vcf<-read.vcfR(file="outputs/106/plink-pruned.vcf")
genind<-vcfR2genind(vcf)
genind@pop<-factor(meta$Pop, levels=c("AUW","AUE","PNG","INA","MAL","THA"))
save(genind, file="outputs/102/plink-genind.rda")
```

```{r, eval=FALSE}
vcf<-read.vcfR(file="outputs/106/chrom01.vcf")
genind<-vcfR2genind(vcf)
genind@pop<-factor(meta$Pop, levels=c("AUW","AUE","PNG","INA","MAL","THA"))
save(genind, file="outputs/102/chrom01-genind.rda")
```
```{r}
#load("outputs/102/chrom01-genind.rda")
load("outputs/102/plink-genind.rda")
```

Looking at chrom01, then all chroms
```{r}
gen<-genind
X <- tab(gen, NA.method="mean")

pca1 <- dudi.pca(X,scannf=FALSE,scale=FALSE,nf=3)
plot(pca1$li)

```

Plotting again
```{r}
df<-pca1$li
df<-df %>% bind_cols(meta)
eig<-pca1$eig/sum(pca1$eig)*100
df$Population<-factor(df$Pop, levels=c("AUW","AUE","PNG","INA","MAL","THA"))

eig
```

```{r}
pc12<-ggplot(df) + 
  geom_point(aes(x=Axis1, y=Axis2, fill=Population), pch=21, alpha=0.75, cex=2) +
  theme_bw() +
  xlab(paste0("PC1 ",round(eig[1],2), "%")) +
  ylab(paste0("PC2 ",round(eig[2],2), "%")) +
  theme(panel.grid = element_blank()) +
  scale_fill_viridis_d(option="H")
pc12
ggsave("outputs/106/pcs12.jpeg")
```

```{r}
pc13<-ggplot(df) + 
  geom_point(aes(x=Axis1, y=Axis3, fill=Population), pch=21, alpha=0.75, cex=2) +
  theme_bw() +
  xlab(paste0("PC1 ",round(eig[1],2), "%")) +
  ylab(paste0("PC3 ",round(eig[3],2), "%")) +
  theme(panel.grid = element_blank()) +
  scale_fill_viridis_d(option="H")
pc13
```

```{r}
eigs<-eig %>% as_tibble() %>% head(n=5) %>% rename(Variance=value) %>%
  mutate(PC=1:n())
e<-ggplot(eigs, aes(x=PC, y=Variance)) +
  geom_bar(stat="identity") +
  theme_bw() +
  theme(panel.grid=element_blank()) +
  scale_x_continuous(breaks=c(1,2,3,4,5)) +
  ylab("% Variance\n") +
  xlab("\nPC") + 
  theme(axis.title=element_text(size=14, face="bold")) +
  theme(axis.text=element_text(size=12))
e
```

```{r}
ggarrange(pc12+theme(legend.position = "") + ggtitle("A") + theme(plot.title=element_text(size=14, face="bold")),
          pc13+ggtitle("B") + theme(plot.title=element_text(size=14, face="bold")), widths=c(1,1.3))
ggsave("outputs/106/combined-radseqpcs.pdf", width=8, height=3.75)
```

Looks sane. Filtering to AUE, AUW, PNG and maf of 0.1 

```{sh, eval=FALSE}
bcftools reheader --samples  bamlists/130-sample-names.txt  -o outputs/106/renamed.vcf.gz outputs/106/plink.vcf.gz
bcftools view -S bamlists/oz-png-names.txt outputs/106/renamed.vcf.gz | bcftools view -q 0.10:minor  > outputs/106/oz-png-maf01.vcf


bcftools reheader --samples  bamlists/130-sample-names.txt  -o outputs/106/renamed-pruned.vcf.gz outputs/106/plink-pruned.vcf.gz
bcftools view -S bamlists/oz-png-names.txt outputs/106/renamed-pruned.vcf.gz | bcftools view -q 0.10:minor  > outputs/106/oz-png-pruned-maf01.vcf


```


19,200 variants   

```{r, eval=FALSE}
vcf<-read.vcfR(file="outputs/106/oz-png-maf01.vcf")
goz<-vcfR2genind(vcf)
goz@pop<-factor(ozpng$Pop, levels=c("AUW","AUE","PNG"))
save(goz, file="outputs/106/ozpng-genind.rda")
```

```{r}
load("outputs/106/ozpng-genind.rda")
```

```{r}
cols<-viridis(6, option="H")
```

```{r}
gen<-goz
X <- tab(gen, NA.method="mean")
pca1 <- dudi.pca(X,scannf=FALSE,scale=FALSE,nf=3)

df<-pca1$li
df<-df %>% bind_cols(ozpng)
eig<-pca1$eig/sum(pca1$eig)*100

df$Population<-factor(df$Pop, levels=c("AUW","AUE","PNG"))
totpc<-ggplot(df) + 
  geom_point(aes(x=Axis1, y=Axis2, fill=Population), pch=21, cex=2, alpha=0.75) +
  theme_bw() +
  xlab(paste0("PC1 ",round(eig[1],2), "%")) +
  ylab(paste0("PC2 ",round(eig[2],2), "%")) +
  theme(panel.grid = element_blank()) +
  scale_fill_manual(values=cols[1:3])

totpc
ggsave("outputs/106/ozpng-pcs12.jpeg")

```

Looks like expected, including hints at structure in AUW.     


What values separate PNG from Oz?   

```{r}
popvector2<-gsub("AUE","AUS",gen@pop)
popvector2<-gsub("AUW","AUS", popvector2)

d2<-gen
d2@pop<-as.factor(popvector2)
```

Looks to be the same as published snps here with n.pca
```{r}
dapc<-dapc(d2, d2@pop, n.pca = 45, n.da = 1)
```

```{r}
pdf("outputs/106/discriminant-function.pdf")
scatter(dapc)
dev.off()
scatter(dapc)
```

Loadings      
```{r}
loads<-dapc$var.contr
ldf<-as_tibble(loads)
ldf$SNP<-rownames(loads)


tops<-ldf %>% arrange(-LD1) %>% top_n(40, LD1)
tops$locus<-gsub(".\\d$","",tops$SNP)
tops$Chrom<-gsub("_\\d+$","",tops$locus)
tops$Site<-gsub("NC_\\d+_\\d_","",tops$locus)
tops

write_csv(tops, file="Supplemental/Supplemental Table SX AUS-NG loci.csv")
```
```{r}
ggplot(ldf %>% arrange(-LD1) %>% mutate(Position=1:n())) +
  geom_point(aes(x=Position, y=LD1)) +
  geom_vline(xintercept = 40)+
  xlim(0,100)
```

Pull out top snps and plot those as a PCA.    

```{r}
d3<-d2[loc=unique(tops$locus),]

loci<-d3@tab %>% as_tibble()
loci$Ind<-rownames(d3@tab)
loci$Pop<-d3@pop
loci<-relocate(loci, Pop, Ind)
loci <-arrange(loci,Pop)
```


```{r}
x<-tab(d3,freq=TRUE,NA.method="mean")
pca<-dudi.pca(x,center=TRUE,scale=FALSE, scannf = FALSE, nf =3)

pcadf<-pca$li %>% as_tibble()
pcadf$Pop<-gen@pop
eig<- pca$eig
sum<-(eig/(sum(eig)))*100

pcadf$Population<-pcadf$Pop
pca<-ggplot(pcadf) +
  geom_point(aes(x=Axis1, y=Axis2, fill=Population), pch=21, cex=2, alpha=0.75)+
  theme_bw() +
  theme(panel.grid = element_blank()) +
  xlab(paste0("PC1 ", round(sum[1],2),"%")) +
  ylab(paste0("PC2 ", round(sum[2],2),"%")) +
  ggtitle("C") +
  theme(plot.title = element_text(size=14, face="bold")) +
  scale_fill_manual(values=cols[1:3])


pca

ggsave("outputs/106/top-loci-pca.pdf")
```



Looks like we can place all these clusters with the SNPS

```{r}
tops2<-tops %>% select(locus, Chrom, Site) %>% group_by(Chrom) %>% summarize(Count=n())
unique(tops2$Chrom)
```

20 snps on 13 chroms
30 snps on 14 chroms
Distribution      
```{r}
ggplot(tops2) + 
  geom_bar(aes(x=Chrom, y=Count), stat='identity') +
  theme_bw() +
  theme(panel.grid = element_blank()) +
  theme(axis.text.x=element_text(angle=45, vjust=1, hjust=1))

```


Check to see if any are spatially close

```{r}
locs<-tops
locs$Site<-as.numeric(locs$Site)
locs %>% select(locus,Chrom,Site) %>% unique() %>% group_by(Chrom) %>% arrange(Chrom, -Site) %>% mutate(Lag=lag(Site)) %>%
  mutate(Diff=abs(Site-Lag)) %>% na.omit()
```

Far apart.


Signal from these loci     

```{r,eval=FALSE}
kstat<-find.clusters(d3, n.pca=20) # n.clust=3)
save(kstat, file="outputs/106/kstat.rda")
```
```{r}
load("outputs/106/kstat.rda")
bic<-kstat$Kstat %>% as_tibble() %>% rename(BIC=value) %>% mutate(K=1:n())
bicplot<-ggplot(bic, aes(x=K, y=BIC)) +
  geom_line() +
  geom_point() +
  theme_bw() +
  theme(panel.grid = element_blank()) +
  #ggtitle("BIC Scores from K Means Clustering of Diversity Loci") +
  ylab("BIC\n") +
  xlab("\nK") +
 # theme(plot.title=element_text(hjust=0.5, size=14, face="bold")) +
  theme(axis.title=element_text(size=12)) +
  scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8,9,10), labels=c("1","2","3","4","5","6","7","8","9","10")) +
  theme(axis.title = element_text(size=12, face="bold")) +
  theme(axis.text = element_text(size=10)) +
  ggtitle("C") +
  theme(plot.title = element_text(size=14, face="bold")) 

bicplot

ggsave("outputs/106/bic-plot.pdf")
```



Now, let's look assignments    

```{r}
dft<-as.data.frame(table(pop(gen), kstat$grp)) %>% as_tibble() %>%
  rename(Location=Var1, Assignment=Var2, Number=Freq)

assign<-ggplot(dft, aes(y=Location, x=Assignment)) +
  theme(axis.title.y = element_text(size = rel(2))) +
  theme(axis.title.x = element_text(size = rel(2))) +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(x="\nInferred Group", y="Sampling Location\n") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  theme(text=element_text(family='Times')) +
  theme(axis.text.x= element_text(face="bold", size=10, vjust = 0.5)) +
  theme(axis.text.y= element_text(face="bold", size=10)) +
  geom_point(aes(x=Assignment, y=Location, size=Number)) +
  geom_text(aes(x=Assignment, y=Location, label=Number), color="white", size=3) +
  scale_size_area(limits=c(1,25), breaks=c(0,5,10,15,20,25))

assign
```


100% assignment probs!!!    

Write loci for a Table to get allele freqs from each pop and to check against WGS data.     

```{r}
t1<-tops %>% select(Chrom,Site) %>% unique()
t1$Chrom<-gsub("_1$",".1",t1$Chrom)
t1<- t1 %>% arrange(Chrom)
t1
write_tsv(t1,"meta/top-site-list.tsv", col_names = FALSE)
```

`(base) Macs-MacBook-Pro-2:meta mac$ angsd sites index top-site-list.tsv `   

```{r}
d4<-d3
d4@pop<-gen@pop

poppr(d4)
```

(d4 to look at three pops)
```{r}
d5<-genind2genpop(d4)
```
```{r}
adf<-d5@tab %>% as_tibble()
adf$Pop<-rownames(d5@tab)

adf<-adf %>% relocate(Pop) %>% pivot_longer(2:41)
adf$Chrom<-gsub("_\\d+\\.\\d$","",adf$name)
adf$Chrom<-gsub("_1$",".1",adf$Chrom)
adf$Site<-gsub("NC_\\d+_1_","",adf$name)
adf$Site<-gsub("\\.\\d$","",adf$Site)
adf$Locus<-gsub("NC_\\d+_1_","",adf$name)
adf$Locus<-gsub("^\\d+\\.","",adf$Locus)
adf
```

```{r}
adf2<-adf %>% group_by(Pop,Chrom,Site) %>% mutate(TotalAlleles=sum(value)) %>%
  ungroup() %>% group_by(Pop, Chrom, Site, Locus) %>% mutate(AF=value/TotalAlleles)

#dropping total allleles column that tells us a bit about missingness
adf3<-adf2 %>% select(Pop, Chrom, Site, Locus, TotalAlleles, AF) %>% filter(Locus==0) %>% ungroup() %>%
  select(-Locus, -TotalAlleles) %>% pivot_wider(names_from = c("Pop"), values_from = c("AF")) %>% arrange(Chrom, Site)
#with three pops
adf4<-adf3 %>%  mutate(Marker=1:n()) %>% relocate(Chrom, Site, Marker) %>% pivot_longer(4:6, names_to = "Population",values_to = "AF")

#Two pop version
#adf4<-adf3 %>% mutate(Difference=abs(PNG-AUS)) %>% arrange(-Difference) %>% mutate(Marker=1:n()) %>% relocate(Chrom, Site, Marker, Difference) %>% pivot_longer(5:6, names_to = "Population",values_to = "AF")

adf4
```
As major allele freqs
```{r}
ggplot(adf4) +
  geom_bar(aes(x=Marker, y=AF, fill=Population), color="black",stat = 'identity') +
  facet_grid(Population~.) +
  theme_bw() +
  scale_fill_viridis_d() +
  theme(panel.grid = element_blank())
```
```{r}
ggplot(adf4) +
  geom_point(aes(x=Marker, y=AF, fill=Population), pch=21) +
  geom_line(aes(x=Marker, y=AF, color=Population), alpha=0.75) +
  theme_bw() +
  scale_fill_viridis_d() +
  scale_color_viridis_d() +
  theme(panel.grid = element_blank())
```

For two pops
```{r, eval=FALSE}
ggplot(adf4) +
  geom_point(aes(x=Marker, y=Difference))+
  theme_bw() +
  theme(panel.grid = element_blank()) +
  ylim(0,1)
```
NC_066836_1_17592689, NC_066853_1_2248175.0 are the highest in terms of DAPC loadings (marker 2,17 here, showing low PNG AF). Two ways to visualize this plot more clearly.    

## Validate with WGS data

```{r}
m2<-read_csv("meta/58.csv")
m2$Region<-factor(m2$Region, levels=c("Queensland","Northern Territory","Papua New Guinea",
                                              "Indonesia","Philippines","Vietnam","Cambodia","Thailand",
                                              "India Eastern Coast","India Western Coast"))

wop<-m2 %>% filter(Region %in% c("Queensland","Northern Territory","Papua New Guinea")) 
wop %>% group_by(Region) %>% summarize(Count=n())

write_tsv(wop %>% select(Path), file="bamlists/17.bamlist", col_names = FALSE)
```

Had to move site list and index in genome dir 
```{sh, eval=FALSE}
srun -t 12:00:00 -p high --mem=32G --nodes=1 --ntasks-per-node=1 --cpus-per-task=12 $HOME/angsd/angsd -nthreads 24 \
-minInd 9 -bam bamlists/17.bamlist -ref genome/GCF_001640805.2_TLL_Latcal_v3_genomic.fna \
-rf genome/lates-lgs.txt -sites genome/top-site-list.tsv -out outputs/106/snps-wgs  \
-minMaf 0.05 -minMapQ 20 -minQ 20 -GL 1 -doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 \
-doGeno 2 -doPost 1 -postCutoff 0.9 -doPlink 2  > outputs/106/snps-wgs.out 2> outputs/106/snps-wgs.err &

srun -t 12:00:00 -p high --mem=32G --nodes=1 --ntasks-per-node=1 --cpus-per-task=12 $HOME/angsd/angsd -nthreads 24 \
-minInd 9 -bam bamlists/17.bamlist -ref genome/GCF_001640805.2_TLL_Latcal_v3_genomic.fna \
-rf genome/lates-lgs.txt -sites genome/top-site-list.tsv -out outputs/106/snps-wgs-geno4  \
-minMaf 0.05 -minMapQ 20 -minQ 20 -GL 1 -doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 \
-doGeno 4 -doPost 1 -postCutoff 0.9   > outputs/106/snps-wgs-geno4.out 2> outputs/106/snps-wgs-geno4.err &
```

min maf doesn't do anything, but leaving it in

	-> Number of sites retained after filtering: 12 with minInd 15 in bak subdir
	-> 
hmmm...

```{sh, eval=FALSE}
plink --tped snps-wgs.tped --tfam snps-wgs.tfam  --out snps-wgs-binary --recode --allow-extra-chr --noweb
plink --ped snps-wgs-binary.ped --map snps-wgs-binary.map --recode vcf --allow-extra-chr -out snps-wgs
```


```{r}
vcfwgs<-read.vcfR(file="outputs/106/bak/snps-wgs.vcf")
wgs<-vcfR2genind(vcfwgs)
wgs@pop<-factor(wop$Region, levels=c("Northern Territory","Papua New Guinea", "Queensland"))
wgs
```
```{r}
X <- tab(wgs, NA.method="mean")
pca1 <- dudi.pca(X,scannf=FALSE,scale=FALSE,nf=3)

df<-pca1$li
df<-df %>% bind_cols(wop)
eig<-pca1$eig/sum(pca1$eig)*100

ggplot(df) + 
  geom_point(aes(x=Axis1, y=Axis2, fill=Region), pch=21) +
  theme_bw() +
  xlab(paste0("PC1 ",round(eig[1],2), "%"))
  ylab(paste0("PC2 ",round(eig[2],2), "%")) +
  theme(panel.grid = element_blank()) +
  scale_fill_viridis_d()

```


Combining

```{r}
d4<-d3[loc=unique(wgs@loc.fac),]
d4@pop<-gen@pop
comb<-repool(d4,wgs)

```

```{r}
X <- tab(comb, NA.method="mean")
pca1 <- dudi.pca(X,scannf=FALSE,scale=FALSE,nf=3)

df<-pca1$li
df$Pop<-comb@pop
df<-df %>% mutate(DataType=ifelse(Pop %in% c("AUW","AUE","PNG"), "RADSeq","WGS"))
eig<-pca1$eig/sum(pca1$eig)*100
```

```{r}
ggplot(df) + 
  geom_point(aes(x=Axis1, y=Axis2, fill=Pop, shape=DataType)) +
  theme_bw() +
  scale_shape_manual(values = c(21,23)) +
   xlab(paste0("PC1 ",round(eig[1],2), "%")) +
  ylab(paste0("PC2 ",round(eig[2],2), "%")) +
  theme(panel.grid = element_blank()) +
  scale_fill_viridis_d(option="H") +
  guides(fill = guide_legend(override.aes = list(pch = 22))) 



```

Neat! Combined with existing samples the 20 loci separate the fish into groups.


```{r}
kstat<-find.clusters(comb, n.pca=12,n.clust=2)

#with 20 loci
#kstat<-find.clusters(comb, n.pca=20,n.clust=2)
dft<-as.data.frame(table(pop(comb), kstat$grp)) %>% as_tibble() %>%
  rename(Location=Var1, Assignment=Var2, Number=Freq)

dft$Location<-factor(dft$Location, levels=c("AUW","AUE","Northern Territory","Queensland","PNG","Papua New Guinea"))
assign<-ggplot(dft, aes(y=Location, x=Assignment)) +
  theme(axis.title.y = element_text(size = rel(1))) +
  theme(axis.title.x = element_text(size = rel(1))) +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(x="\nInferred Group", y="Sampling Location\n") +
  theme(text=element_text(family='Times')) +
  theme(axis.text.x= element_text(face="bold", size=10, vjust = 0.5)) +
  theme(axis.text.y= element_text(face="bold", size=10)) +
  geom_point(aes(x=Assignment, y=Location, size=Number)) +
 # geom_text(aes(x=Assignment, y=Location, label=Number), color="white", size=3) +
  scale_size_area(limits=c(1,30), breaks=c(1,10,20,30)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black")) 
assign  

ggsave("outputs/106/assignments.pdf", width=6, height=4)
```
71 Individauls


```{r}
ggarrange(totpc+ggtitle("A") +  theme(plot.title = element_text(size=14, face="bold"), legend.position = "none") ,
          pca+ggtitle("B"), bicplot, assign+ggtitle("D") +  theme(plot.title = element_text(size=14, face="bold")),
                                                                  widths = c(1,1.25))

ggsave("outputs/106/Figure.pdf")
```

```{r}
d1<-dapc(comb, kstat$grp, n.pca=12, n.da=2)

post<-d1$posterior %>% as_tibble()
post$Pop<-comb@pop
post$Ind<-rownames(comb@tab)
post<-post %>% mutate(DataType=ifelse(Pop %in% c("AUW","AUE","PNG"), "RADSeq","WGS")) %>% relocate(DataType,Pop, Ind) 
post$Pop<-factor(post$Pop, levels=c("AUW","Northern Territory","AUE","Queensland","PNG","Papua New Guinea"))
post <- post %>% arrange(Pop) %>% mutate(Individual=1:n()) %>% relocate(Individual)

post<- post %>%  pivot_longer(5:6, names_to = "Cluster", values_to = "Posterior")
post
```
```{r}
ggplot(post) +
  geom_col(aes(x=Individual,y=Posterior, fill=Cluster), color="NA", size = 0, width = 1, alpha=0.8) +
  scale_fill_viridis_d() +
 # coord_flip() +
  facet_grid(.~Pop, scales = "free", space = "free") +
  theme_bw() +
  theme(panel.grid = element_blank()) +
  theme(axis.ticks.x = element_blank())+
  theme(axis.text.x = element_blank())
  
```

Pretty good!  Is missing data a problem? Basically one missassignment with WGS

Individual 4_1 doesn't have missing data with 12 snps.  