---
title: "1203-mtdna"
output: html_document
date: "2024-12-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(tidyverse)
```

For some genomic analysis, we can use fragmentary de novo assemblies. We can also use the mtDNA to generate control region data because of _1_ unique andaman mtDNA, _2_ Wallacean fish, and _3_  better characterization of diversity in Australia.

let's start with the Wallacean fish and see if we can get a complete mitogenome.Options, use alignment to reference mtdna and pull out aligned/single aligned data and assemble. Otherwise, use all the data and see what shakes out.    

(base) maccamp@farm:~$ module load spades
Loading spades/3.15.5
spades.py --test

Seems to work.    
```{r}
sra<-read_csv("meta/lates-wgs-SraRunInfo.csv")
indo<-sra %>% select(Run, Experiment,SampleName,Region) %>% filter(Region=="Indonesia")
sra %>% select(Run, Experiment,SampleName,Region) %>% group_by(Region) %>% summarize(Count=n())
indo
```
ind data/raw
```{sh, eval=FALSE}
cat ../../meta/lates-wgs-SraRunInfo.csv | grep Indonesia | cut -d ',' -f 10 | while read line; do wget $line; done;
```

Getting SRR3165613.sralite.1

module load ncbi-toolkit/26_0_1 (added to bash_profile)     
module load sratoolkit/3.0.0       

 `for f in data/raw/*sralite.1; do echo $f; fastq-dump --outdir data/denovo --skip-technical --read-filter pass --dumpbase --split-3 --gzip --clip $f; done;  `    
```{r}
indo %>% mutate(Command=paste0("fastq-dump --outdir data/denovo --skip-technical --read-filter pass --dumpbase --split-3 --gzip --clip data/raw/", Run, ".sralite.1")) %>% select(Command) %>% write_tsv(file="1203.1-split.sh", col_names = FALSE)

```

module load parallel
module load ncbi-toolkit/26_0_1
module load sratoolkit/3.0.0       

```{sh, eval=FALSE}
srun -p bigmemm --time 2:00:00 --nodes=1 --ntasks-per-node=1 --cpus-per-task=10 parallel -j 10 < 1203.1-split.sh
```


# Spades
module load spades

bin/spades.py -1 left.fastq.gz -2 right.fastq.gz -o output_folder

```{r}

```