---
title: "1204.3-mtdna"
output: html_document
date: "2025-01-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

Have some mtDNA from WJC. Checking it out.

```{r}
library(tidyverse)
library(ggtree)
library(phytools)
library(viridis)
```

aligned with mafft

in outputs/1204/mtdna
(base) ➜  mtdna git:(main) ✗ iqtree2 -nt AUTO -s coi-wjc.afasta -T AUTO -st DNA -m MFP -bb 10000 --redo 

now-no og

 mafft coi-wjc-noog.fasta > coi-wjc-noog.afasta
 
iqtree2 -nt AUTO -s coi-wjc-noog.afasta -T AUTO -st DNA -m MFP -bb 10000 --redo 

```{r}
tree<-read.tree("outputs/1204/mtdna/coi-wjc-noog.afasta.contree")
t2<-midpoint.root(tree)
t3<-as.polytomy(t2, feature='node.label', fun=function(x) as.numeric(x) < 75)

t<-t3

t<-ggtree(t)

t$data$Bootstrap<-as.numeric(t$data$label)

d <- t$data
d <- d[!d$isTip,]
d$label <- as.numeric(d$label)
d <- d[d$label >= 90,]

e <- t$data
e <- e[!e$isTip,]
e$label <- as.numeric(e$label)
e <- e[e$label < 90,]
e <- e[e$label >= 75,]
```



```{r}
m2<-read_csv("meta/combined-mtdna.csv")
u<-t %<+% m2 + #bind_rows(m58, rm) +
  geom_point(data=e,  fill="gray50", cex=2, alpha=1, pch=21) +
  geom_point(data=d,  fill="black", cex=2, alpha=1, pch=21) +
  geom_tiplab(aes(label=paste0(label," ",Region), x=x+0.001), align = FALSE, size=2) +
  #geom_text(data=t$data %>% filter(isTip==TRUE) %>% filter(label %in% Run), aes(label=label, x=x+0.01), size=3) +
  guides(fill = guide_legend(override.aes = list(pch = 22))) +
  xlim(0,.07) +
  scale_fill_viridis_d(option="H") +
  theme(legend.position = "none") +
  geom_treescale()

u
ggsave("outputs/1204/mtdna-coi-phylo.pdf", width=6.5, height=8)
```


## From alignments

_1_ create bam for each
_2_ convert to consensus fasta
_3_ getbarcode region

Here is a loop:
srun -p high --nodes=1 --mem=32G -t 01:30:00 cut -f 1 -d ',' meta/58.csv | while read run; do samtools view -b data/split/$run.sort.flt.bam NC_007439.1 > data/mtdna/$run-mtdna.bam; samtools index data/mtdna/$run-mtdna.bam; /home/maccamp/proovread/bin/bam2cns --bam data/mtdna/$run-mtdna.bam --ref genome/NC_007439.1.fasta --prefix data/mtdna/$run-mtdna;  ~/seqtk/seqtk seq -a -q20 -n N data/mtdna/$run-mtdna.fq > data/mtdna/$run-mtdna-q20.fasta; samtools faidx data/mtdna/$run-mtdna-q20.fasta NC_007439.1:6329-7879 > data/mtdna/$run-coi.fasta; done;


```{sh, eval=FALSE}
srun -p high --nodes=1 --mem=32G -t 01:30:00 cat bamlists/103.bamlist | while read path; do samtools view -b $path NC_007439.1 > data/new-mtdna/`basename $path .sort.flt.bam`.bam; samtools index data/new-mtdna/`basename $path .sort.flt.bam`.bam; /home/maccamp/proovread/bin/bam2cns --bam data/new-mtdna/`basename $path .sort.flt.bam`.bam --ref genome/NC_007439.1.fasta --prefix data/new-mtdna/`basename $path .sort.flt.bam`-mtdna;  ~/seqtk/seqtk seq -a -q20 -n N data/new-mtdna/`basename $path .sort.flt.bam`-mtdna.fq > data/new-mtdna/`basename $path .sort.flt.bam`-mtdna-q20.fasta; samtools faidx data/new-mtdna/`basename $path .sort.flt.bam`-mtdna-q20.fasta NC_007439.1:6329-7879 > data/new-mtdna/`basename $path .sort.flt.bam`-coi.fasta; samtools faidx data/new-mtdna/`basename $path .sort.flt.bam`-mtdna-q20.fasta NC_007439.1:769- > data/new-mtdna/`basename $path .sort.flt.bam`-ex-control.fasta; done;


#redoing a bit
cat bamlists/103.bamlist | while read path; do samtools faidx data/new-mtdna/`basename $path .sort.flt.bam`-mtdna-q20.fasta NC_007439.1:6329-7879 > data/new-mtdna/`basename $path .sort.flt.bam`-coi.fasta; samtools faidx data/new-mtdna/`basename $path .sort.flt.bam`-mtdna-q20.fasta NC_007439.1:769- > data/new-mtdna/`basename $path .sort.flt.bam`-ex-control.fasta; done;

#rename and consolidate.
awk '/^>/{print ">" substr(FILENAME,1,length(FILENAME)-10); next} 1' *-coi.fasta | perl -pe 's/.reduced.bam//g' > coi-taiwan.fasta

#mitogenomes without control region
awk '/^>/{print ">" substr(FILENAME,1,length(FILENAME)-10); next} 1' *-ex-control.fasta | perl -pe 's/.reduced.bam//g' | perl -pe 's/-ex-con//g' > mitogenomes.fasta

```

/Users/mac/github/lates-wgs/data/taiwan-coi

aligned with mafft

```{sh, eval=FALSE}
iqtree2 -nt AUTO -s coi-taiwan.afas -T AUTO -st DNA -m MFP -bb 10000 --redo 
iqtree2 -nt AUTO -s mitogenomes.afas -T AUTO -st DNA -m MFP -bb 10000 --redo 
```

```{r}
m103<-read_csv("meta/m103.csv")
m103$Region<-factor(m103$Region, levels=c("Queensland","Northern Territory","Papua New Guinea","Mainstream","OceanPick",
                                           "Indonesia-K","Indonesia-SU","Indonesia-SJ","Philippines","Taiwan",
                                              "Vietnam","Cambodia","Thailand", "Bangladesh",
                                              "India East Coast","Sri Lanka","India West Coast"))

```

```{r}
tree<-read.tree("data/taiwan-coi/coi-taiwan.afas.contree")
t2<-midpoint.root(tree)
t3<-as.polytomy(t2, feature='node.label', fun=function(x) as.numeric(x) < 50)

t<-t3

t<-ggtree(t)

t$data$Bootstrap<-as.numeric(t$data$label)

d <- t$data
d <- d[!d$isTip,]
d$label <- as.numeric(d$label)
d <- d[d$label >= 90,]

e <- t$data
e <- e[!e$isTip,]
e$label <- as.numeric(e$label)
e <- e[e$label < 90,]
e <- e[e$label >= 75,]
```



```{r}
u<-t %<+% m103 + #bind_rows(m58, rm) +
  geom_point(data=e,  fill="gray50", cex=2, alpha=1, pch=21) +
  geom_point(data=d,  fill="black", cex=2, alpha=1, pch=21) +
  geom_tiplab(aes(label=paste0(label," ",Region), x=x+0.003), align = FALSE, size=2) +
  geom_tippoint(aes(fill=Region, shape=Lineage, x=x+0.001), cex=2)+
  #geom_text(data=t$data %>% filter(isTip==TRUE) %>% filter(label %in% Run), aes(label=label, x=x+0.01), size=3) +
  guides(fill = guide_legend(override.aes = list(pch = 22))) +
  xlim(0,.07) +
  scale_fill_viridis_d(option="H") +
  scale_shape_manual(values=c(21,23,23,21,21,24)) + 
  theme(legend.position = "none") +
  geom_treescale()

u
ggsave("outputs/1204/mapping-mtdna-coi-phylo.pdf", width=6.5, height=12)
```


## Mitogenomes


```{r}
tree<-read.tree("data/taiwan-coi/mitogenomes.afas.contree")
t2<-midpoint.root(tree)
t3<-as.polytomy(t2, feature='node.label', fun=function(x) as.numeric(x) < 50)

t<-t3

t<-ggtree(t)

t$data$Bootstrap<-as.numeric(t$data$label)

d <- t$data
d <- d[!d$isTip,]
d$label <- as.numeric(d$label)
d <- d[d$label >= 90,]

e <- t$data
e <- e[!e$isTip,]
e$label <- as.numeric(e$label)
e <- e[e$label < 90,]
e <- e[e$label >= 75,]
```



```{r}
u<-t %<+% m103 + #bind_rows(m58, rm) +
  geom_point(data=e,  fill="gray50", cex=2, alpha=1, pch=22) +
  geom_point(data=d,  fill="black", cex=2, alpha=1, pch=22) +
  geom_tiplab(aes(label=paste0(label," ",Region), x=x+0.003), align = FALSE, size=2) +
  geom_tippoint(aes(fill=Region, shape=Lineage, x=x+0.001), cex=2)+
  #geom_text(data=t$data %>% filter(isTip==TRUE) %>% filter(label %in% Run), aes(label=label, x=x+0.01), size=3) +
  guides(fill = guide_legend(override.aes = list(pch = 22))) +
  xlim(0,.09) +
  scale_fill_viridis_d(option="H") +
  scale_shape_manual(values=c(21,23,23,21,21,24)) + 
  theme(legend.position = "none") +
  geom_treescale()

u
ggsave("outputs/1204/mapping-mtdna-mitogenome-phylo.pdf", width=12, height=12)
```



## Attach a barplot of admixture proportions

```{r}
admix<-read_csv("outputs/1204/k4.csv")
admix$Cluster<-factor(admix$Cluster, levels=c("1","2","3","4"))
```

```{r}
q<-read_delim("outputs/1204/admixture/myplink2.3.Q", delim=" ", col_names=FALSE)
#Make generic colnames

nums<-1:length(colnames(q))
mynames<-paste0(nums)

qs<-length(colnames(q))-1

colnames(q)<-mynames

q2<-bind_cols(q, m103 %>% select(Run)) %>% pivot_longer(cols = mynames, names_to = "Cluster", values_to = "Percentage")
```

```{r}
m18<-m103 %>% filter(Region %in% c("Taiwan","Thailand"))

q<-read_delim("outputs/1211/myplink2.2.Q", delim=" ", col_names=FALSE)
#Make generic colnames

nums<-4:(length(colnames(q))+3)
mynames<-paste0(nums)

qs<-length(colnames(q))-1

colnames(q)<-mynames

q3<-bind_cols(q, m18 %>% select(Run)) %>% pivot_longer(cols = mynames, names_to = "Cluster", values_to = "Percentage")
```

```{r}
data<-read_tsv("outputs/1206/lc05-haplos.txt")
fills<-viridis(3)

df05<-m103 %>% left_join(data, by=c("Run"="samples")) %>%
  mutate(Genotype=ifelse(NumberRR > NumberAA & NumberRR > NumberAR, "RHom",
                       ifelse(NumberAA > NumberRR & NumberAA > NumberAR, "AHom",
                       ifelse(NumberAR > NumberAA & NumberAR > NumberRR, "Het","Other")))) %>%
 mutate(Color=ifelse(NumberRR > NumberAA & NumberRR > NumberAR, fills[1],
                       ifelse(NumberAA > NumberRR & NumberAA > NumberAR, fills[2],
                       ifelse(NumberAR > NumberAA & NumberAR > NumberRR, fills[3],"Other"))))

data<-read_tsv("outputs/1206/lc20-haplos.txt")

df20<-m103 %>% left_join(data, by=c("Run"="samples")) %>%
  mutate(Genotype=ifelse(NumberRR > NumberAA & NumberRR > NumberAR, "RHom",
                       ifelse(NumberAA > NumberRR & NumberAA > NumberAR, "AHom",
                       ifelse(NumberAR > NumberAA & NumberAR > NumberRR, "Het","Other")))) %>%
 mutate(Color=ifelse(NumberRR > NumberAA & NumberRR > NumberAR, fills[1],
                       ifelse(NumberAA > NumberRR & NumberAA > NumberAR, fills[2],
                       ifelse(NumberAR > NumberAA & NumberAR > NumberRR, fills[3],"Other"))))

```

lca03 from mat
```{r}
df03<-read_csv("outputs/1206/lc03.csv")
df0301<-df03 %>% select(FID, `genotype Inversion 1`) %>% mutate(Genotype=ifelse(`genotype Inversion 1`==1,"RHom",
                                                                   ifelse(`genotype Inversion 1`==2,"Het","AHom")))
df0302<-df03 %>% select(FID, `genotype Inversion 2`) %>% mutate(Genotype=ifelse(`genotype Inversion 2`==1,"RHom",
                                                                   ifelse(`genotype Inversion 2`==2,"Het","AHom")))
```

Which individuals are hets for both

```{r}
df03 %>% filter(`genotype Inversion 1`==`genotype Inversion 2`) %>% filter(`genotype Inversion 1`==2)
```

sanity check

```{r}
d01<-read_csv("~/Dropbox/Australian-fishes/barra-con-gen/lca03-analyses/lg03-01-hets.csv") %>% 
  left_join(df0301)

labels01<-d01%>% group_by(Genotype) %>% mutate(Count=n())

ggplot(d01) +
  geom_boxplot(aes(x=Genotype, y=heterozygosity)) +
  geom_text(data=labels01,aes(x=Genotype, y=0.4, label=Count)) +
  ggtitle("Lca03-01 Heterozygosity")


```


```{r}
d02<-read_csv("~/Dropbox/Australian-fishes/barra-con-gen/lca03-analyses/lg03-01-hets.csv") %>% 
  left_join(df0302)

labels02<-d02%>% group_by(Genotype) %>% mutate(Count=n())

ggplot(d02) +
  geom_boxplot(aes(x=Genotype, y=heterozygosity)) +
  geom_text(data=labels02,aes(x=Genotype, y=0.4, label=Count)) +
  ggtitle("Lca03-02 Heterozygosity")



```

```{r}
v<-t %<+% m103 + #bind_rows(m58, rm) +
 # geom_point(data=e,  fill="gray50", cex=2, alpha=1, pch=22) +
  #geom_point(data=d,  fill="black", cex=2, alpha=1, pch=22) +
  geom_tiplab(aes(label=paste0(label," ",Region), x=x+0.003), align = FALSE, size=2) +
  geom_tippoint(aes(shape=Lineage, x=x+0.001),fill="grey50", cex=2)+
  #geom_text(data=t$data %>% filter(isTip==TRUE) %>% filter(label %in% Run), aes(label=label, x=x+0.01), size=3) +
  guides(fill = guide_legend(override.aes = list(pch = 22))) +
  scale_shape_manual(values=c(21,23,23,21,21,24)) + 
  #theme(legend.position = "none") +
  geom_treescale()
v
```


````{r}
w<-v + 
  #geom_facet(panel = 'Admixture Proportions', data = admix, geom = geom_bar, 
   #              mapping = aes(x=Percentage, fill=Cluster), 
    #            orientation = 'y', width = 1, stat="identity") +
    geom_facet(panel = 'Admixture Proportions', data = q2, geom = geom_bar, 
                 mapping = aes(x=Percentage, fill=Cluster), 
                orientation = 'y', width = 1, stat="identity") +
   #   geom_facet(panel = 'Admixture Proportions T', data = q3, geom = geom_bar, 
    #             mapping = aes(x=Percentage, fill=Cluster), 
     #           orientation = 'y', width = 1, stat="identity") +
   geom_facet(panel="Lca03-01", data=df0301, geom=geom_tile,
                  mapping = aes(x=1, fill=Genotype))  +
  geom_facet(panel="Lca03-02", data=df0302, geom=geom_tile,
                  mapping = aes(x=1, fill=Genotype))  +
       geom_facet(panel="Lca05", data=df05, geom=geom_tile,
                  mapping = aes(x=1, fill=Genotype))  +
  geom_facet(panel="Lca20", data=df20, geom=geom_tile,
                  mapping = aes(x=1, fill=Genotype)) +
       xlim_tree(.09) + #scale_fill_viridis_d(option="magma", direction=-1) 
       scale_fill_manual(values=c(viridis(3),viridis(3, option="magma")))
facet_widths(w, c(Tree = 4, `Admixture Proportions`=1, `Lca03-01`=0.5, `Lca03-02`=0.5, `Lca05`=0.5,`Lca20`=0.5))
ggsave("outputs/1204/mapping-mtdna-mitogenome-admixture-phylo.pdf", width=12, height=12)

```

```{r}

admix %>% filter(pop %in% c("Taiwan", "Thailand","Philippines")) %>% filter(Cluster=="3") %>% arrange(-Percentage)

```


```