---
title: "1206-taiwanese-inversions"
output: html_document
date: "2025-01-17"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(tidyverse)
```

```{r}
meta<-read_csv("meta/m103.csv")
meta$Pop<-gsub(" ","-",meta$Region)
```

Let's examine the inversion regions. Have genotypes called from 1204, but need -doGeno 4 

```{sh, eval=FALSE}
srun -t 8:00:00 -p high --mem=32G --nodes=1 --ntasks-per-node=1 --cpus-per-task=12 $HOME/angsd/angsd -nthreads 12 \
-minInd 93 -bam bamlists/103.bamlist -ref genome/GCF_001640805.2_TLL_Latcal_v3_genomic.fna \
-r NC_066835.1:1-17500000 -out outputs/1206/lg03  \
-minMaf 0.05 -minMapQ 20 -minQ 20 -GL 1 -doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 \
-doGeno 4 -doPost 1 -postCutoff 0.9 -doPlink 2  > outputs/1206/lg03.out 2> outputs/1206/lg03.err &

srun -t 8:00:00 -p high --mem=32G --nodes=1 --ntasks-per-node=1 --cpus-per-task=12 $HOME/angsd/angsd -nthreads 12 \
-minInd 93 -bam bamlists/103.bamlist -ref genome/GCF_001640805.2_TLL_Latcal_v3_genomic.fna \
-r NC_066837.1:5247652- -out outputs/1206/lg05  \
-minMaf 0.05 -minMapQ 20 -minQ 20 -GL 1 -doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 \
-doGeno 4 -doPost 1 -postCutoff 0.9 -doPlink 2  > outputs/1206/lg05.out 2> outputs/1206/lg05.err &

srun -t 8:00:00 -p high --mem=32G --nodes=1 --ntasks-per-node=1 --cpus-per-task=12 $HOME/angsd/angsd -nthreads 12 \
-minInd 93 -bam bamlists/103.bamlist -ref genome/GCF_001640805.2_TLL_Latcal_v3_genomic.fna \
-r NC_066852.1:3500000- -out outputs/1206/lg20  \
-minMaf 0.05 -minMapQ 20 -minQ 20 -GL 1 -doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 \
-doGeno 4 -doPost 1 -postCutoff 0.9 -doPlink 2  > outputs/1206/lg20.out 2> outputs/1206/lg20.err &

#in 1204
plink --tped lg03.tped --tfam lg03.tfam  --out lg03-binary --recode --allow-extra-chr --noweb
plink --ped lg03-binary.ped --map lg03-binary.map --recode vcf --allow-extra-chr -out lg03
bgzip lg03.vcf 
tabix lg03.vcf.gz

plink --tped lg05.tped --tfam lg05.tfam  --out lg05-binary --recode --allow-extra-chr --noweb
plink --ped lg05-binary.ped --map lg05-binary.map --recode vcf --allow-extra-chr -out lg05
bgzip lg05.vcf 
tabix lg05.vcf.gz

plink --tped lg20.tped --tfam lg20.tfam  --out lg20-binary --recode --allow-extra-chr --noweb
plink --ped lg20-binary.ped --map lg20-binary.map --recode vcf --allow-extra-chr -out lg20
bgzip lg20.vcf 
tabix lg20.vcf.gz

```

We can use the diagnostic loci from the g3 paper.


```{sh, eval=FALSE}
cp ~/github/g3-lates-inversions/outputs/607/*diagnostic.tsv .
cp ~/github/g3-lates-inversions/omy05-haplotyper.pl 

scp farm:~/lates-wgs/outputs/1206/lg*.geno.gz .

gunzip -c lg20.geno.gz | cut -f 2-105 > lc20.geno    
gunzip -c lg05.geno.gz | cut -f 2-105 > lc05.geno   
gunzip -c lg03.geno.gz | cut -f 2-105 > lc03.geno   


#./105-omy05-haplotyper.pl genotypes.txt  genosToTest.txt bamlist
#This script is hard coded for some reason for the number of samples 

 ./omy05-haplotyper.pl lc20-diagnostic.tsv lc20.geno ../../bamlists/103-sample-names.txt > lc20-haplos.txt 
./omy05-haplotyper.pl lc05-diagnostic.tsv lc05.geno ../../bamlists/103-sample-names.txt > lc05-haplos.txt 
./omy05-haplotyper.pl lc03-diagnostic.tsv lc03.geno ../../bamlists/103-sample-names.txt > lc03-haplos.txt 

```


IO data

```{r}
io<-m103 %>% filter(Lineage %in% c("IND","lakdiva"))
io %>% select(Run) %>% write_tsv("meta/io-samples.txt", col_names = FALSE)

sea<-m103 %>% filter(Lineage %in% c("SEA"))
sea %>% select(Run) %>% write_tsv("meta/sea-samples.txt", col_names = FALSE)

aus<-m103 %>% filter(Lineage %in% c("AUS+NG"))
aus %>% select(Run) %>% write_tsv("meta/aus-samples.txt", col_names = FALSE)

```

# PCAs

```{sh, eval=FALSE}
scp farm:~/lates-wgs/outputs/1204/lg*.vcf.gz .

bcftools +fill-tags lg03.vcf.gz  -- -t MAF,F_MISSING | bcftools view -i 'F_MISSING < 0.05' | bcftools view -i 'INFO/MAF > 0.05' > lg03-filtered.vcf

#pull out lg03 IO fish 

bcftools reheader --samples bamlists/103-sample-names.txt -o outputs/1206/lg03-renamed.vcf.gz outputs/1206/lg03.vcf.gz
bcftools view -S meta/io-samples.txt outputs/1206/lg03-renamed.vcf.gz | bcftools +fill-tags  -- -t MAF,F_MISSING | bcftools view -i 'F_MISSING < 0.05' | bcftools view -i 'INFO/MAF > 0.05' > outputs/1206/lg03-io.vcf


bcftools +fill-tags lg05.vcf.gz  -- -t MAF,F_MISSING | bcftools view -i 'F_MISSING < 0.05' | bcftools view -i 'INFO/MAF > 0.05' > lg05-filtered.vcf

bcftools +fill-tags lg20.vcf.gz  -- -t MAF,F_MISSING | bcftools view -i 'F_MISSING < 0.05' | bcftools view -i 'INFO/MAF > 0.05' > lg20-filtered.vcf
```
from 55,952 variants to 18372 for lg03

## Lca03

```{r}
vcf<-read.vcfR(file="outputs/1206/lg03-filtered.vcf")
genind<-vcfR2genind(vcf)
genind@pop<-as.factor(meta$Pop)
```

```{r}
gen<-genind
X <- tab(gen, NA.method="mean")

pca1 <- dudi.pca(X,scannf=FALSE,scale=FALSE,nf=3)

df<-pca1$li
df<-df %>% bind_cols(meta)
df$Lineage<-factor(df$Lineage, levels=c("AUS+NG","Mainstream","OceanPick","SEA","IND","lakdiva"))
df$Region<-factor(df$Pop, levels=c("Queensland","Northern-Territory","Papua-New-Guinea","Mainstream","OceanPick","Indonesia-K","Indonesia-SU","Indonesia-SJ","Philippines","Taiwan","Vietnam","Cambodia","Thailand","Bangladesh","India-East-Coast","Sri-Lanka","India-West-Coast"))

eig<-pca1$eig/sum(pca1$eig)*100
```

```{r}
lc03pc12<-ggplot(df) + 
  geom_point(aes(x=Axis1, y=Axis2, fill=Region, shape=Lineage), alpha=0.75, cex=2) +
  theme_bw() +
  xlab(paste0("PC1 ",round(eig[1],2), "%")) +
  ylab(paste0("PC2 ",round(eig[2],2), "%")) +
  theme(panel.grid = element_blank()) +
  scale_fill_viridis_d(option="H") +
  scale_shape_manual(values=c(21,21,21,24,23,23)) +
  guides(fill = guide_legend(override.aes = list(pch = 22))) +
  theme(legend.position = "top")
lc03pc12

ggsave("outputs/1206/lg03.jpeg", width=14, height=10)
```



```{r}
vcf<-read.vcfR(file="outputs/1206/lg03-io.vcf")
genind<-vcfR2genind(vcf)
genind@pop<-as.factor(io$Pop)
```

```{r}
gen<-genind
X <- tab(gen, NA.method="mean")

pca1 <- dudi.pca(X,scannf=FALSE,scale=FALSE,nf=3)

df<-pca1$li
df<-df %>% bind_cols(io)

eig<-pca1$eig/sum(pca1$eig)*100
```

```{r}
lc03pc12<-ggplot(df) + 
  geom_point(aes(x=Axis1, y=Axis2, fill=Region,), alpha=0.75, cex=2, pch=23) +
  theme_bw() +
  xlab(paste0("PC1 ",round(eig[1],2), "%")) +
  ylab(paste0("PC2 ",round(eig[2],2), "%")) +
  theme(panel.grid = element_blank()) +
  scale_fill_viridis_d(option="magma") +
  guides(fill = guide_legend(override.aes = list(pch = 22))) +
  theme(legend.position = "top")
lc03pc12

ggsave("outputs/1206/lg03-io.jpeg", width=10, height=10)
```
Well, crap. Should look at LD across the whole chrom.

```{sh, eval=FALSE}
srun -t 8:00:00 -p high --mem=32G --nodes=1 --ntasks-per-node=1 --cpus-per-task=12 $HOME/angsd/angsd -nthreads 12 \
-minInd 93 -bam bamlists/103.bamlist -ref genome/GCF_001640805.2_TLL_Latcal_v3_genomic.fna \
-r NC_066835.1 -out outputs/1206/lg03-whole-chrom  \
-minMaf 0.05 -minMapQ 20 -minQ 20 -GL 1 -doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 \
-doGeno 4 -doPost 1 -postCutoff 0.9 -doPlink 2  > outputs/1206/lg03-whole-chrom.out 2> outputs/1206/lg03-whole-chrom.err &

plink --tped lg03-whole-chrom.tped --tfam lg03-whole-chrom.tfam  --out lg03-whole-chrom-binary --recode --allow-extra-chr --noweb
plink --ped lg03-whole-chrom-binary.ped --map lg03-whole-chrom-binary.map --recode vcf --allow-extra-chr -out lg03-whole-chrom
bgzip lg03-whole-chrom.vcf 
tabix lg03-whole-chrom.vcf.gz


bcftools reheader --samples bamlists/103-sample-names.txt outputs/1206/lg03-whole-chrom.vcf.gz | bcftools +fill-tags  -- -t MAF,F_MISSING | bcftools view -i 'F_MISSING < 0.05' | bcftools view -i 'INFO/MAF > 0.05' > outputs/1206/lg03-all-samples-whole-chrom.vcf


bcftools reheader --samples bamlists/103-sample-names.txt -o outputs/1206/lg03-whole-chrom-renamed.vcf.gz outputs/1206/lg03-whole-chrom.vcf.gz
bcftools view -S meta/io-samples.txt outputs/1206/lg03-whole-chrom-renamed.vcf.gz | bcftools +fill-tags  -- -t MAF,F_MISSING | bcftools view -i 'F_MISSING < 0.05' | bcftools view -i 'INFO/MAF > 0.05' > outputs/1206/lg03-io-whole-chrom.vcf

#SEA samples
bcftools view -S meta/sea-samples.txt outputs/1206/lg03-whole-chrom-renamed.vcf.gz | bcftools +fill-tags  -- -t MAF,F_MISSING | bcftools view -i 'F_MISSING < 0.05' | bcftools view -i 'INFO/MAF > 0.05' > outputs/1206/lg03-sea-whole-chrom.vcf

#AUS+NG
bcftools view -S meta/aus-samples.txt outputs/1206/lg03-whole-chrom-renamed.vcf.gz | bcftools +fill-tags  -- -t MAF,F_MISSING | bcftools view -i 'F_MISSING < 0.05' | bcftools view -i 'INFO/MAF > 0.05' > outputs/1206/lg03-aus-whole-chrom.vcf

```

```{r}
vcf<-read.vcfR(file="outputs/1206/lg03-all-samples-whole-chrom.vcf.gz")
genind<-vcfR2genind(vcf)
genind@pop<-as.factor(io$Pop)
```


```{r}
gen<-genind
X <- tab(gen, NA.method="mean")

pca1 <- dudi.pca(X,scannf=FALSE,scale=FALSE,nf=3)

df<-pca1$li
df<-df %>% bind_cols(m103)

eig<-pca1$eig/sum(pca1$eig)*100
```

```{r}
lc03pc12<-ggplot(df) + 
  geom_point(aes(x=Axis1, y=Axis2, fill=Region,), alpha=0.75, cex=2, pch=23) +
  theme_bw() +
  xlab(paste0("PC1 ",round(eig[1],2), "%")) +
  ylab(paste0("PC2 ",round(eig[2],2), "%")) +
  theme(panel.grid = element_blank()) +
  scale_fill_viridis_d(option="magma") +
  guides(fill = guide_legend(override.aes = list(pch = 22))) +
  theme(legend.position = "top")
lc03pc12

ggsave("outputs/1206/lg03-all-samples-whole-chrom.jpeg", width=10, height=10)
```

```{r}
vcf<-read.vcfR(file="outputs/1206/lg03-io-whole-chrom.vcf")
genind<-vcfR2genind(vcf)
genind@pop<-as.factor(io$Pop)
```

```{r}
gen<-genind
X <- tab(gen, NA.method="mean")

pca1 <- dudi.pca(X,scannf=FALSE,scale=FALSE,nf=3)

df<-pca1$li
df<-df %>% bind_cols(io)

eig<-pca1$eig/sum(pca1$eig)*100
```

```{r}
lc03pc12<-ggplot(df) + 
  geom_point(aes(x=Axis1, y=Axis2, fill=Region,), alpha=0.75, cex=2, pch=23) +
  theme_bw() +
  xlab(paste0("PC1 ",round(eig[1],2), "%")) +
  ylab(paste0("PC2 ",round(eig[2],2), "%")) +
  theme(panel.grid = element_blank()) +
  scale_fill_viridis_d(option="magma") +
  guides(fill = guide_legend(override.aes = list(pch = 22))) +
  theme(legend.position = "top")
lc03pc12

ggsave("outputs/1206/lg03-io-whole-chrom.jpeg", width=10, height=10)
```

Looking at LD

```{sh, eval=FALSE}
#Let's thin 
cat lg03-io-whole-chrom.vcf | grep "#" > header.txt
cat lg03-io-whole-chrom.vcf | grep -v "#" | awk 'BEGIN{i=0}{i++;if (i%50==0) print}' > lg03-thinned.vcf
cat header.txt lg03-thinned.vcf > lg03-thinned.wheader.vcf

plink --vcf lg03-thinned.wheader.vcf --r2 inter-chr --ld-window-r2 0.2 --out lg03-io.ldf --allow-extra-chr --double-id

```

```{r}
lc03<-read.delim("outputs/1206/lg03-io.ldf.ld",sep="",stringsAsFactors=FALSE) %>% as_tibble() %>% arrange(R2) %>% 
  filter(R2 >0.5)

ggplot(lc03) +
  geom_point(aes(x=BP_A, y=BP_B, color=R2), alpha=0.5) +
  scale_color_gradient(low="khaki1", high="red") + 
  theme_bw()
ggsave("outputs/1206/lg03-io-ld.jpeg")
```

Let's look at SEA LD

```{r}
vcf<-read.vcfR(file="outputs/1206/lg03-sea-whole-chrom.vcf")
genind<-vcfR2genind(vcf)
genind@pop<-as.factor(io$Pop)
```

```{r}
gen<-genind
X <- tab(gen, NA.method="mean")

pca1 <- dudi.pca(X,scannf=FALSE,scale=FALSE,nf=3)

df<-pca1$li
df<-df %>% bind_cols(sea)

eig<-pca1$eig/sum(pca1$eig)*100
```

```{r}
lc03pc12<-ggplot(df) + 
  geom_point(aes(x=Axis1, y=Axis2, fill=Region,), alpha=0.75, cex=2, pch=23) +
  theme_bw() +
  xlab(paste0("PC1 ",round(eig[1],2), "%")) +
  ylab(paste0("PC2 ",round(eig[2],2), "%")) +
  theme(panel.grid = element_blank()) +
  scale_fill_viridis_d(option="magma") +
  guides(fill = guide_legend(override.aes = list(pch = 22))) +
  theme(legend.position = "top")
lc03pc12

ggsave("outputs/1206/lg03-sea-whole-chrom.jpeg", width=10, height=10)
```

```{sh, eval=FALSE}
#Let's thin 
cat lg03-sea-whole-chrom.vcf | grep "#" > sea-header.txt
cat lg03-sea-whole-chrom.vcf | grep -v "#" | awk 'BEGIN{i=0}{i++;if (i%50==0) print}' > lg03-sea-thinned.vcf
cat sea-header.txt lg03-sea-thinned.vcf > lg03-sea-thinned.wheader.vcf

plink --vcf lg03-sea-thinned.wheader.vcf --r2 inter-chr --ld-window-r2 0.2 --out lg03-sea.ldf --allow-extra-chr --double-id

```

```{r}
lc03<-read.delim("outputs/1206/lg03-sea.ldf.ld",sep="",stringsAsFactors=FALSE) %>% as_tibble() %>% arrange(R2) %>% 
  filter(R2 >0.5)

ggplot(lc03) +
  geom_point(aes(x=BP_A, y=BP_B, color=R2), alpha=0.5) +
  scale_color_gradient(low="khaki1", high="red") + 
  theme_bw() 
ggsave("outputs/1206/lg03-sea-ld.jpeg")
```

Where's this peak?

```{R}
lc03 %>% filter(BP_A < 2.5e5) %>% filter(BP_B < 2.5e5)
```
Australasian fish

```{r}
vcf<-read.vcfR(file="outputs/1206/lg03-aus-whole-chrom.vcf")
genind<-vcfR2genind(vcf)
genind@pop<-as.factor(aus$Pop)
```

```{r}
gen<-genind
X <- tab(gen, NA.method="mean")

pca1 <- dudi.pca(X,scannf=FALSE,scale=FALSE,nf=3)

df<-pca1$li
df<-df %>% bind_cols(aus)

eig<-pca1$eig/sum(pca1$eig)*100
```

```{r}
lc03pc12<-ggplot(df) + 
  geom_point(aes(x=Axis1, y=Axis2, fill=Region,), alpha=0.75, cex=2, pch=23) +
  theme_bw() +
  xlab(paste0("PC1 ",round(eig[1],2), "%")) +
  ylab(paste0("PC2 ",round(eig[2],2), "%")) +
  theme(panel.grid = element_blank()) +
  scale_fill_viridis_d(option="magma") +
  guides(fill = guide_legend(override.aes = list(pch = 22))) +
  theme(legend.position = "top")
lc03pc12

ggsave("outputs/1206/lg03-aus-whole-chrom.jpeg", width=10, height=10)
```

Pop structure

```{sh, eval=FALSE}
#Let's thin 
cat lg03-aus-whole-chrom.vcf | grep "#" > aus-header.txt
cat lg03-aus-whole-chrom.vcf | grep -v "#" | awk 'BEGIN{i=0}{i++;if (i%10==0) print}' > lg03-aus-thinned.vcf
cat aus-header.txt lg03-aus-thinned.vcf > lg03-aus-thinned.wheader.vcf

plink --vcf lg03-aus-thinned.wheader.vcf --r2 inter-chr --ld-window-r2 0.2 --out lg03-aus.ldf --allow-extra-chr --double-id

```



```{r}
lc03<-read.delim("outputs/1206/lg03-aus.ldf.ld",sep="",stringsAsFactors=FALSE) %>% as_tibble() %>% arrange(R2) %>% 
  filter(R2 >0.5)

ggplot(lc03) +
  geom_point(aes(x=BP_A, y=BP_B, color=R2), alpha=0.5) +
  scale_color_gradient(low="khaki1", high="red") + 
  theme_bw()
ggsave("outputs/1206/lg03-aus-ld.jpeg")
```
### Whole chrom

First bit, subset 1:2.5e5

```{sh, eval=FALSE}
bcftools view -r NC_066835.1:1-2.5e5 outputs/1206/lg03-whole-chrom-renamed.vcf.gz | bcftools +fill-tags  -- -t MAF,F_MISSING | bcftools view -i 'F_MISSING < 0.05' | bcftools view -i 'INFO/MAF > 0.05' > outputs/1206/front.vcf
bcftools view -r NC_066835.1:2.5e5-2.0e7 outputs/1206/lg03-whole-chrom-renamed.vcf.gz | bcftools +fill-tags  -- -t MAF,F_MISSING | bcftools view -i 'F_MISSING < 0.05' | bcftools view -i 'INFO/MAF > 0.05'  > outputs/1206/back.vcf
```

```{r}
vcf<-read.vcfR(file="outputs/1206/front.vcf")
genind<-vcfR2genind(vcf)
genind@pop<-as.factor(meta$Pop)
```

```{r}
gen<-genind
X <- tab(gen, NA.method="mean")

pca1 <- dudi.pca(X,scannf=FALSE,scale=FALSE,nf=3)

df<-pca1$li
df<-df %>% bind_cols(meta)
df$Lineage<-factor(df$Lineage, levels=c("AUS+NG","Mainstream","OceanPick","SEA","IND","lakdiva"))
df$Region<-factor(df$Pop, levels=c("Queensland","Northern-Territory","Papua-New-Guinea","Mainstream","OceanPick","Indonesia-K","Indonesia-SU","Indonesia-SJ","Philippines","Taiwan","Vietnam","Cambodia","Thailand","Bangladesh","India-East-Coast","Sri-Lanka","India-West-Coast"))

eig<-pca1$eig/sum(pca1$eig)*100
```

```{r}
front<-ggplot(df) + 
  geom_point(aes(x=Axis1, y=Axis2, fill=Region, shape=Lineage), alpha=0.75, cex=2) +
  theme_bw() +
  xlab(paste0("PC1 ",round(eig[1],2), "%")) +
  ylab(paste0("PC2 ",round(eig[2],2), "%")) +
  theme(panel.grid = element_blank()) +
  scale_fill_viridis_d(option="H") +
  scale_shape_manual(values=c(21,21,21,24,23,23)) +
  guides(fill = guide_legend(override.aes = list(pch = 22))) +
  theme(legend.position = "top") +
  ggtitle("Lca03 1-2.5e5 bp") 
front

ggsave("outputs/1206/front.jpeg", width=10, height=10)
```

```{r}
vcf<-read.vcfR(file="outputs/1206/back.vcf")
genind<-vcfR2genind(vcf)
genind@pop<-as.factor(meta$Pop)
```

```{r}
gen<-genind
X <- tab(gen, NA.method="mean")

pca1 <- dudi.pca(X,scannf=FALSE,scale=FALSE,nf=3)

df<-pca1$li
df<-df %>% bind_cols(meta)
df$Lineage<-factor(df$Lineage, levels=c("AUS+NG","Mainstream","OceanPick","SEA","IND","lakdiva"))
df$Region<-factor(df$Pop, levels=c("Queensland","Northern-Territory","Papua-New-Guinea","Mainstream","OceanPick","Indonesia-K","Indonesia-SU","Indonesia-SJ","Philippines","Taiwan","Vietnam","Cambodia","Thailand","Bangladesh","India-East-Coast","Sri-Lanka","India-West-Coast"))

eig<-pca1$eig/sum(pca1$eig)*100
```

```{r}
back<-ggplot(df) + 
  geom_point(aes(x=Axis1, y=Axis2, fill=Region, shape=Lineage), alpha=0.75, cex=2) +
  theme_bw() +
  xlab(paste0("PC1 ",round(eig[1],2), "%")) +
  ylab(paste0("PC2 ",round(eig[2],2), "%")) +
  theme(panel.grid = element_blank()) +
  scale_fill_viridis_d(option="H") +
  scale_shape_manual(values=c(21,21,21,24,23,23)) +
  guides(fill = guide_legend(override.aes = list(pch = 22))) +
  theme(legend.position = "top") +
  ggtitle("Lca03 2.5e5 - 2.0e7 bp")
back

ggsave("outputs/1206/back.jpeg", width=10, height=10)
```


Check cambodia/thai labels

```{r}
ggplot(df) + 
  geom_point(aes(x=Axis1, y=Axis2, fill=Region, shape=Lineage), alpha=0.75, cex=2) +
  theme_bw() +
  geom_text_repel(data=df %>% filter(Region %in% c("Thailand","Cambodia")), aes(x=Axis1, y=Axis2, label=Run), max.overlaps = Inf) +
  xlab(paste0("PC1 ",round(eig[1],2), "%")) +
  ylab(paste0("PC2 ",round(eig[2],2), "%")) +
  theme(panel.grid = element_blank()) +
  scale_fill_viridis_d(option="H") +
  scale_shape_manual(values=c(21,21,21,24,23,23)) +
  guides(fill = guide_legend(override.aes = list(pch = 22))) +
  theme(legend.position = "top") +
  ggtitle("Lca03 2.5e5 - 2.0e7 bp") +
  facet_wrap(.~Lineage)


ggsave("outputs/1206/back-with-cambodia-labels.jpeg", width=10, height=10)
```

## Lca05

```{r}
vcf<-read.vcfR(file="outputs/1206/lg05-filtered.vcf")
genind<-vcfR2genind(vcf)
genind@pop<-as.factor(meta$Pop)
```

```{r}
gen<-genind
X <- tab(gen, NA.method="mean")

pca1 <- dudi.pca(X,scannf=FALSE,scale=FALSE,nf=3)

df<-pca1$li
df<-df %>% bind_cols(meta)
df$Lineage<-factor(df$Lineage, levels=c("AUS+NG","Mainstream","OceanPick","SEA","IND","lakdiva"))
df$Region<-factor(df$Pop, levels=c("Queensland","Northern-Territory","Papua-New-Guinea","Mainstream","OceanPick","Indonesia-K","Indonesia-SU","Indonesia-SJ","Philippines","Taiwan","Vietnam","Cambodia","Thailand","Bangladesh","India-East-Coast","Sri-Lanka","India-West-Coast"))

eig<-pca1$eig/sum(pca1$eig)*100
```

```{r}
lc05pc12<-ggplot(df) + 
  geom_point(aes(x=Axis1, y=Axis2, fill=Region, shape=Lineage), alpha=0.75, cex=2) +
  theme_bw() +
  xlab(paste0("PC1 ",round(eig[1],2), "%")) +
  ylab(paste0("PC2 ",round(eig[2],2), "%")) +
  theme(panel.grid = element_blank()) +
  scale_fill_viridis_d(option="H") +
  scale_shape_manual(values=c(21,21,21,24,23,23)) +
  guides(fill = guide_legend(override.aes = list(pch = 22))) +
  theme(legend.position = "top")
lc05pc12

ggsave("outputs/1206/lg05.jpeg", width=10, height=10)
```




## Lca20

```{r}
vcf<-read.vcfR(file="outputs/1206/lg20-filtered.vcf")
genind<-vcfR2genind(vcf)
genind@pop<-as.factor(meta$Pop)
```

```{r}
gen<-genind
X <- tab(gen, NA.method="mean")

pca1 <- dudi.pca(X,scannf=FALSE,scale=FALSE,nf=3)

df<-pca1$li
df<-df %>% bind_cols(meta)
df$Lineage<-factor(df$Lineage, levels=c("AUS+NG","Mainstream","OceanPick","SEA","IND","lakdiva"))
df$Region<-factor(df$Pop, levels=c("Queensland","Northern-Territory","Papua-New-Guinea","Mainstream","OceanPick","Indonesia-K","Indonesia-SU","Indonesia-SJ","Philippines","Taiwan","Vietnam","Cambodia","Thailand","Bangladesh","India-East-Coast","Sri-Lanka","India-West-Coast"))

eig<-pca1$eig/sum(pca1$eig)*100
```

```{r}
lc20pc12<-ggplot(df) + 
  geom_point(aes(x=Axis1, y=Axis2, fill=Region, shape=Lineage), alpha=0.75, cex=2) +
  theme_bw() +
  xlab(paste0("PC1 ",round(eig[1],2), "%")) +
  ylab(paste0("PC2 ",round(eig[2],2), "%")) +
  theme(panel.grid = element_blank()) +
  scale_fill_viridis_d(option="H") +
  scale_shape_manual(values=c(21,21,21,24,23,23)) +
  guides(fill = guide_legend(override.aes = list(pch = 22))) +
  theme(legend.position = "top")
lc20pc12

ggsave("outputs/1206/lg20.jpeg", width=10, height=10)
```


#Figure Frequencies

```{r}
data<-read_tsv("outputs/1206/lc03-haplos.txt")

df<-meta %>% left_join(data, by=c("Run"="samples")) %>%
  mutate(Genotype=ifelse(NumberRR > NumberAA & NumberRR > NumberAR, "RHom",
                       ifelse(NumberAA > NumberRR & NumberAA > NumberAR, "AHom",
                       ifelse(NumberAR > NumberAA & NumberAR > NumberRR, "Het","Other"))))
ddf<-df %>% group_by(Lineage, Region, Genotype) %>% summarise(Count=n()) %>% ungroup() %>%
  group_by(Lineage, Region) %>% mutate(Proportion=Count/sum(Count)) %>% mutate(SampleSize=sum(Count))

counts<-df %>% group_by(Genotype) %>% summarize(Count=n())
ggplot(ddf) +
  geom_col(aes(x=Region, y=Count, fill=Genotype), color="black") +
  facet_grid(.~Lineage, scales = "free_x", space="free_x") +
  scale_fill_viridis_d(option="inferno") +
  theme_bw() +
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1)) +
  theme(panel.grid = element_blank()) +
  ggtitle("lc03 Variant Frequencies\n") +
  theme(plot.title=element_text(size=14, face="bold", hjust=0.5)) +
  scale_y_continuous(breaks=c(0,5,10,15))
```

```{r}

data<-read_tsv("outputs/1206/lc05-haplos.txt")

df<-meta %>% left_join(data, by=c("Run"="samples")) %>%
  mutate(Genotype=ifelse(NumberRR > NumberAA & NumberRR > NumberAR, "RHom",
                       ifelse(NumberAA > NumberRR & NumberAA > NumberAR, "AHom",
                       ifelse(NumberAR > NumberAA & NumberAR > NumberRR, "Het","Other"))))
ddf<-df %>% group_by(Lineage, Region, Genotype) %>% summarise(Count=n()) %>% ungroup() %>%
  group_by(Lineage, Region) %>% mutate(Proportion=Count/sum(Count)) %>% mutate(SampleSize=sum(Count))

counts<-df %>% group_by(Genotype) %>% summarize(Count=n())
ggplot(ddf) +
  geom_col(aes(x=Region, y=Count, fill=Genotype), color="black") +
  facet_grid(.~Lineage, scales = "free_x", space="free_x") +
  scale_fill_viridis_d(option="inferno") +
  theme_bw() +
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1)) +
  theme(panel.grid = element_blank()) +
  ggtitle("lc05 Variant Frequencies\n") +
  theme(plot.title=element_text(size=14, face="bold", hjust=0.5)) +
  scale_y_continuous(breaks=c(0,5,10,15))

ggsave("outputs/1206/lc05-inversions.pdf")
```

```{r}

data<-read_tsv("outputs/1206/lc20-haplos.txt")

df<-meta %>% left_join(data, by=c("Run"="samples")) %>%
  mutate(Genotype=ifelse(NumberRR > NumberAA & NumberRR > NumberAR, "RHom",
                       ifelse(NumberAA > NumberRR & NumberAA > NumberAR, "AHom",
                       ifelse(NumberAR > NumberAA & NumberAR > NumberRR, "Het","Other"))))
ddf<-df %>% group_by(Lineage, Region, Genotype) %>% summarise(Count=n()) %>% ungroup() %>%
  group_by(Lineage, Region) %>% mutate(Proportion=Count/sum(Count)) %>% mutate(SampleSize=sum(Count))

counts<-df %>% group_by(Genotype) %>% summarize(Count=n())
ggplot(ddf) +
  geom_col(aes(x=Region, y=Count, fill=Genotype), color="black") +
  facet_grid(.~Lineage, scales = "free_x", space="free_x") +
  scale_fill_viridis_d(option="inferno") +
  theme_bw() +
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1)) +
  theme(panel.grid = element_blank()) +
  ggtitle("lc20 Variant Frequencies\n") +
  theme(plot.title=element_text(size=14, face="bold", hjust=0.5)) +
  scale_y_continuous(breaks=c(0,5,10,15))

ggsave("outputs/1206/lc20-inversions.pdf")

```