---
title: "1210-mtDNA"
output: html_document
date: "2025-02-12"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(tidyverse)
library(ape)
library(pegas)
library(ggtree)
library(phytools)
library(phylotools)
library(viridis)
```





need to exchange names for a network analysis.
rownames(dna)

```{r}
dna<-read.dna(file="data/vij-et-al/comb-trim.fas", format="fasta")
names<-rownames(dna) %>% as_tibble() %>% separate(value, sep = " ", into = c("Accession"))

seqm<-read_tsv("data/vij-et-al/ward-vij-data.tsv") %>% mutate(Geo=ifelse(Location=="Thailand","Thailand",
                                                                  ifelse(Location=="Taiwan","Taiwan",
                                                                  ifelse(Location %in% c("Indian West Coast","Indian East Coast","Bangladesh","Myanmar","Andaman and Nicobar Islands"),"Indian Ocean",
                                                                  ifelse(Location=="French Polynesia","French Polynesia","Other Location")))))

mdf<-left_join(names,seqm)

rownames(dna)<-mdf$Geo
```


```{r}

haps<- haplotype(dna)

net <- haploNet(haps)

ind.hap<-with(
  utils::stack(setNames(attr(haps, "index"), rownames(haps))),
  table(hap=ind, individuals=rownames(dna)[values])
 )


plot(net, size=attr(net,"freq"), fast=FALSE)
```


```{r}
pdf("outputs/1210/coi-network.pdf", width=11, height=8.5)

plot(net, size=attr(net, "freq"), scale.ratio = .5, cex = 6, pie=ind.hap, labels = FALSE,
     bg = viridis(n=length(colnames(ind.hap)), option="H"))
legend("topright",colnames(ind.hap),text.col = viridis(n=length(colnames(ind.hap)), option="H"))

dev.off()
```


## Calculation

We had access to a previous 6 samples from Thailand (Vij et al. 2014; 2016), they produced 0 I0 haplotypes. We have the same fish I think and there are 7.

We sequenced 5 samples from Thailand and found 3 IO haplotypes. The probability of sequencing six fish and not observing a IO haplotype based on the observed haplotypes we had (60%) is?

Binomial distribution:

6 flips, 0 heads (IO) as positive outcome

```{r}
dbinom(0, 7, .6)

```

Conversely, let's assume that Vij et al. were correct at the time/our data are representative

```{r}
dbinom(3,5,0)
```


Or, let's calculate them as a pooled sample

6+5=11
3 IO 

```{r}
dbinom(0,6,(3/11))
```

A 14% chance that six sequences would not reveal an IO haplotype if the chance is 3/11.