---
title: "1301-uwisara"
output: html_document
date: "2025-04-07"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(tidyverse)
```

putting in data/uwisara

-at some point I can clean up the farm a bit

Two lanes of each, that should be combined. 

1613156
1613186
1613217
1613247

```{sh, eval=FALSE}
#checksums
 maccamp@farm:~/lates-wgs/data/uwisara/AGRF_NXGSQCAGRF24120169-1_22YMCCLT3$ for f in *.fastq.gz; do echo $f; md5sum $f  >> md5s.txt; done;

cat AGRF_NXGSQCAGRF24120169-1_22YMCCLT3/1613156_22YMCCLT3_TTGGACATCG-GAATCTGGTC_L007_R1.fastq.gz AGRF_NXGSQCAGRF24120169-1_22YMCCLT3/1613156_22YMCCLT3_TTGGACATCG-GAATCTGGTC_L008_R1.fastq.gz > 1613156-R1.fastq.gz

cat AGRF_NXGSQCAGRF24120169-1_22YMCCLT3/1613156_22YMCCLT3_TTGGACATCG-GAATCTGGTC_L007_R2.fastq.gz AGRF_NXGSQCAGRF24120169-1_22YMCCLT3/1613156_22YMCCLT3_TTGGACATCG-GAATCTGGTC_L008_R2.fastq.gz > 1613156-R2.fastq.gz

cat AGRF_NXGSQCAGRF24120169-1_22YMCCLT3/1613186_22YMCCLT3_AACGTTGAGA-CGGTCGGTAA_L007_R1.fastq.gz AGRF_NXGSQCAGRF24120169-1_22YMCCLT3/1613186_22YMCCLT3_AACGTTGAGA-CGGTCGGTAA_L008_R1.fastq.gz > 1613186-fastq.gz

cat AGRF_NXGSQCAGRF24120169-1_22YMCCLT3/1613186_22YMCCLT3_AACGTTGAGA-CGGTCGGTAA_L007_R2.fastq.gz AGRF_NXGSQCAGRF24120169-1_22YMCCLT3/1613186_22YMCCLT3_AACGTTGAGA-CGGTCGGTAA_L008_R2.fastq.gz > 1613186-R2.fastq.gz

cat AGRF_NXGSQCAGRF24120169-1_22YMCCLT3/1613217_22YMCCLT3_GGCCAGTGAA-TCTGCTAATG_L007_R1.fastq.gz AGRF_NXGSQCAGRF24120169-1_22YMCCLT3/1613217_22YMCCLT3_GGCCAGTGAA-TCTGCTAATG_L008_R1.fastq.gz > 1613217-R1.fastq.gz

cat AGRF_NXGSQCAGRF24120169-1_22YMCCLT3/1613217_22YMCCLT3_GGCCAGTGAA-TCTGCTAATG_L007_R2.fastq.gz AGRF_NXGSQCAGRF24120169-1_22YMCCLT3/1613217_22YMCCLT3_GGCCAGTGAA-TCTGCTAATG_L008_R2.fastq.gz > 1613217-R2.fastq.gz

cat AGRF_NXGSQCAGRF24120169-1_22YMCCLT3/1613247_22YMCCLT3_ATGTCTCCGG-CTCTTATTCG_L007_R1.fastq.gz AGRF_NXGSQCAGRF24120169-1_22YMCCLT3/1613247_22YMCCLT3_ATGTCTCCGG-CTCTTATTCG_L008_R1.fastq.gz > 1613247-R1.fastq.gz

cat AGRF_NXGSQCAGRF24120169-1_22YMCCLT3/1613247_22YMCCLT3_ATGTCTCCGG-CTCTTATTCG_L007_R2.fastq.gz AGRF_NXGSQCAGRF24120169-1_22YMCCLT3/1613247_22YMCCLT3_ATGTCTCCGG-CTCTTATTCG_L008_R2.fastq.gz > 1613247-R2.fastq.gz

```

bash ../../doAlign-zipped.sh to-align.txt /home/maccamp/lates-wgs/genome/GCF_001640805.2_TLL_Latcal_v3_genomic.fna.gz

```{r}
m118<-read_csv("meta/m118.csv")
m118 %>% select(NewPath) %>% write_tsv("bamlists/118.bamlist", col_names = FALSE)
down<-m118 %>% filter(Region=="Myanmar") %>% mutate(Frac=7/Coverage) %>%
  mutate(Command = paste0("samtools view -bs ", Frac, " ", "data/uwisara/",Run,".sort.flt.bam", " > ",   "/home/maccamp/lates-wgs/data/downsample/", Run, ".reduced.bam ;"," samtools index ", "/home/maccamp/lates-wgs/data/downsample/", Run, ".reduced.bam ;")) 
down %>% select(Command)
 down %>% select(Command) %>% write_tsv(file="1301.1-downsample.sh", col_names = FALSE)
```

# Trial of Chromosome 1 to visualize PCA of all samples.

need a bamlist

srun -p high -t 16:00:00 --mem=32G --nodes=1 --cpus-per-task=6  $HOME/angsd/angsd -P 6  \
-bam bamlists/188.bamlist -r NC_066833.1 \
-ref  genome/GCF_001640805.2_TLL_Latcal_v3_genomic.fna \
-minInd 106 -minMapQ 20 -minQ 20 -GL 2 -doGLF 2 \
-doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 \
-doIBS 1 -doCounts 1 -doCov 1 -makeMatrix 1 -minMaf 0.05 \
-out outputs/1301/118-ibs-90 > outputs/1301/118-ibs-90.out 2> outputs/1301/118-ibs-90.err &

