---
title: "1400-wa"
output: html_document
date: "2026-01-28"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(tidyverse)
library(ggrepel)
```

Received new samples from WA, Fitzroy River and Cambridge Gulf. Need to check checksums and merge data, align, etc.

Don't forget to md5sum -c checksums.md5.     
`srun -p bmh -t 12:00:00 --mem=32G --nodes=1 --ntasks-per-node=1 --cpus-per-task=2 md5sum -c checksums.md5 > check.out 2> check.err`.     
cat check.out returns all OK status.       

Manually combining, don't ask me why.    

```{sh, eval=FALSE}
cat AGRF_NXGSQCAGRF25120123-1_23GGJFLT3/FIT-45*R1.fastq.gz > Fitzroy45-R1.fastq.gz
cat AGRF_NXGSQCAGRF25120123-1_23GGJFLT3/FIT-45*R2.fastq.gz > Fitzroy45-R2.fastq.gz

cat AGRF_NXGSQCAGRF25120123-1_23GGJFLT3/FIT-47*R1.fastq.gz > Fitzroy47-R1.fastq.gz
cat AGRF_NXGSQCAGRF25120123-1_23GGJFLT3/FIT-47*R2.fastq.gz > Fitzroy47-R2.fastq.gz

cat AGRF_NXGSQCAGRF25120123-1_23GGJFLT3/WAF-003767*R1.fastq.gz > WAF003767-R1.fastq.gz
cat AGRF_NXGSQCAGRF25120123-1_23GGJFLT3/WAF-003767*R2.fastq.gz > WAF003767-R2.fastq.gz

cat AGRF_NXGSQCAGRF25120123-1_23GGJFLT3/WAF-003768*R1.fastq.gz > WAF003768-R1.fastq.gz
cat AGRF_NXGSQCAGRF25120123-1_23GGJFLT3/WAF-003768*R2.fastq.gz > WAF003768-R2.fastq.gz

cat AGRF_NXGSQCAGRF25120123-1_23GGJFLT3/WAF-003770*R1.fastq.gz > WAF003770-R1.fastq.gz
cat AGRF_NXGSQCAGRF25120123-1_23GGJFLT3/WAF-003770*R2.fastq.gz > WAF003770-R2.fastq.gz

cat AGRF_NXGSQCAGRF25120123-1_23GGJFLT3/WAF-003774*R1.fastq.gz > WAF003774-R1.fastq.gz
cat AGRF_NXGSQCAGRF25120123-1_23GGJFLT3/WAF-003774*R2.fastq.gz > WAF003774-R2.fastq.gz

cat AGRF_NXGSQCAGRF25120123-1_23GGJFLT3/WAF-003775*R1.fastq.gz > WAF003775-R1.fastq.gz
cat AGRF_NXGSQCAGRF25120123-1_23GGJFLT3/WAF-003775*R2.fastq.gz > WAF003775-R2.fastq.gz

cat AGRF_NXGSQCAGRF25120123-1_23GGJFLT3/WAF-003776*R1.fastq.gz > WAF003776-R1.fastq.gz
cat AGRF_NXGSQCAGRF25120123-1_23GGJFLT3/WAF-003776*R2.fastq.gz > WAF003776-R2.fastq.gz

cat AGRF_NXGSQCAGRF25120123-1_23GGJFLT3/WAF-004001*R1.fastq.gz > WAF004001-R1.fastq.gz
cat AGRF_NXGSQCAGRF25120123-1_23GGJFLT3/WAF-004001*R2.fastq.gz > WAF004001-R2.fastq.gz

cat AGRF_NXGSQCAGRF25120123-1_23GGJFLT3/WAF-004002*R1.fastq.gz > WAF004002-R1.fastq.gz
cat AGRF_NXGSQCAGRF25120123-1_23GGJFLT3/WAF-004002*R2.fastq.gz > WAF004002-R2.fastq.gz

cat AGRF_NXGSQCAGRF25120123-1_23GGJFLT3/WAF-004003*R1.fastq.gz > WAF004003-R1.fastq.gz
cat AGRF_NXGSQCAGRF25120123-1_23GGJFLT3/WAF-004003*R2.fastq.gz > WAF004003-R2.fastq.gz

cat AGRF_NXGSQCAGRF25120123-1_23GGJFLT3/WAF-004008*R1.fastq.gz > WAF004008-R1.fastq.gz
cat AGRF_NXGSQCAGRF25120123-1_23GGJFLT3/WAF-004008*R2.fastq.gz > WAF004008-R2.fastq.gz

cat AGRF_NXGSQCAGRF25120123-1_23GGJFLT3/WAF-004014*R1.fastq.gz > WAF004014-R1.fastq.gz
cat AGRF_NXGSQCAGRF25120123-1_23GGJFLT3/WAF-004014*R2.fastq.gz > WAF004014-R2.fastq.gz
```


Need to align, but the options have changed! Edited do-align.sh.       

```{sh, eval=FALSE}
ls | grep R1 > forward
ls | grep R2 > reverse
ls | grep R1 | perl -pe s'/-R1.fastq.gz//g' > names.txt
paste forward reverse names.txt > to-align.txt
bash ../../do-align.sh to-align.txt /home/maccamp/lates-wgs/genome/GCF_001640805.2_TLL_Latcal_v3_genomic.fna.gz
```

Can downsample if needed 


# meta

```{r}
meta<-read_csv("meta/m164.csv") 
summary<-meta %>% group_by(Region, Locality) %>% summarize(`Sample Size`=n())
locs<-read_tsv("outputs/range-map/points-edited-4.tsv")
points<-summary %>% left_join(locs)
points$Lineage<-factor(points$Lineage, levels=c("IND","uwisara","lakdiva","SEA","WAL","AUS"))
points
```

```{r}
names<-read_tsv("meta/existing-names.tsv")
names
```
```{r}
ggplot() +
  geom_point(data=names, aes(x=Longitude, y=Latitude)) +
  geom_text_repel(data=names, aes(x=Longitude, y=Latitude, label=paste0(Name, " ", Authority)))
```

Dropping 81.37789136152588	8.467975090691	WGS	Trinco	green	23	IND	Sri Lankan Aquaculture	Sri Lankan Aquaculture

```{r}
ggplot() +
  geom_point(data=points, aes(x=long, y=lat, size=`Sample Size`,fill=Lineage), pch=21, alpha=0.75) +
  geom_point(data=names, aes(x=Longitude, y=Latitude), pch=15) +
  geom_text_repel(data=names, aes(x=Longitude, y=Latitude, label=paste0(Name, "\n", Authority)), size=3) +
  scale_size_continuous(breaks=c(1,5,10)) +
  scale_fill_viridis_d(option="H") 

ggsave("outputs/1400/sampling-map-with-names.pdf", width=12, height=8.5)
```



```{r, eval=FALSE}
load("data/earth/world-rast.rda")

earth<-ggplot() +
  geom_raster(data = rast.table, mapping = aes(x = x, y = y), fill = rast.table$rgb, interpolate = TRUE)  +
  geom_rect(aes(xmin=55, xmax=55+degrees,ymin=-1, ymax=1), fill="white", color="black") +
  geom_rect(aes(xmin=55+degrees, xmax=55+(2*degrees), ymin=-1, ymax=1), fill="black", color="black") +
  ylab("Latitude\n") +
  xlab("\nLongitude") +
  theme_bw() +
  theme(panel.grid=element_blank()) +
  theme(axis.text=element_text(color="black", size=12)) +
  theme(axis.title=element_text(color="black", face="bold", size=14))

earth+geom_point(data=points, aes(x=long, y=lat, size=`Sample Size`,fill=Lineage), pch=21, alpha=0.75) +
  geom_point(data=names, aes(x=Longitude, y=Latitude), pch=15) +
  geom_text_repel(data=names, aes(x=Longitude, y=Latitude, label=paste0(Name, "\n", Authority)), size=3) +
  scale_size_continuous(breaks=c(1,5,10)) +
  scale_fill_viridis_d(option="H")

ggsave("outputs/1400/sampling-map.pdf", width=12, height=8.5)
```

# Downsample


```{r}
down<-meta %>% filter(Locality %in% c("Fitzroy River WA-Historical","Fitzroy River WA","Cambridge Gulf")) %>% filter(Coverage > 7) %>% mutate(Frac=7/Coverage) %>% filter(Run !="Fitzroy01") %>%
  mutate(Command = paste0("samtools view -bs ", Frac, " ", Path, " > ",   "/home/maccamp/lates-wgs/data/downsample/", Run, ".reduced.bam ;"," samtools index ", "/home/maccamp/lates-wgs/data/downsample/", Run, ".reduced.bam ;")) 
down %>% select(Command) %>% write_tsv(file="1400.1-downsample.sh", col_names = FALSE)
```

```{sh, eval=FALSE}
module load parallel
srun -p bmh -t 4:00:00 --mem=32G --nodes=1 --ntasks-per-node=1 --cpus-per-task=12 parallel -j 12 < 1400.1-downsample.sh
```


```{r}
m90<-meta %>% filter(Run !="WAF011639") %>% filter(Region != "Australian Aquaculture") %>% filter(Region !="Sri Lankan Aquaculture") %>% 
  filter( Locality %in% c("DeGrey River","Broome","Fitzroy River WA","Fitzroy River WA-Historical","Cambridge Gulf","Daly River","Darwin Harbour","Roper River","Tully Inlet","Fly River","Hinchinbrook Channel", "Fitzroy River QLD","Samarinda","Sulawesi","Tamsui River"))
m90$Locality<-factor(m90$Locality, levels=c("DeGrey River","Broome","Fitzroy River WA","Fitzroy River WA-Historical","Cambridge Gulf","Daly River","Darwin Harbour","Roper River","Tully Inlet","Fly River","Hinchinbrook Channel", "Fitzroy River QLD","Samarinda","Sulawesi","Tamsui River") )

m90 %>% select(NewPath) %>% write_tsv(file="bamlists/90.bamlist", col_names = FALSE)
m90 %>% select(Run) %>% write_tsv(file="bamlists/90.names", col_names = FALSE)

m89<-m90 %>% filter(Run!="WAF003776")
m89 %>% select(NewPath) %>% write_tsv(file="bamlists/89.bamlist", col_names = FALSE)
m89 %>% select(Run) %>% write_tsv(file="bamlists/89.names", col_names = FALSE)

```

One chrom GLs for sanity

```{sh, eval=FALSE}
srun -p bmh -t 5:00:00 --mem=32G --nodes=1 --cpus-per-task=12  $HOME/angsd/angsd -P 12  \
-bam bamlists/90.bamlist -r NC_066833.1 \
-ref genome/GCF_001640805.2_TLL_Latcal_v3_genomic.fna \
-minInd 81 -minMapQ 20 -minQ 20 -GL 2 -doGLF 2 \
-doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 \
-doIBS 1 -doCounts 1 -doCov 1 -makeMatrix 1 -minMaf 0.05 \
-out outputs/1400/ibs-90-Lcal01 > outputs/1400/ibs-90-Lcal01.out 2> outputs/1400/ibs-90-Lcal01.err &

```

	-> Number of sites retained after filtering: 92652 


```{r}
m <- as.matrix(read.table("outputs/1400/ibs-90-Lcal01.covMat"))
eig <- eigen(m)
var<-eig$values/sum(eig$values)
cumvar<-cumsum(eig$values)/sum(eig$values)

head(var)
head(cumvar)

vdf<-var %>% as_tibble() %>% rename(Variance=value) %>% mutate(PC=1:n()) %>% head(n=10)

scree<-ggplot(vdf) +
  geom_line(aes(x=PC, y=Variance)) +
  theme_bw() +
  theme(panel.grid = element_blank()) +
  scale_x_continuous(breaks=vdf$PC) +
  theme(axis.text=element_text(size=8)) +
  ggtitle("Scree Plot") +
  theme(plot.title = element_text(hjust=0.5, face="bold"))

scree
ggsave("outputs/1400/chrom01-scree-plot.jpeg")
```


```{r}
meta<-m90
covs<-eig$vectors[,1:4] %>% as_tibble() %>% bind_cols(meta)

text12<-covs %>% select(Run, Region, V1, V2) %>%
  group_by(Region) %>% summarize(Count=n(), x=mean(V1), y=mean(V2))

text12L<-covs %>% select(Run, Locality, V1, V2) %>%
  group_by(Locality) %>% summarize(Count=n(), x=mean(V1), y=mean(V2))

pc12<-ggplot(covs) +
  geom_point(aes(x=V1, y=V2, fill=Locality), pch=21, alpha=0.75, cex=2) +
  #  geom_text(aes(x=V1, y=V2, label=Run), pch=21, alpha=0.75, cex=2) +
  geom_text_repel(data=text12, aes(x=x, y=y, label=Region), max.overlaps = Inf) +
 # geom_text_repel(data=text12L, aes(x=x, y=y, label=Locality), size=3, max.overlaps = Inf) +
  xlab(paste("PC1", " ", round((100*var[1]),2), "%", sep = "")) +
  ylab(paste("PC2", " ", round((100*var[2]),2), "%", sep = "")) +
  theme_bw() +
  theme(panel.grid=element_blank()) +
  scale_fill_viridis_d(option="C") +
  ggtitle("PCs 1 and 2") +
  theme(plot.title = element_text(hjust=0.5, face="bold")) +
  theme(legend.position = "none")

pc12
ggsave("outputs/1400/chrom01-lates-pc12.jpeg", width=6, height=6)
ggsave("outputs/1400/chrom01-lates-pc12.pdf", width=6, height=6)

```

0.230  -0.211   -0.0361  0.795    WAF0… WAF003776

Its a stinker!  Time to drop it

```{r}
text13<-covs %>% select(Run, Region, V1, V3) %>%
  group_by(Region) %>% summarize(Count=n(), x=mean(V1), y=mean(V3))

text13L<-covs %>% select(Run, Locality, V1, V3) %>%
  group_by(Locality) %>% summarize(Count=n(), x=mean(V1), y=mean(V3))

pc13<-ggplot(covs) +
  geom_point(aes(x=V1, y=V3, fill=Locality), pch=21, alpha=0.75, cex=2) +
  #  geom_text(aes(x=V1, y=V2, label=Run), pch=21, alpha=0.75, cex=2) +
  geom_text_repel(data=text13, aes(x=x, y=y, label=Region), max.overlaps = Inf) +
 # geom_text_repel(data=text13L, aes(x=x, y=y, label=Locality), size=3, max.overlaps = Inf) +
  xlab(paste("PC1", " ", round((100*var[1]),2), "%", sep = "")) +
  ylab(paste("PC3", " ", round((100*var[3]),2), "%", sep = "")) +
  theme_bw() +
  theme(panel.grid=element_blank()) +
  scale_fill_viridis_d(option="C") +
  ggtitle("PCs 1 and 3") +
  theme(plot.title = element_text(hjust=0.5, face="bold")) +
  theme(legend.position = "none")

pc13
```

# Calls

Excluding inversion zones

```{sh, eval=FALSE}
srun -t 48:00:00 -p bmh --mem=32G --nodes=1 --ntasks-per-node=1 --cpus-per-task=12 $HOME/angsd/angsd -nthreads 12 \
-minInd 81 -bam bamlists/90.bamlist -ref genome/GCF_001640805.2_TLL_Latcal_v3_genomic.fna \
-rf  meta/no-inv.txt -out outputs/1400/snps-wgs-01-glf  \
-minMaf 0.01 -minMapQ 20 -minQ 20 -GL 1 -doGLF 2 -doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 \
-doGeno 2 -doPost 1 -postCutoff 0.9 -doPlink 2  > outputs/1400/snps-wgs-01-glf.out 2> outputs/1400/snps-wgs-01-glf.err &
```

	-> Number of sites retained after filtering: 11383714 


```{sh}
plink --tped snps-wgs-01-glf.tped --tfam snps-wgs-01-glf.tfam  --out plink-binary-01 --recode --allow-extra-chr --noweb
plink --ped plink-binary-01.ped --map plink-binary-01.map --recode vcf --allow-extra-chr -out plink-01
bgzip plink-01.vcf 
tabix plink-01.vcf.gz

#renaming vcf bcftools/1.13
module load bcftools

bcftools reheader --samples bamlists/90.names -o outputs/1400/renamed-01-90.vcf.gz outputs/1400/plink-01.vcf.gz
bcftools view --samples bamlists/89.names -o outputs/1400/renamed-01.vcf.gz outputs/1400/renamed-01-90.vcf.gz

bcftools +fill-tags outputs/1400/renamed-01.vcf.gz  -- -t MAF,F_MISSING | bcftools view -i 'F_MISSING < 0.05' | bcftools view -i 'INFO/MAF > 0.05' | bcftools view -i 'INFO/MAF < 0.45' |  bcftools +prune -m 0.20 -w 50kb --nsites-per-win 1 --nsites-per-win-mode rand  > outputs/1400/pruned-01-maf05-45.vcf

bcftools +fill-tags outputs/1400/renamed-01.vcf.gz  -- -t MAF,F_MISSING | bcftools view -i 'F_MISSING < 0.05' | bcftools view -i 'INFO/MAF > 0.01' | bcftools view -i 'INFO/MAF < 0.45' |  bcftools +prune -m 0.20 -w 50kb --nsites-per-win 1 --nsites-per-win-mode rand  > outputs/1400/pruned-01-maf01-45.vcf

bcftools +fill-tags outputs/1400/renamed-01.vcf.gz  -- -t MAF,F_MISSING | bcftools view -i 'F_MISSING < 0.05' | bcftools view -i 'INFO/MAF > 0.10' | bcftools view -i 'INFO/MAF < 0.45' |  bcftools +prune -m 0.20 -w 50kb --nsites-per-win 1 --nsites-per-win-mode rand  > outputs/1400/pruned-01-maf10-45.vcf

bcftools +fill-tags outputs/1400/renamed-01.vcf.gz  -- -t MAF,F_MISSING | bcftools view -i 'F_MISSING < 0.05' | bcftools view -i 'INFO/MAF > 0.10' | bcftools view -i 'INFO/MAF < 0.45' |  bcftools +prune -m 0.20 -w 50kb --nsites-per-win 1 --nsites-per-win-mode maxAF  > outputs/1400/pruned-01-maf10-45-max.vcf



#Convert to phylip and then to nex
conda activate py2;

~/github/mccloud-rrt/vcf2phylip.py -i pruned-01-maf01-45.vcf;
~/github/mccloud-rrt/vcf2phylip.py -i pruned-01-maf05-45.vcf;
~/github/mccloud-rrt/vcf2phylip.py -i pruned-01-maf10-45-max.vcf;
~/github/mccloud-rrt/vcf2phylip.py -i pruned-01-maf10-45.vcf;

conda deactivate;
```
