---
title: "1401-taxonomy"
output: html_document
date: "2026-03-02"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(ape)
library(phangorn)
library(tidyverse)
library(pcadapt)
library(ggpubr)
library(grid)
library(ggrepel)
library(ggtree)
library(tanggle)
```


Have a comprehensive data set, but am including two L. japonicus

Need to dump one and align.    
```{sh, eval=FALSE}
module load sratoolkit
fastq-dump --outdir split --skip-technical --read-filter pass --dumpbase --split-3 --gzip --clip DRR397260.lite.1.1

# in data/split
bash ../../../do-align.sh to-align.txt /home/maccamp/lates-wgs/genome/GCF_001640805.2_TLL_Latcal_v3_genomic.fna.gz

# downsample to 20x to match other sample 20/110.53=0.1809463
srun -p bmh -t 24:00:00 --mem=32G --nodes=1 samtools view -bs 0.1809463  /home/maccamp/lates-wgs/data/japonicus/split/DRR397260.sort.flt.bam > /home/maccamp/lates-wgs/data/downsample/DRR397260.reduced.bam
samtools index /home/maccamp/lates-wgs/data/downsample/DRR397260.reduced.bam
```

Goal - created rooted phylogenetic tree of samples. Can use svd quartets

_1_ Create bamlist excluding aquaculture samples 

Broome01 is odd in behavior as well
Can excluded taiwanese admixed fish

```{r}
meta<-read_csv("meta/m164.csv") %>% filter(Run !="WAF011639") %>% filter(Run !="WAF003776") %>% filter(Run !="Broome01") %>% filter(Region != "Australian Aquaculture") %>% filter(Region !="Sri Lankan Aquaculture")  

meta$Lineage<-factor(meta$Lineage, levels=c("IND","uwisara","lakdiva","SEA","WAL","AUS","japonicus"))

summary<-meta %>% group_by(Region, Locality, Lineage) %>% summarize(`Sample Size`=n())
locs<-read_tsv("outputs/range-map/points-edited-4.tsv")
points<-summary %>% left_join(locs)
points$Lineage<-factor(points$Lineage, levels=c("IND","uwisara","lakdiva","SEA","WAL","AUS","japonicus"))
points
```

```{r}
m141<-meta
m141 %>% write_csv("meta/taxonomy-paper.csv")
m141 %>% dplyr::select(NewPath) %>% write_tsv("bamlists/141.bamlist", col_names = FALSE)
m141 %>% dplyr::select(Run) %>% write_tsv("bamlists/141.names", col_names = FALSE)

nometa<-meta %>% filter(Lineage !="japonicus")
nometa %>% dplyr::select(NewPath) %>% write_tsv("bamlists/139.bamlist", col_names = FALSE)
nometa %>% dplyr::select(Run) %>% write_tsv("bamlists/139.names", col_names = FALSE)

```

 levels=c("DeGrey River","Broome","Fitzroy River WA","Fitzroy River WA-Historical","Cambridge Gulf","Daly River","Darwin Harbour","Roper River","Tully Inlet","Fly River","Hinchinbrook Channel", "Fitzroy River QLD","Samarinda","Sulawesi","Tamsui River") )

_2_ One chrom GLs for sanity

One chrom GLs for sanity

```{sh, eval=FALSE}
srun -p bmh -t 5:00:00 --mem=32G --nodes=1 --cpus-per-task=12  $HOME/angsd/angsd -P 12  \
-bam bamlists/139.bamlist -r NC_066833.1 \
-ref genome/GCF_001640805.2_TLL_Latcal_v3_genomic.fna \
-minInd 125 -minMapQ 20 -minQ 20 -GL 2 -doGLF 2 \
-doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 \
-doIBS 1 -doCounts 1 -doCov 1 -makeMatrix 1 -minMaf 0.05 \
-out outputs/1401/ibs-90-Lcal01 > outputs/1401/ibs-90-Lcal01.out 2> outputs/1401/ibs-90-Lcal01.err &
```

	-> Number of sites retained after filtering: 580629 at maf=0.01.        
	-> Number of sites retained after filtering: 147600 at maf=0.05.    

6/139 = 0.04, so maf < 0.05 won't produce unique variants in some pops. Setting maf initially to 0.01. Very noisy PCA, trying again at 0.05.     

Should try 0.01, 0.05 and 0.10 for phylogenies though, using rand when pruning and maxAF options.


```{r}
m <- as.matrix(read.table("outputs/1401/ibs-90-Lcal01.covMat"))
eig <- eigen(m)
var<-eig$values/sum(eig$values)
cumvar<-cumsum(eig$values)/sum(eig$values)

head(var)
head(cumvar)

vdf<-var %>% as_tibble() %>% rename(Variance=value) %>% mutate(PC=1:n()) %>% head(n=10)

scree<-ggplot(vdf) +
  geom_line(aes(x=PC, y=Variance)) +
  theme_bw() +
  theme(panel.grid = element_blank()) +
  scale_x_continuous(breaks=vdf$PC) +
  theme(axis.text=element_text(size=8)) +
  ggtitle("Scree Plot") +
  theme(plot.title = element_text(hjust=0.5, face="bold"))

scree
ggsave("outputs/1401/chrom01-scree-plot.jpeg")
```


```{r}
meta<-nometa
covs<-eig$vectors[,1:4] %>% as_tibble() %>% bind_cols(meta)

text12<-covs %>% dplyr::select(Run, Region, V1, V2) %>%
  group_by(Region) %>% summarize(Count=n(), x=mean(V1), y=mean(V2))

text12L<-covs %>% dplyr::select(Run, Locality, V1, V2) %>%
  group_by(Locality) %>% summarize(Count=n(), x=mean(V1), y=mean(V2))

pc12<-ggplot(covs) +
  geom_point(aes(x=V1, y=V2, fill=Lineage), pch=21, alpha=0.75, cex=2) +
  #  geom_text(aes(x=V1, y=V2, label=Run), pch=21, alpha=0.75, cex=2) +
  geom_text_repel(data=text12, aes(x=x, y=y, label=Region), max.overlaps = Inf) +
 # geom_text_repel(data=text12L, aes(x=x, y=y, label=Locality), size=3, max.overlaps = Inf) +
  xlab(paste("PC1", " ", round((100*var[1]),2), "%", sep = "")) +
  ylab(paste("PC2", " ", round((100*var[2]),2), "%", sep = "")) +
  theme_bw() +
  theme(panel.grid=element_blank()) +
  scale_fill_viridis_d(option="H") +
  ggtitle("PCs 1 and 2") +
  theme(plot.title = element_text(hjust=0.5, face="bold")) 
#  theme(legend.position = "none")

pc12
ggsave("outputs/1401/chrom01-lates-pc12.jpeg", width=6, height=6)
ggsave("outputs/1401/chrom01-lates-pc12.pdf", width=6, height=6)

```

_3_ Calls

# Calls

Excluding inversion zones

```{sh, eval=FALSE}
srun -t 48:00:00 -p bmh --mem=32G --nodes=1 --ntasks-per-node=1 --cpus-per-task=12 $HOME/angsd/angsd -nthreads 12 \
-minInd 127 -bam bamlists/141.bamlist -ref genome/GCF_001640805.2_TLL_Latcal_v3_genomic.fna \
-rf  meta/no-inv.txt -out outputs/1401/snps-wgs-01-glf  \
-minMaf 0.01 -minMapQ 20 -minQ 20 -GL 1 -doGLF 2 -doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 \
-doGeno 2 -doPost 1 -postCutoff 0.9 -doPlink 2  > outputs/1401/snps-wgs-01-glf.out 2> outputs/1401/snps-wgs-01-glf.err &
```

	-> Number of sites retained after filtering: 19024878 


```{sh, eval=FALSE}
plink --tped snps-wgs-01-glf.tped --tfam snps-wgs-01-glf.tfam  --out plink-binary-01 --recode --allow-extra-chr --noweb
plink --ped plink-binary-01.ped --map plink-binary-01.map --recode vcf --allow-extra-chr -out plink-01
bgzip plink-01.vcf 
tabix plink-01.vcf.gz

#renaming vcf bcftools/1.13
module load bcftools

bcftools reheader --samples bamlists/141.names -o outputs/1401/renamed-01.vcf.gz outputs/1401/plink-01.vcf.gz
#bcftools view -S bamlists/89.names -o outputs/1401/renamed-01.vcf.gz outputs/1401/renamed-01-90.vcf.gz

bcftools +fill-tags outputs/1401/renamed-01.vcf.gz  -- -t MAF,F_MISSING | bcftools view -i 'F_MISSING < 0.05' | bcftools view -i 'INFO/MAF > 0.01' | bcftools view -i 'INFO/MAF < 0.45' |  bcftools +prune -m 0.20 -w 50kb --nsites-per-win 1 --nsites-per-win-mode rand  > outputs/1401/pruned-01-maf01-45.vcf

bcftools +fill-tags outputs/1401/renamed-01.vcf.gz  -- -t MAF,F_MISSING | bcftools view -i 'F_MISSING < 0.05' | bcftools view -i 'INFO/MAF > 0.05' | bcftools view -i 'INFO/MAF < 0.45' |  bcftools +prune -m 0.20 -w 50kb --nsites-per-win 1 --nsites-per-win-mode rand  > outputs/1401/pruned-01-maf05-45.vcf

bcftools +fill-tags outputs/1401/renamed-01.vcf.gz  -- -t MAF,F_MISSING | bcftools view -i 'F_MISSING < 0.05' | bcftools view -i 'INFO/MAF > 0.10' | bcftools view -i 'INFO/MAF < 0.45' |  bcftools +prune -m 0.20 -w 50kb --nsites-per-win 1 --nsites-per-win-mode rand  > outputs/1401/pruned-01-maf10-45.vcf

bcftools +fill-tags outputs/1401/renamed-01.vcf.gz  -- -t MAF,F_MISSING | bcftools view -i 'F_MISSING < 0.05' | bcftools view -i 'INFO/MAF > 0.10' | bcftools view -i 'INFO/MAF < 0.45' |  bcftools +prune -m 0.20 -w 50kb --nsites-per-win 1 --nsites-per-win-mode maxAF  > outputs/1401/pruned-01-maf10-45-max.vcf


#Convert to phylip and then to nex
conda activate py27;

~/mccloud-rrt/vcf2phylip.py -i pruned-01-maf01-45.vcf;
~/mccloud-rrt/vcf2phylip.py -i pruned-01-maf05-45.vcf;
~/mccloud-rrt/vcf2phylip.py -i pruned-01-maf10-45-max.vcf;
~/mccloud-rrt/vcf2phylip.py -i pruned-01-maf10-45.vcf;

conda deactivate
```

_4_ Network
```{r}
dat<-read.dna(file="outputs/1401/maf01/pruned-01-maf01-45.min4.phy")
write.nexus.data(dat, file="outputs/1401/maf01/pruned-01-maf01-45.min4.nex")


dat<-read.dna(file="outputs/1401/maf05/pruned-01-maf05-45.min4.phy")
write.nexus.data(dat, file="outputs/1401/maf05/pruned-01-maf05-45.min4.nex")

dat<-read.dna(file="outputs/1401/maf10-max/pruned-01-maf10-45-max.min4.phy")
write.nexus.data(dat, file="outputs/1401/maf10-max/pruned-01-maf10-45-max.min4.nex")

dat<-read.dna(file="outputs/1401/maf10-rand/pruned-01-maf10-45.min4.phy")
write.nexus.data(dat, file="outputs/1401/maf10-rand/pruned-01-maf10-45.min4.nex")
```


```{r}
net<-read.nexus.networx("outputs/1401/maf05/pruned-01-maf05-45.min4.network")
#net<-read.nexus.networx("outputs/1401/maf01/pruned-01-maf01-45.min4.network")
#net<-read.nexus.networx("outputs/1401/maf10-max/pruned-01-maf10-45-max.network")

m<-m141
```

```{r}
g<-ggsplitnet(net, color="black")  
g$data<-left_join(g$data, m, by=c("label"="Run")) 

n<-g + 
  geom_tippoint(aes(fill=Lineage), cex=5, alpha=1.00, pch=21) +
  scale_fill_viridis_d(option="H") +
  guides(fill = guide_legend(override.aes = list(pch = 22))) +
#  theme(legend.position = "none") +
  theme(panel.grid=element_blank())
  #theme(panel.background = element_rect(fill="black", color="black")) +
  #theme(plot.background = element_rect(fill="black", color="black")) +
  #theme(legend.background =element_rect(fill="black", color="black"), legend.text = element_text(color="white"), legend.title = element_text(color="white")) +
  #theme(axis.text=element_text(color="white", size=12)) +
  #theme(axis.title=element_text(color="white", face="bold", size=14))  +
 # theme(legend.position = "none")
  
  
  #color white and black
n


```

_5_ Ml tree


```{sh, eval=FALSE}
iqtree2  -nt AUTO -m MFP+ASC -bb 1000 -s pruned-01-maf10-45-max.min4.phy --seqtype DNA --redo
iqtree2  -nt AUTO -m MFP+ASC -bb 10000 -s pruned-01-maf10-45-max.min4.phy.varsites.phy --seqtype DNA --redo

iqtree2  -nt AUTO -m MFP+ASC -bb 1000 -s pruned-01-maf01-45.min4.phy --seqtype DNA --redo
iqtree2  -nt AUTO -m MFP+ASC -bb 10000 -s pruned-01-maf01-45.min4.phy.varsites.phy --seqtype DNA --redo

```
ERROR: Invalid use of +ASC because of 198 invariant sites in the alignment

_6_ Species tree


## Aside

SNPs differentiating WA from QLD

```{r}
comp<-nometa %>% filter(Lineage=="AUS") %>% filter(Region %in% c("Queensland", "Western Australia")) %>% filter(Locality != "Tully Inlet")
comp %>% dplyr::select(Run) %>% write_tsv("bamlists/comp.names", col_names = FALSE)
comp %>% dplyr::select(NewPath) %>% write_tsv("bamlists/comp.bamlist", col_names = FALSE)

comp %>% filter(Region=="Western Australia")  %>% dplyr::select(Run) %>% write_tsv("outputs/1401/pop1.names", col_names = FALSE)
comp %>% filter(Region=="Queensland")  %>% filter(Locality=="Fitzroy River QLD") %>% dplyr::select(Run) %>% write_tsv("outputs/1401/pop2.names", col_names = FALSE)

```

```{sh, eval=FALSE}
srun -t 48:00:00 -p bmh --mem=32G --nodes=1 --ntasks-per-node=1 --cpus-per-task=12 $HOME/angsd/angsd -nthreads 12 \
-minInd 43 -bam bamlists/comp.bamlist -ref genome/GCF_001640805.2_TLL_Latcal_v3_genomic.fna \
-rf  meta/lates-lgs.txt  -out outputs/1401/comp-01-glf  \
-minMaf 0.05 -minMapQ 20 -minQ 20 -GL 1 -doGLF 2 -doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 \
-doGeno 2 -doPost 1 -postCutoff 0.9 -doVcf 1  > outputs/1401/comp.out 2> outputs/1401/comp.err &
```

	-> Number of sites retained after filtering: 682868 

```{sh, eval=FALSE}
bcftools reheader --samples bamlists/comp.names -o outputs/1401/comp-renamed.vcf.gz outputs/1401/comp-01-glf.vcf.gz

```


```{sh, eval=FALSE}
bcftools view -S outputs/1401/pop1.names outputs/1401/comp-renamed.vcf.gz   \
  | bcftools +fill-tags -- -t AF \
  | bcftools query -f '%CHROM\t%POS\t%REF\t%ALT\t%AF\n' \
  > outputs/1401/pop1.af.txt

bcftools view -S outputs/1401/pop2.names outputs/1401/comp-renamed.vcf.gz   \
  | bcftools +fill-tags -- -t AF \
  | bcftools query -f '%CHROM\t%POS\t%REF\t%ALT\t%AF\n' \
  > outputs/1401/pop2.af.txt
  
paste outputs/1401/pop1.af.txt outputs/1401/pop2.af.txt | awk '{print $1,$2,$3,$4,$5-$10}' > outputs/1401/diff.txt
```

```{r}
pop1<-read_tsv("outputs/1401/pop1.af.txt", col_names = c("Chrom","Pos","Ref","Alt","Freq1"))
pop2<-read_tsv("outputs/1401/pop2.af.txt", col_names = c("Chrom","Pos","Ref","Alt","Freq2"))
pop1 %>% left_join(pop2) %>% mutate(Diff=abs(Freq1-Freq2)) %>% arrange(-Diff)  %>% filter(Diff < 1.0 & Diff > 0.95)
```


# For phylogeny -

Why not use higher coverage data?

Why not 'high grade' fish for wild-caught, non admixed fish? 

Can use L. uwisara, L. lakdiva
1 Sulawesi, 1 Kalimantan, WJC9559
etc.

Can test indian ocean molecular phylogenetics separately with 'all' the fish.

```{r}
subset<-c("DRR397260","DRR391968","SRR3183260","SRR3183261","SRR3183253","SRR3165594","Trinco1","Mannar1","1613156","1613186","SRR3165617","SRR3165612","SRR3165609","WJC9559","SRR3165603","SRR3165600",
          "SRR3165624","WAF011638",
          "Broome08","Fitzroy45","WAF003767","Daly02","Roper02","Tully02","Fitz07")

phylo<-read_csv("meta/m164.csv") %>% filter(Run !="WAF011639") %>% filter(Run !="WAF003776") %>% filter(Run !="Broome01") %>% filter(Region != "Australian Aquaculture") %>% filter(Region !="Sri Lankan Aquaculture")  %>% filter(Run %in% subset) %>% arrange(Lineage)
  

phylo$Lineage<-factor(phylo$Lineage, levels=c("IND","uwisara","lakdiva","SEA","WAL","AUS","japonicus"))

phylo<-phylo %>% arrange(Lineage, Locality) 

phylo %>% dplyr::select(NewPath) %>% write_tsv(file="bamlists/phylo.bamlist", col_names = FALSE)
phylo %>% dplyr::select(NewPath) %>% write_tsv(file="bamlists/phylo.names", col_names = FALSE)
phylo
```


rf  meta/no-inv.txt

First, NC_066833.1
```{sh, eval=FALSE}
srun -t 2:00:00 -p bmh --mem=32G --nodes=1 --ntasks-per-node=1 --cpus-per-task=12 $HOME/angsd/angsd -nthreads 12 \
-minInd 21 -bam bamlists/phylo.bamlist -ref genome/GCF_001640805.2_TLL_Latcal_v3_genomic.fna \
-r NC_066833.1 -out outputs/1401/phylo-snps-01  \
-minMaf 0.01 -minMapQ 20 -minQ 20 -GL 1 -doGLF 2 -doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 \
-doGeno 2 -doPost 1 -postCutoff 0.9 -doVcf 1  > outputs/1401/phylo-snps-01.out 2> outputs/1401/phylo-snps-01.err &
```



```{sh, eval=FALSE}
plink --tped snps-wgs-01-glf.tped --tfam snps-wgs-01-glf.tfam  --out plink-binary-01 --recode --allow-extra-chr --noweb
plink --ped plink-binary-01.ped --map plink-binary-01.map --recode vcf --allow-extra-chr -out plink-01
bgzip plink-01.vcf 
tabix plink-01.vcf.gz
module load bcftools

bcftools reheader --samples bamlists/141.names -o outputs/1401/renamed-01.vcf.gz outputs/1401/plink-01.vcf.gz
#bcftools view -S bamlists/89.names -o outputs/1401/renamed-01.vcf.gz outputs/1401/renamed-01-90.vcf.gz

bcftools +fill-tags outputs/1401/renamed-01.vcf.gz  -- -t MAF,F_MISSING | bcftools view -i 'F_MISSING < 0.05' | bcftools view -i 'INFO/MAF > 0.01' | bcftools view -i 'INFO/MAF < 0.45' |  bcftools +prune -m 0.20 -w 50kb --nsites-per-win 1 --nsites-per-win-mode rand  > outputs/1401/pruned-01-maf01-45.vcf

bcftools +fill-tags outputs/1401/renamed-01.vcf.gz  -- -t MAF,F_MISSING | bcftools view -i 'F_MISSING < 0.05' | bcftools view -i 'INFO/MAF > 0.05' | bcftools view -i 'INFO/MAF < 0.45' |  bcftools +prune -m 0.20 -w 50kb --nsites-per-win 1 --nsites-per-win-mode rand  > outputs/1401/pruned-01-maf05-45.vcf

bcftools +fill-tags outputs/1401/renamed-01.vcf.gz  -- -t MAF,F_MISSING | bcftools view -i 'F_MISSING < 0.05' | bcftools view -i 'INFO/MAF > 0.10' | bcftools view -i 'INFO/MAF < 0.45' |  bcftools +prune -m 0.20 -w 50kb --nsites-per-win 1 --nsites-per-win-mode rand  > outputs/1401/pruned-01-maf10-45.vcf

bcftools +fill-tags outputs/1401/renamed-01.vcf.gz  -- -t MAF,F_MISSING | bcftools view -i 'F_MISSING < 0.05' | bcftools view -i 'INFO/MAF > 0.10' | bcftools view -i 'INFO/MAF < 0.45' |  bcftools +prune -m 0.20 -w 50kb --nsites-per-win 1 --nsites-per-win-mode maxAF  > outputs/1401/pruned-01-maf10-45-max.vcf


#Convert to phylip and then to nex
conda activate py27;

~/mccloud-rrt/vcf2phylip.py -i pruned-01-maf01-45.vcf;
~/mccloud-rrt/vcf2phylip.py -i pruned-01-maf05-45.vcf;
~/mccloud-rrt/vcf2phylip.py -i pruned-01-maf10-45-max.vcf;
~/mccloud-rrt/vcf2phylip.py -i pruned-01-maf10-45.vcf;

conda deactivate
```
