---
title: "1401-taxonomy"
output: html_document
date: "2026-03-02"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(ape)
library(phangorn)
library(tidyverse)
library(pcadapt)
library(ggpubr)
library(grid)
library(ggrepel)
library(ggtree)
library(tanggle)
```


Have a comprehensive data set, but am including two L. japonicus

Need to dump one and align.    
```{sh, eval=FALSE}
module load sratoolkit
fastq-dump --outdir split --skip-technical --read-filter pass --dumpbase --split-3 --gzip --clip DRR397260.lite.1.1

# in data/split
bash ../../../do-align.sh to-align.txt /home/maccamp/lates-wgs/genome/GCF_001640805.2_TLL_Latcal_v3_genomic.fna.gz

# downsample
srun -p bmh -t 24:00:00 --mem=32G --nodes=1 samtools view -bs  /home/maccamp/lates-wgs/data/split/DRR397260.sort.flt.bam > /home/maccamp/lates-wgs/data/downsample/DRR397260.reduced.bam

```

Goal - created rooted phylogenetic tree of samples. Can use svd quartets

_1_ Create bamlist excluding aquaculture samples 

Broome01 is odd in behavior as well
Can excluded taiwanese admixed fish

```{r}
meta<-read_csv("meta/m164.csv") %>% filter(Run !="WAF011639") %>% filter(Run !="WAF003776") %>% filter(Run !="Broome01") %>% filter(Region != "Australian Aquaculture") %>% filter(Region !="Sri Lankan Aquaculture")  

meta$Lineage<-factor(meta$Lineage, levels=c("IND","uwisara","lakdiva","SEA","WAL","AUS","japonicus"))

summary<-meta %>% group_by(Region, Locality, Lineage) %>% summarize(`Sample Size`=n())
locs<-read_tsv("outputs/range-map/points-edited-4.tsv")
points<-summary %>% left_join(locs)
points$Lineage<-factor(points$Lineage, levels=c("IND","uwisara","lakdiva","SEA","WAL","AUS","japonicus"))
points
```

```{r}
m141<-meta
m141 %>% write_csv("meta/taxonomy-paper.csv")
m141 %>% select(NewPath) %>% write_tsv("bamlists/141.bamlist", col_names = FALSE)
m141 %>% select(Run) %>% write_tsv("bamlists/141.names", col_names = FALSE)

nometa<-meta %>% filter(Lineage !="japonicus")
nometa %>% select(NewPath) %>% write_tsv("bamlists/139.bamlist", col_names = FALSE)
nometa %>% select(Run) %>% write_tsv("bamlists/139.names", col_names = FALSE)

```

 levels=c("DeGrey River","Broome","Fitzroy River WA","Fitzroy River WA-Historical","Cambridge Gulf","Daly River","Darwin Harbour","Roper River","Tully Inlet","Fly River","Hinchinbrook Channel", "Fitzroy River QLD","Samarinda","Sulawesi","Tamsui River") )

_2_ One chrom GLs for sanity

One chrom GLs for sanity

```{sh, eval=FALSE}
srun -p bmh -t 5:00:00 --mem=32G --nodes=1 --cpus-per-task=12  $HOME/angsd/angsd -P 12  \
-bam bamlists/139.bamlist -r NC_066833.1 \
-ref genome/GCF_001640805.2_TLL_Latcal_v3_genomic.fna \
-minInd 125 -minMapQ 20 -minQ 20 -GL 2 -doGLF 2 \
-doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 \
-doIBS 1 -doCounts 1 -doCov 1 -makeMatrix 1 -minMaf 0.05 \
-out outputs/1401/ibs-90-Lcal01 > outputs/1401/ibs-90-Lcal01.out 2> outputs/1401/ibs-90-Lcal01.err &
```

	-> Number of sites retained after filtering: 580629 at maf=0.01.        
	-> Number of sites retained after filtering: 147600 at maf=0.05.    

6/139 = 0.04, so maf < 0.05 won't produce unique variants in some pops. Setting maf initially to 0.01. Very noisy PCA, trying again at 0.05.     

Should try 0.01, 0.05 and 0.10 for phylogenies though, using rand when pruning and maxAF options.


```{r}
m <- as.matrix(read.table("outputs/1401/ibs-90-Lcal01.covMat"))
eig <- eigen(m)
var<-eig$values/sum(eig$values)
cumvar<-cumsum(eig$values)/sum(eig$values)

head(var)
head(cumvar)

vdf<-var %>% as_tibble() %>% rename(Variance=value) %>% mutate(PC=1:n()) %>% head(n=10)

scree<-ggplot(vdf) +
  geom_line(aes(x=PC, y=Variance)) +
  theme_bw() +
  theme(panel.grid = element_blank()) +
  scale_x_continuous(breaks=vdf$PC) +
  theme(axis.text=element_text(size=8)) +
  ggtitle("Scree Plot") +
  theme(plot.title = element_text(hjust=0.5, face="bold"))

scree
ggsave("outputs/1401/chrom01-scree-plot.jpeg")
```


```{r}
meta<-nometa
covs<-eig$vectors[,1:4] %>% as_tibble() %>% bind_cols(meta)

text12<-covs %>% select(Run, Region, V1, V2) %>%
  group_by(Region) %>% summarize(Count=n(), x=mean(V1), y=mean(V2))

text12L<-covs %>% select(Run, Locality, V1, V2) %>%
  group_by(Locality) %>% summarize(Count=n(), x=mean(V1), y=mean(V2))

pc12<-ggplot(covs) +
  geom_point(aes(x=V1, y=V2, fill=Lineage), pch=21, alpha=0.75, cex=2) +
  #  geom_text(aes(x=V1, y=V2, label=Run), pch=21, alpha=0.75, cex=2) +
  geom_text_repel(data=text12, aes(x=x, y=y, label=Region), max.overlaps = Inf) +
 # geom_text_repel(data=text12L, aes(x=x, y=y, label=Locality), size=3, max.overlaps = Inf) +
  xlab(paste("PC1", " ", round((100*var[1]),2), "%", sep = "")) +
  ylab(paste("PC2", " ", round((100*var[2]),2), "%", sep = "")) +
  theme_bw() +
  theme(panel.grid=element_blank()) +
  scale_fill_viridis_d(option="H") +
  ggtitle("PCs 1 and 2") +
  theme(plot.title = element_text(hjust=0.5, face="bold")) 
#  theme(legend.position = "none")

pc12
ggsave("outputs/1401/chrom01-lates-pc12.jpeg", width=6, height=6)
ggsave("outputs/1401/chrom01-lates-pc12.pdf", width=6, height=6)

```

_3_ Calls

# Calls

Excluding inversion zones

```{sh, eval=FALSE}
srun -t 48:00:00 -p bmh --mem=32G --nodes=1 --ntasks-per-node=1 --cpus-per-task=12 $HOME/angsd/angsd -nthreads 12 \
-minInd 127 -bam bamlists/141.bamlist -ref genome/GCF_001640805.2_TLL_Latcal_v3_genomic.fna \
-rf  meta/no-inv.txt -out outputs/1401/snps-wgs-01-glf  \
-minMaf 0.01 -minMapQ 20 -minQ 20 -GL 1 -doGLF 2 -doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 \
-doGeno 2 -doPost 1 -postCutoff 0.9 -doPlink 2  > outputs/1401/snps-wgs-01-glf.out 2> outputs/1401/snps-wgs-01-glf.err &
```

	-> Number of sites retained 


```{sh, eval=FALSE}
plink --tped snps-wgs-01-glf.tped --tfam snps-wgs-01-glf.tfam  --out plink-binary-01 --recode --allow-extra-chr --noweb
plink --ped plink-binary-01.ped --map plink-binary-01.map --recode vcf --allow-extra-chr -out plink-01
bgzip plink-01.vcf 
tabix plink-01.vcf.gz

#renaming vcf bcftools/1.13
module load bcftools

bcftools reheader --samples bamlists/141.names -o outputs/1401/renamed-01-90.vcf.gz outputs/1401/plink-01.vcf.gz
#bcftools view -S bamlists/89.names -o outputs/1401/renamed-01.vcf.gz outputs/1401/renamed-01-90.vcf.gz

bcftools +fill-tags outputs/1401/renamed-01.vcf.gz  -- -t MAF,F_MISSING | bcftools view -i 'F_MISSING < 0.05' | bcftools view -i 'INFO/MAF > 0.01' | bcftools view -i 'INFO/MAF < 0.45' |  bcftools +prune -m 0.20 -w 50kb --nsites-per-win 1 --nsites-per-win-mode rand  > outputs/1401/pruned-01-maf01-45.vcf

bcftools +fill-tags outputs/1401/renamed-01.vcf.gz  -- -t MAF,F_MISSING | bcftools view -i 'F_MISSING < 0.05' | bcftools view -i 'INFO/MAF > 0.05' | bcftools view -i 'INFO/MAF < 0.45' |  bcftools +prune -m 0.20 -w 50kb --nsites-per-win 1 --nsites-per-win-mode rand  > outputs/1401/pruned-01-maf05-45.vcf

bcftools +fill-tags outputs/1401/renamed-01.vcf.gz  -- -t MAF,F_MISSING | bcftools view -i 'F_MISSING < 0.05' | bcftools view -i 'INFO/MAF > 0.10' | bcftools view -i 'INFO/MAF < 0.45' |  bcftools +prune -m 0.20 -w 50kb --nsites-per-win 1 --nsites-per-win-mode rand  > outputs/1401/pruned-01-maf10-45.vcf

bcftools +fill-tags outputs/1401/renamed-01.vcf.gz  -- -t MAF,F_MISSING | bcftools view -i 'F_MISSING < 0.05' | bcftools view -i 'INFO/MAF > 0.10' | bcftools view -i 'INFO/MAF < 0.45' |  bcftools +prune -m 0.20 -w 50kb --nsites-per-win 1 --nsites-per-win-mode maxAF  > outputs/1401/pruned-01-maf10-45-max.vcf


#Convert to phylip and then to nex
conda activate py2;

~/github/mccloud-rrt/vcf2phylip.py -i pruned-01-maf01-45.vcf;
~/github/mccloud-rrt/vcf2phylip.py -i pruned-01-maf05-45.vcf;
~/github/mccloud-rrt/vcf2phylip.py -i pruned-01-maf10-45-max.vcf;
~/github/mccloud-rrt/vcf2phylip.py -i pruned-01-maf10-45.vcf;

conda deactivate
```
