---
title: "201-mystery-chrom"
output: html_document
date: "2023-08-25"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(tidyverse)
library(ggpubr)
library(vcfR)
library(adegenet)
library(snpR)
```

NC_066849.1 has many diagnostic SNPs to separate IND from other pops. What is going on? Structural variant, dups?   

Meta    

```{r}
m2<-read_csv("meta/58.csv")
m2$Region<-factor(m2$Region, levels=c("Northern Territory","Queensland","Papua New Guinea",
                                              "Indonesia","Philippines","Vietnam","Cambodia","Thailand",
                                              "India Eastern Coast","India Western Coast"))
m2 <-m2 %>% mutate(Lineage=ifelse(Region %in% c("Northern Territory","Queensland","Papua New Guinea"),"AUS+PNG",
                                                ifelse(Region %in% c("India Eastern Coast","India Western Coast"),"IND","SEA")))
m2 %>% group_by(Region) %>% summarize(Count=n(), Cov=mean(Coverage))
```

Can look at just this with calls or with GLs

GL version

```{sh, eval=FALSE}
srun -p high -t 12:00:00 --mem=32G --nodes=1 $HOME/angsd/angsd -P 12  \
-bam bamlists/58.bamlist -r NC_066849.1\
-ref  genome/GCF_001640805.2_TLL_Latcal_v3_genomic.fna \
-minInd 44 -minMapQ 10 -minQ 20 -GL 2 -doGLF 2 \
-doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 \
-doIBS 1 -doCounts 1 -doCov 1 -makeMatrix 1 -minMaf 0.05 \
-out outputs/201/58-ibs > outputs/201/58-ibs.out 2> outputs/201/58-ibs.err &


srun -p high -t 02:00:00 --nodes=1 $HOME/angsd/misc/NGSadmix -P 12 -likes outputs/201/58-ibs.beagle.gz -K 2 -o outputs/201/58-75-K2 &
srun -p high -t 02:00:00 --nodes=1 $HOME/angsd/misc/NGSadmix -P 12 -likes outputs/201/58-ibs.beagle.gz -K 3 -o outputs/201/58-75-K3 &
srun -p high -t 04:00:00 --nodes=1 $HOME/angsd/misc/NGSadmix -P 12 -likes outputs/201/58-ibs.beagle.gz -K 4 -o outputs/201/58-75-K4 &
srun -p high -t 04:00:00 --nodes=1 $HOME/angsd/misc/NGSadmix -P 12 -likes outputs/201/58-ibs.beagle.gz -K 5 -o outputs/201/58-75-K5 &
````

Can look for paralogs...

## Called genos
    
```{sh, eval=FALSE}
bcftools view -Ov -r NC_066849.1 outputs/108/vcf/renamed.vcf.gz > outputs/201/NC_066849.1.vcf

grep "^#" outputs/108/pruned.vcf  > outputs/201/header.txt
grep "NC_066849.1" outputs/108/pruned.vcf > outputs/201/NC_066849.1-body.txt
cat outputs/201/header.txt outputs/201/NC_066849.1-body.txt > outputs/201/NC_066849.1-pruned.vcf
```

```{r}
sample_meta<-m2 %>% select(Run,Region,Lineage) %>% mutate(Group=ifelse(Lineage=="AUS+PNG","1",
                                                        ifelse(Lineage=="SEA","2",
                                                        ifelse(Lineage=="IND","3","None")))) %>%
  mutate(Pop=ifelse(Region=="Northern Territory","1",
                   ifelse( Region=="Queensland","2",
                   ifelse( Region=="Papua New Guinea","3",
                   ifelse( Region=="Indonesia","4",
                   ifelse( Region=="Philippines","5",
                   ifelse( Region=="Vietnam","6",
                   ifelse( Region=="Cambodia","7",
                   ifelse( Region=="Thailand","8",
                   ifelse( Region=="India Eastern Coast","9",
                   ifelse( Region=="India Western Coast","10","None")))))))))))

my.dat <- import.snpR.data("outputs/201/NC_066849.1-pruned.vcf", sample.meta = sample_meta) 
```


```{r}
p<-plot_clusters(my.dat, facets = "Region", viridis.option = "H" )
```

```{r}
p
```


```{r}
ggplot(merge %>% filter(Chromosome=="NC_066849.1")) +
  geom_density2d_filled(aes(x=Position, y=AbsoluteDifference), alpha=0.75)
```

## Local PCA, NGS Paralogs, or coverage??

Trying local pca of  plink-33.vcf in 209

```{sh, eval=FALSE}
cat lates-lgs.txt  | while read line; do bcftools view -Ob -r $line plink-33.vcf.gz > $line.bcf; done;
for f in *.bcf; do bcftools index $f; done;

```

```{r}
m33<-read_csv("meta/33.csv")

samples<-m33 %>% select(Run) %>% rename(ID=Run)

population<-m33 %>% select(Pop) %>% rename(population=Pop)


table<-cbind(samples, population)
write.table(table, "outputs/201/plink-33/sample_info.tsv", quote = TRUE, row.names = FALSE, sep="\t")
```

This is ~73,315 snps, so pretty dense, ~3000 snps/chrom


./run_lostruct.R -i /Users/mac/github/lates-wgs/outputs/201/plink-33 -t snp -s 20 -m 4 -I /Users/mac/github/lates-wgs/outputs/201/plink-33/sample_info.tsv -j l201

./run_lostruct.R -i /Users/mac/github/lates-wgs/outputs/201/plink-33 -t snp -s 30 -m 4 -I /Users/mac/github/lates-wgs/outputs/201/plink-33/sample_info.tsv -j l202

Using the smaller (snp20 windows first)
```{r}
mds<-read_csv("outputs/201/plink-33/mds_coords.csv")
#make tidy
tidymds<-mds %>% gather(MDS, Value, 3:6)
MDS1<-filter(tidymds, MDS=="MDS1") %>% rename(MDS1=MDS) %>% rename(Value1=Value)
MDS2<-filter(tidymds, MDS=="MDS2") %>% rename(MDS2=MDS) %>% rename(Value2=Value)
MDS3<-filter(tidymds, MDS=="MDS3") %>% rename(MDS3=MDS) %>% rename(Value3=Value)
MDS4<-filter(tidymds, MDS=="MDS4") %>% rename(MDS4=MDS) %>% rename(Value4=Value)

ggplot(mds)+
  geom_point(aes(x=MDS1, y=MDS2), alpha=0.75) +
  theme_bw()

ggplot(mds)+
  geom_point(aes(x=MDS1, y=MDS3), alpha=0.75) +
  theme_bw()
```


Plot along chroms    

```{r}
p1<-MDS1 %>% mutate(Index=1:n())

out <- boxplot.stats(p1$Value1)$out
out_ind <- which(p1$Value1 %in% c(out))
outliers<-p1[out_ind,]
```

```{r}
chroms<-p1 %>% group_by(chrom) %>% mutate(Start=min(Index), Stop=max(Index)) %>% select(chrom,Start,Stop) %>% unique() %>% 
  mutate(Position=round((Start+Stop)/2))

nb.cols <- nrow(chroms)
mycolors <- colorRampPalette(brewer.pal(8, "Set1"))(nb.cols)

ggplot(p1) +
  geom_rect(data=chroms, aes(xmin=Start, xmax=Stop, ymin=min(p1$Value1), ymax=max(p1$Value1)), fill=mycolors, alpha=0.25) +
  geom_point(data=p1, aes(x=Index, y=Value1, color=chrom), alpha=0.75, cex=0.5) +
  geom_point(data=outliers, aes(x=Index, y=Value1), color="black", cex=0.5) +
  theme_bw() +
  scale_x_continuous(breaks=chroms$Position, labels=chroms$chrom) +
  theme(axis.text.x = element_text(angle=45, hjust = 1, face="bold", size=6)) +
  theme(legend.title = element_blank()) +
  theme(panel.grid = element_blank()) +
  theme(legend.position = "none") +
  scale_color_manual(values=mycolors) +
  ylab("MDS1") +
  xlab("Chromosome")
```

```{r}
p2<-MDS2 %>% mutate(Index=1:n())

out2 <- boxplot.stats(p2$Value2)$out
out_ind2 <- which(p2$Value2 %in% c(out2))
outliers2<-p2[out_ind2,]

chroms<-p2 %>% group_by(chrom) %>% mutate(Start=min(Index), Stop=max(Index)) %>% select(chrom,Start,Stop) %>% unique() %>% 
  mutate(Position=round((Start+Stop)/2))

#Make enough colors
nb.cols <- nrow(chroms)
mycolors <- colorRampPalette(brewer.pal(8, "Set1"))(nb.cols)


ggplot(p2) +
  geom_rect(data=chroms, aes(xmin=Start, xmax=Stop, ymin=min(p2$Value2), ymax=max(p2$Value2)), fill=mycolors, alpha=0.25) +
  geom_point(data=p2, aes(x=Index, y=Value2, color=chrom), alpha=0.75, cex=0.5) +
  geom_point(data=outliers2, aes(x=Index, y=Value2), color="black", cex=0.5) +
  theme_bw() +
  scale_x_continuous(breaks=chroms$Position, labels=chroms$chrom) +
  theme(axis.text.x = element_text(angle=45, hjust = 1, face="bold", size=6)) +
  theme(legend.title = element_blank()) +
  theme(panel.grid = element_blank()) +
  theme(legend.position = "none") +
  scale_color_manual(values=mycolors) +
  ylab("MDS2") +
  xlab("Chromosome")
```
