---
title: "202-pairwise-Fst"
output: html_document
date: "2023-08-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(tidyverse)
library(viridis)
library(ggpubr)
library(grid)
```

Calculating pairwise Fst with ANGSD

_1_ SFS need things organized like so

poplist

bamlist for each pop

meta   

```{r}
m2<-read_csv("meta/58-Indo-split.csv")
bamlist<-read_tsv("bamlists/downsample-58.bamlist", col_names=c("Downsample"))
m2$Path<-bamlist$Downsample
m2$Region<-factor(m2$Region, levels=c("Northern Territory","Queensland","Papua New Guinea",
                                              "Indonesia-K","Indonesia-SJ","Indonesia-SU",
                                      "Philippines","Vietnam","Cambodia","Thailand",
                                              "India Eastern Coast","India Western Coast"))

m2<-m2 %>% mutate(Lineage=ifelse(Region %in% c("India Eastern Coast","India Western Coast"), "IND",
                       ifelse(Region %in% c("Northern Territory","Queensland","Papua New Guinea"), "AUS+NG","SEA")))


m3<-filter(m2,! Region %in% c("Indonesia-SU","Vietnam") )
m3 %>% group_by(Lineage, Region) %>% summarize(Count=n())
```


```{r}
Region<-m3 %>% select(Region)
Region$Region<-gsub(" ","", Region$Region)
write_tsv(Region %>% unique(), file="poplists/poplist.txt", col_names = FALSE)

pops<-unique(Region$Region)
m3$pop<-gsub(" ","", m3$Region)
```

```{r}
writeBamlist<-function(Pop, Meta) {
  write_tsv(Meta %>% filter(pop==Pop) %>% select(Path), col_names = FALSE, file=paste0("poplists/",Pop,".bamlist"))
  
}
```

```{r}
lapply(pops,writeBamlist, m3)
```

Note, not necessary to do this I think, but if so, need to include Vietnam/Indonesia for 58 inds
```{r}
writeLineage<-function(Lin, Meta) {
  write_tsv(Meta %>% filter(Lineage==Lin) %>% select(Path), col_names = FALSE, file=paste0("poplists/",Lin,".bamlist"))
  
}
lapply(c("AUS+NG","SEA","IND"),writeLineage, m2)

Lineage<-m2 %>% select(Lineage)
write_tsv(Lineage %>% unique(), file="poplists/poplist2.txt", col_names = FALSE)

```
then sbatch 202.1-calc-sfs.sh

Then to calc pairwise fst, need pairwise list, should be 9*(9-1)/2 = 36 options.
or
10*(10-1)/2 = 45 options
```{r}
#https://stackoverflow.com/questions/48961247/how-do-i-create-all-unique-pairwise-combinations-of-my-sample-dataset
x<-unique(m3$pop)
y<-apply(combn(x,2),2,paste,collapse='\t')
y
write.table(y, file="poplists/pairwise-list.txt", quote = FALSE, row.names = FALSE, col.names = FALSE)
```

poplists/pairwise-list.txt is made

Also, what about main lineages?     

```{r}
x<-unique(m3$Lineage)
y<-apply(combn(x,2),2,paste,collapse='\t')
y
write.table(y, file="poplists/lineage-list.txt", quote = FALSE, row.names = FALSE, col.names = FALSE)
```

Running 202.2

 sbatch 202.1-calc-fst.sh, seeing what we need

```{r}
list<-read_tsv("poplists/pairwise-list.txt", col_names=c("Pop1","Pop2")) %>% mutate(Position=1:n())
fst<-read_tsv("outputs/202/pwfst.all", col_names=c("Pop1","Pop2","Unweighted","Weighted"))

fsts<-list %>% left_join(fst)
fsts

```
```{r}
incomplete<-fsts %>% filter(is.na(Weighted)==TRUE)
incomplete
write_tsv(incomplete %>% select(Pop1, Pop2), col_names = FALSE, file="poplists/pairwise-list2.txt")
```
```{r, eval=TRUE}

fsts2<-fsts %>% rename(Population2=Pop1, Population1=Pop2) %>% rename(Pop2=Population2, Pop1=Population1)
fsts3<-bind_rows(fsts,fsts2)
fsts<-fsts3
fsts$Pop1<-factor(fsts$Pop1, levels=c("NorthernTerritory","Queensland","PapuaNewGuinea",
                                              "Indonesia-K", "Indonesia-SJ","Philippines","Cambodia","Thailand",
                                              "IndiaEasternCoast","IndiaWesternCoast"))

fsts$Pop2<-factor(fsts$Pop2, levels=c("NorthernTerritory","Queensland","PapuaNewGuinea",
                                              "Indonesia-K", "Indonesia-SJ","Philippines","Cambodia","Thailand",
                                              "IndiaEasternCoast","IndiaWesternCoast"))
```

Indonesia.sfs is empty, splitting into KJ anD SU


oom event for thailand, need to up mem allocation (to 124 GB)

Make symmetric    

```{r}
list2<-list %>% rename(Population2=Pop1, Population1=Pop2) %>% rename(Pop2=Population2, Pop1=Population1)
list3<-bind_rows(list,list2)

```

```{r}
list3$Pop1<-factor(list3$Pop1, levels=c("NorthernTerritory","Queensland","PapuaNewGuinea",
                                              "Indonesia-K", "Indonesia-SJ","Philippines","Cambodia","Thailand",
                                              "IndiaEasternCoast","IndiaWesternCoast"))

list3$Pop2<-factor(list3$Pop2, levels=c("NorthernTerritory","Queensland","PapuaNewGuinea",
                                             "Indonesia-K", "Indonesia-SJ","Philippines","Cambodia","Thailand",
                                              "IndiaEasternCoast","IndiaWesternCoast"))

ggplot(list3) +
    geom_raster(aes(x=Pop1, y=Pop2, fill=Position))  +
    theme(axis.text.x=element_text(angle=45, vjust=1, hjust=1)) 

```
```{r}
back<-viridis(n=2, option="cividis")
```

```{r}
fstplot<-ggplot(fsts) +
  geom_raster(aes(x=Pop1, y=Pop2, fill=Weighted)) +
  geom_text(aes(x=Pop1, y=Pop2, label=sprintf("%.2f", Weighted)), color="white", fontface="bold") +
  scale_fill_viridis_c(option="cividis", direction=-1, alpha=1) +
  xlab("\nRegion") +
  ylab("Region\n") +
  theme_bw() +
  theme(panel.background = element_rect(fill=back[1])) +
  theme(panel.grid = element_blank()) +
 # scale_x_discrete(labels=c("AUE","PNG","INA","MAL","THA")) +
#  scale_y_discrete(labels=c("AUW","AUE","PNG","INA","MAL")) +
  theme(axis.text=element_text(size=12)) +
  theme(axis.text.x=element_text(angle=45, vjust=1, hjust=1)) +
  theme(axis.title = element_text(size=14, face="bold")) +
  ggtitle("A") +
  theme(plot.title=element_text(size=16, face="bold"))

fstplot
```

__3_ Nucleotide diversity

```{sh, eval=FALSE}
#Get .sfs (folded)
realSFS out.saf.idx -P 24 -fold 1 > out.sfs
realSFS saf2theta out.saf.idx -outname out -sfs out.sfs -fold 1
#Then, Estimate for every Chromosome/scaffold
thetaStat do_stat out.thetas.idx
```

I have .sfs in 202.1-calc-sfs.sh      

See 202.3 calculatign TW, TP, TajD etc



cat poplists/poplist.txt | while read pop; do echo $pop; awk 'NR == 1 {print "Population" "\t" $0 ; next;}{print FILENAME "\t" $0 ;}' outputs/202/$pop-thetas-stat.pestPG > outputs/202/$pop-diversity.stats; done;


done;
awk 'NR == 1 {print "Population" "\t" $0 ; next;}{print FILENAME "\t" $0 ;}' outputs/202/Cambodia-thetas-stat.pestPG

```{r}
files<-list.files("outputs/202", pattern="*diversity.stats", full.names = TRUE)
files

stats<-lapply(files, read_tsv) %>% bind_rows()
```

```{r}
stats2<-stats %>% select(Population, Chr, tW, tP, Tajima, nSites) 
stats2$Population<-gsub("outputs/202/","",stats2$Population)
stats2$Population<-gsub("-thetas-stat.pestPG","",stats2$Population)
stats2$Population<-factor(stats2$Population, levels=c("NorthernTerritory","Queensland","PapuaNewGuinea",
                                             "Indonesia-K", "Indonesia-SJ","Philippines","Cambodia","Thailand",
                                              "IndiaEasternCoast","IndiaWesternCoast"))
stats2<-stats2 %>%
  mutate(Lineage=ifelse(Population %in% c("IndiaEasternCoast","IndiaWesternCoast"), "IND",
                       ifelse(Population %in% c("NorthernTerritory","Queensland","PapuaNewGuinea"), "AUS+NG","SEA")))

```


```{r}
blank <- grid.rect(gp=gpar(col="white"))
```

```{r}
pi<-ggplot(stats2) +
  geom_boxplot(aes(x=Population, y=tP, fill=Lineage), outlier.size = 0.25,  alpha=0.50)  +
  theme_bw() +
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1)) +
  xlab("\nSampling Region") +
  ylab("Theta Pi\n") +
  scale_fill_viridis_d() +
  theme(legend.position = "none") +
  theme(panel.grid = element_blank()) +
  ggtitle("A") +
  theme(plot.title = element_text(size=16, face="bold"))

taj<-ggplot(stats2) +
  geom_boxplot(aes(x=Population, y=Tajima, fill=Lineage), outlier.size = 0.25, alpha=0.50)  +
  theme_bw() +
  theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1)) +
  xlab("\nSampling Region") +
  ylab("Tajima's D\n") +
  scale_fill_viridis_d() +
  theme(legend.position = "none") +
  theme(panel.grid = element_blank()) +
  ggtitle("B") +
  theme(plot.title = element_text(size=16, face="bold"))

pi
```

```{r}
ggarrange(pi, blank, taj, ncol=3, widths=c(5,1,5))

ggsave("outputs/202/stats.pdf", width=8, height=4)
```
  
