---
title: "202-pairwise-Fst"
output: html_document
date: "2023-08-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(tidyverse)
```

Calculating pairwise Fst with ANGSD

_1_ SFS need things organized like so

poplist

bamlist for each pop

meta   

```{r}
m2<-read_csv("meta/58.csv")
m2$Region<-factor(m2$Region, levels=c("Northern Territory","Queensland","Papua New Guinea",
                                              "Indonesia","Philippines","Vietnam","Cambodia","Thailand",
                                              "India Eastern Coast","India Western Coast"))

m3<-filter(m2,Region != "Vietnam") 
m3 %>% group_by(Region) %>% summarize(Count=n())
```


```{r}
Region<-m3 %>% select(Region)
Region$Region<-gsub(" ","", Region$Region)
write_tsv(Region %>% unique(), file="poplists/poplist.txt", col_names = FALSE)

pops<-unique(Region$Region)
m3$pop<-gsub(" ","", m3$Region)
```

```{r}
writeBamlist<-function(Pop, Meta) {
  write_tsv(Meta %>% filter(pop==Pop) %>% select(Path), col_names = FALSE, file=paste0("poplists/",Pop,".bamlist"))
  
}
```

```{r}
lapply(pops,writeBamlist, m3)
```

then sbatch 202.1-calc-sfs.sh

Then to calc pairwise fst, need pairwise list, should be 9*(9-1)/2 = 36 options.

```{r}
#https://stackoverflow.com/questions/48961247/how-do-i-create-all-unique-pairwise-combinations-of-my-sample-dataset
x<-unique(m3$pop)
y<-apply(combn(x,2),2,paste,collapse='\t')
y
write.table(y, file="poplists/pairwise-list.txt", quote = FALSE, row.names = FALSE, col.names = FALSE)
```

poplists/pairwise-list.txt is made

Running 202.2

 sbatch 202.1-calc-fst.sh, seeing what we need

```{r}
list<-read_tsv("poplists/pairwise-list.txt", col_names=c("Pop1","Pop2"))
fst<-read_tsv("outputs/202/pwfst.all", col_names=c("Pop1","Pop2","Unweighted","Weighted"))

fsts<-list %>% left_join(fst)
fsts$Pop1<-factor(fsts$Pop1, levels=c("NorthernTerritory","Queensland","PapuaNewGuinea",
                                              "Indonesia","Philippines","Vietnam","Cambodia","Thailand",
                                              "IndiaEasternCoast","IndiaWesternCoast"))
fsts$Pop2<-factor(fsts$Pop2, levels=c("NorthernTerritory","Queensland","PapuaNewGuinea",
                                              "Indonesia","Philippines","Vietnam","Cambodia","Thailand",
                                              "IndiaEasternCoast","IndiaWesternCoast"))
```

Indonesia.sfs is empty

realSFS Indonesia.saf.idx > Indonesia.sfs

(base) maccamp@farm:~/lates-wgs/outputs/202$ srun -p bigmemh --nodes=1 --mem=96G  --time=12:00:00 realSFS Indonesia.saf.idx > Indonesia.sfs


```{r}
fstplot<-ggplot(fsts %>% arrange(Pop1)) +
  geom_raster(aes(y=Pop1, x=Pop2, fill=Weighted)) +
  geom_text(aes(y=Pop1, x=Pop2, label=sprintf("%.2f", Weighted)), color="white", fontface="bold") +
  scale_fill_viridis_c(option="cividis", direction=-1, alpha=1) +
  xlab("\nRegion") +
  ylab("Region\n") +
  theme_bw() +
  theme(panel.background = element_blank()) +
  theme(panel.grid = element_blank()) +
 # scale_x_discrete(labels=c("AUE","PNG","INA","MAL","THA")) +
#  scale_y_discrete(labels=c("AUW","AUE","PNG","INA","MAL")) +
  theme(axis.text=element_text(size=12)) +
  theme(axis.text.x=element_text(angle=45, vjust=1, hjust=1)) +
  theme(axis.title = element_text(size=14, face="bold")) +
  ggtitle("A") +
  theme(plot.title=element_text(size=16, face="bold"))

fstplot
```

## Nucleotide diversity

```{sh, eval=FALSE}
#Get .sfs (folded)
realSFS out.saf.idx -P 24 -fold 1 > out.sfs
realSFS saf2theta out.saf.idx -outname out -sfs out.sfs -fold 1
#Then, Estimate for every Chromosome/scaffold
thetaStat do_stat out.thetas.idx
```

I have .sfs in 202.1-calc-sfs.sh      



