---
title: "208-site-lists"
output: html_document
date: "2023-09-06"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(tidyverse)
library(vcfR)
library(snpR)
```

I need a better way of getting admixture proportions....


```{r}
m2<-read_csv("meta/58.csv")
m2$Region<-factor(m2$Region, levels=c("Northern Territory","Queensland","Papua New Guinea",
                                              "Indonesia","Philippines","Vietnam","Cambodia","Thailand",
                                              "India Eastern Coast","India Western Coast"))
m2 <-m2 %>% mutate(Lineage=ifelse(Region %in% c("Northern Territory","Queensland","Papua New Guinea"),"AUS+NG",
                                                ifelse(Region %in% c("India Eastern Coast","India Western Coast"),"IND","SEA")))
m2 %>% group_by(Region) %>% summarize(Count=n(), Cov=mean(Coverage))

write_tsv(m2 %>% select(Run), file="bamlists/58-sample-names.txt", col_names = FALSE)
```


```{r}
aus<-m2 %>% filter(Lineage %in% c("AUS+NG"))
sea<-m2 %>% filter(Lineage %in% c("SEA"))
ind<-m2 %>% filter(Lineage %in% c("IND"))
```

```{r}
aus %>% select(Run) %>% write_tsv("outputs/208/aus.txt", col_names = FALSE)
sea %>% select(Run) %>% write_tsv("outputs/208/sea.txt", col_names = FALSE)
ind %>% select(Run) %>% write_tsv("outputs/208/ind.txt", col_names = FALSE)
```

aus=17
sea=30
ind=11

```{sh, eval=FALSE}
bcftools view -S outputs/208/aus.txt outputs/108/renamed.vcf.gz > outputs/208/aus.vcf
bcftools view -S outputs/208/sea.txt outputs/108/renamed.vcf.gz > outputs/208/sea.vcf
bcftools view -S outputs/208/ind.txt outputs/108/renamed.vcf.gz > outputs/208/ind.vcf

#on farm module load vcftools
vcftools --vcf outputs/208/aus.vcf  --freq --out outputs/208/aus.vcf
vcftools --vcf outputs/208/sea.vcf  --freq --out outputs/208/sea.vcf
vcftools --vcf outputs/208/ind.vcf  --freq --out outputs/208/ind.vcf
```




```{r, eval=FALSE}
freq1<-read_tsv("outputs/208/aus.vcf.frq.gz", skip = 1, col_names = FALSE) %>% 
  rename(Chromosome=X1, Position=X2, NAllelesAUS=X3, NAUS=X4, Major=X5, Minor=X6) %>%
  separate(Major, into=c("Major","MajorFrequencyAUS"), sep=":") %>% 
  separate(Minor, into=c("Minor","MinorFrequencyAUS"), sep=":")
freq1$MajorFrequencyAUS<-as.numeric(freq1$MajorFrequencyAUS)
freq1$MinorFrequencyAUS<-as.numeric(freq1$MinorFrequencyAUS)


freq2<-read_tsv("outputs/208/sea.vcf.frq.gz", skip = 1, col_names = FALSE) %>% 
  rename(Chromosome=X1, Position=X2, NAllelesSEA=X3, NSEA=X4, Major=X5, Minor=X6) %>%
  separate(Major, into=c("Major","MajorFrequencySEA"), sep=":") %>% 
  separate(Minor, into=c("Minor","MinorFrequencySEA"), sep=":")
freq2$MajorFrequencySEA<-as.numeric(freq2$MajorFrequencySEA)
freq2$MinorFrequencySEA<-as.numeric(freq2$MinorFrequencySEA)

freq3<-read_tsv("outputs/208/ind.vcf.frq.gz", skip = 1, col_names = FALSE) %>% 
  rename(Chromosome=X1, Position=X2, NAllelesIND=X3, NIND=X4, Major=X5, Minor=X6)%>%
  separate(Major, into=c("Major","MajorFrequencyIND"), sep=":") %>%
  separate(Minor, into=c("Minor","MinorFrequencyIND"), sep=":")
freq3$MajorFrequencyIND<-as.numeric(freq3$MajorFrequencyIND)
freq3$MinorFrequencyIND<-as.numeric(freq3$MinorFrequencyIND)

comb<-left_join(freq1, freq2) %>% left_join(freq3)

save(comb, file="outputs/208/comb.rda")
```


Combine and generate some metrics

aus=17
sea=30
ind=11


```{r, eval=FALSE}
load("outputs/208/comb.rda")
merge<-comb %>% mutate(AbsoluteDifferenceAUSSEA=abs(MajorFrequencyAUS-MajorFrequencySEA)) %>% 
            mutate(AbsoluteDifferenceAUSIND=abs(MajorFrequencyAUS-MajorFrequencyIND)) %>%
            mutate(AbsoluteDifferenceSEAIND=abs(MajorFrequencySEA-MajorFrequencyIND)) %>%             
  select(Chromosome, Position, Major, Minor, MajorFrequencyAUS, MinorFrequencyAUS, MajorFrequencySEA, MinorFrequencySEA,
         MajorFrequencyIND, MinorFrequencyIND, AbsoluteDifferenceAUSSEA, AbsoluteDifferenceAUSIND,
         AbsoluteDifferenceSEAIND, NAUS, NSEA, NIND)
  
# Sample sizes
#  filter(N > 30, NWinter > 20) 
save(merge, file="outputs/208/merge.rda")
```

Control for missing data at phylogroup level.    
```{r}
load("outputs/208/merge.rda")
```

```{r}
merge2<-merge %>% filter(NAUS > (0.9*2*17)) %>% filter(NSEA > (0.9*2*30)) %>% filter(NIND > (0.9*2*11))
```


1,470,647 variants
```{r}
diffs1<-merge2 %>% filter(AbsoluteDifferenceAUSIND>0.90, AbsoluteDifferenceSEAIND>0.90)
write_csv(diffs1, "meta/site-list-AUSSEA-IND.csv")
```

1285 variants

```{r}
diffs2<-merge2 %>% filter(AbsoluteDifferenceAUSSEA>0.90)
```

70 variants

```{r}
set1<-diffs1 %>% select(Chromosome, Position)
set2<-diffs2 %>% select(Chromosome, Position)
complete<-bind_rows(set1,set2) %>% unique() %>% arrange(Chromosome, Position)

write_tsv(complete, file="meta/complete-site-list.tsv", col_names = FALSE)
```

```{r}
mystery<-diffs1 %>% filter(Chromosome =="NC_066849.1")
ggplot(mystery) +
  geom_point(aes(x=Position,y=MinorFrequencyIND))
```

27673719 bp long, basically genome-wide. so weird! 

```{r}
ggplot(diffs1) +
  geom_histogram(aes(x=Chromosome), stat='count')
```

Can I pull these from a beagle file for ngsAdmix?
(base) maccamp@farm:~/lates-wgs$ cat meta/site-list-AUSSEA-IND.csv  | cut -f 1,2 -d ',' | grep -v "Chrom" | perl -pe 's/,/\t/g' > outputs/208/site-list.txt
angsd sites index site-list.txt

cp meta/complete-site-list.tsv ./outputs/208/
angsd sites index complete-site-list.tsv 
```{sh, eval=FALSE}
srun -p high -t 16:00:00 --mem=32G --nodes=1 $HOME/angsd/angsd -P 12  \
-bam bamlists/downsample-58.bamlist -sites outputs/208/site-list.txt \
-anc  genome/GCF_001640805.2_TLL_Latcal_v3_genomic.fna \
-minInd 52 -minMapQ 20 -minQ 20 -GL 1 -doGLF 2 \
-doMajorMinor 1 -doPost 1 -doMaf 1 -SNP_pval 1e-6 \
-minMaf 0.05 \
-out outputs/208/58-gls-90 > outputs/208/58-gls-90.out 2> outputs/208/58-gls-90.err &

srun -p high -t 04:00:00 --mem=32G --nodes=1 $HOME/angsd/misc/NGSadmix -P 12 -likes outputs/208/58-gls-90.beagle.gz -K 2 -o outputs/208/58-K2-gls &
srun -p high -t 05:00:00 --mem=32G --nodes=1 $HOME/angsd/misc/NGSadmix -P 12 -likes outputs/208/58-gls-90.beagle.gz -K 3 -o outputs/207/58-K3-gls &
srun -p high -t 04:00:00 --mem=32G --nodes=1 $HOME/angsd/misc/NGSadmix -P 12 -likes outputs/208/58-gls-90.beagle.gz -K 4 -o outputs/207/58-K4-gls &


srun -p high -t 16:00:00 --mem=32G --nodes=1 $HOME/angsd/angsd -P 12  \
-bam bamlists/downsample-58.bamlist -sites outputs/208/complete-site-list.tsv  \
-anc  genome/GCF_001640805.2_TLL_Latcal_v3_genomic.fna \
-minInd 52 -minMapQ 20 -minQ 20 -GL 1 -doGLF 2 \
-doMajorMinor 1 -doPost 1 -doMaf 1 -SNP_pval 1e-6 \
-minMaf 0.05 \
-out outputs/208/58-gls-90-clist > outputs/208/58-gls-90-clist.out 2> outputs/208/58-gls-90-clist.err &


srun -p high -t 04:00:00 --mem=32G --nodes=1 $HOME/angsd/misc/NGSadmix -P 12 -likes outputs/208/58-gls-90-clist.beagle.gz -K 2 -o outputs/208/58-K2-gls-clist &
srun -p high -t 05:00:00 --mem=32G --nodes=1 $HOME/angsd/misc/NGSadmix -P 12 -likes outputs/208/58-gls-90-clist.beagle.gz -K 3 -o outputs/207/58-K3-gls-clist &
srun -p high -t 04:00:00 --mem=32G --nodes=1 $HOME/angsd/misc/NGSadmix -P 12 -likes outputs/208/58-gls-90-clist.beagle.gz -K 4 -o outputs/207/58-K4-gls-clist &
```


Removing NC_066849.1
```{r}
incomplete<-complete %>% filter(Chromosome !="NC_066849.1")

ggplot(incomplete) +
  geom_histogram(aes(x=Chromosome), stat='count') +
  theme(axis.text.x = element_text(angle=45, hjust=1, vjust=1))
```

```{r}
nrow(diffs1 %>% select(Chromosome, Position) %>% filter(Chromosome !="NC_066849.1"))
nrow(diffs2 %>% select(Chromosome, Position) %>% filter(Chromosome !="NC_066849.1"))

write_tsv(complete %>% filter(Chromosome !="NC_066849.1"), file="meta/incomplete-site-list.tsv", col_names = FALSE)
```

(base) maccamp@farm:~/lates-wgs$ cp meta/incomplete-site-list.tsv outputs/208/
(base) maccamp@farm:~/lates-wgs/outputs/208$ angsd sites index incomplete-site-list.tsv 

```{sh, eval=FALSE}
srun -p high -t 16:00:00 --mem=32G --nodes=1 $HOME/angsd/angsd -P 12  \
-bam bamlists/downsample-58.bamlist -sites outputs/208/incomplete-site-list.tsv  \
-anc  genome/GCF_001640805.2_TLL_Latcal_v3_genomic.fna \
-minInd 52 -minMapQ 20 -minQ 20 -GL 1 -doGLF 2 \
-doMajorMinor 1 -doPost 1 -doMaf 1 -SNP_pval 1e-6 \
-minMaf 0.05 \
-out outputs/208/58-gls-90-inclist > outputs/208/58-gls-90-inclist.out 2> outputs/208/58-gls-90-inclist.err &


srun -p high -t 16:00:00 --mem=32G --nodes=1 $HOME/angsd/angsd -P 12  \
-bam bamlists/downsample-58.bamlist -sites outputs/208/incomplete-site-list.tsv  \
-anc  genome/GCF_001640805.2_TLL_Latcal_v3_genomic.fna \
-minInd 52 -minMapQ 20 -minQ 20 -GL 1 -doGLF 2 \
-doMajorMinor 1 -doPost 1 -doMaf 1 -SNP_pval 1e-6 \
-minMaf 0.05 -doGeno 4 \
-out outputs/208/58-gls-90-inclist-geno > outputs/208/58-gls-90-inclist-geno.out 2> outputs/208/58-gls-90-inclist-geno.err &

srun -p high -t 04:00:00 --mem=32G --nodes=1 $HOME/angsd/misc/NGSadmix -P 12 -likes outputs/208/58-gls-90-inclist.beagle.gz -K 2 -o outputs/208/58-K2-gls-inclist &
srun -p high -t 05:00:00 --mem=32G --nodes=1 $HOME/angsd/misc/NGSadmix -P 12 -likes outputs/208/58-gls-90-inclist.beagle.gz -K 3 -o outputs/207/58-K3-gls-inclist &
srun -p high -t 04:00:00 --mem=32G --nodes=1 $HOME/angsd/misc/NGSadmix -P 12 -likes outputs/208/58-gls-90-inclist.beagle.gz -K 4 -o outputs/207/58-K4-gls-inclist &
```


Can try to get things together.

_1_ sample vcf to the sites of interest
`chr\tpos format`

```{sh, eval=FALSE}
bcftools view -R meta/incomplete-site-list.tsv  outputs/108/renamed.vcf.gz > outputs/208/sites.vcf
bcftools view -R meta/complete-site-list.tsv  outputs/108/renamed.vcf.gz > outputs/208/csites.vcf
bcftools view -R meta/expanded-site-list.tsv  outputs/108/renamed.vcf.gz > outputs/208/esites.vcf

```


```{r}
mm<-m58 %>% select(Run,Region,Lineage)
#mm$Region<-gsub(" ","",mm$Region)
mydata <- import.snpR.data("outputs/208/esites.vcf", sample.meta = mm)
```


```{r}
plot_clusters(mydata, facets="Lineage")
```

```{r}
plot_structure(mydata, facet = "Region", 
               facet.order = c("Northern Territory","Queensland","Papua New Guinea",
                               "Indonesia","Philippines","Cambodia","Thailand","Vietnam",
                               "India Eastern Coast","India Western Coast"),
               structure_path = "/Users/mac/bin/structure", k=3, qsort=FALSE, reps = 1,
               clumpp_path = "/Users/mac/github/CLUMPP_MacOSX.1.1.2/CLUMPP", 
               iterations=1000000, burnin=10000000)
```


Expanded list


```{r}
diffs3<-merge2 %>% filter(AbsoluteDifferenceAUSIND>0.95, AbsoluteDifferenceSEAIND>0.95)
diffs4<-merge2 %>% filter(AbsoluteDifferenceAUSSEA>0.95)
```

```{r}
set3<-diffs3 %>% select(Chromosome, Position)
set4<-diffs4 %>% select(Chromosome, Position)

expanded<-bind_rows(set3,set4) %>% unique() %>% arrange(Chromosome, Position) %>% filter(Chromosome!="NC_066849.1")

write_tsv(expanded, file="meta/expanded-site-list.tsv", col_names = FALSE)
```

## Read in all the snps

merge2 has low missing dat snps. Let's get those and prune.
MAF filter  
bcftools view -q 0.30:minor 

```{r}
write_tsv(merge2 %>% select(Chromosome, Position), file="outputs/208/merge2.tsv", col_names = FALSE)
```
```{sh,eval=FALSE}
bcftools view -R outputs/208/merge2.tsv  outputs/108/renamed.vcf.gz | bcftools +prune -l 0.20 -w 100000 > outputs/208/pruned-merge2.vcf
#bgzip, tabix
bcftools view -r NC_066834.1 outputs/208/pruned-merge2.vcf.gz > outputs/208/NC_066834.1.vcf
```


```{r}
mydata2 <- import.snpR.data("outputs/208/pruned-merge2.vcf.gz", sample.meta = mm)
```

16,642 variants

```{r}
plot_structure(mydata2, facet = "Region", 
               facet.order = c("Northern Territory","Queensland","Papua New Guinea",
                               "Indonesia","Philippines","Cambodia","Thailand","Vietnam",
                               "India Eastern Coast","India Western Coast"),
               structure_path = "/Users/mac/bin/structure", k=2, qsort=FALSE, reps = 1,
               clumpp_path = "/Users/mac/github/CLUMPP_MacOSX.1.1.2/CLUMPP", 
               iterations=1000000, burnin=10000000)
```

```{r}
plot_structure(mydata2, facet = "Region", 
               facet.order = c("Northern Territory","Queensland","Papua New Guinea",
                               "Indonesia","Philippines","Cambodia","Thailand","Vietnam",
                               "India Eastern Coast","India Western Coast"),
               structure_path = "/Users/mac/bin/structure", k=3, qsort=FALSE, reps = 1,
               clumpp_path = "/Users/mac/github/CLUMPP_MacOSX.1.1.2/CLUMPP", 
               iterations=1000000, burnin=10000000)

ggsave("outputs/208/called-snps-k3.jpeg")
```

```{r}
plot_structure(mydata2, facet = "Region", 
               facet.order = c("Northern Territory","Queensland","Papua New Guinea",
                               "Indonesia","Philippines","Cambodia","Thailand","Vietnam",
                               "India Eastern Coast","India Western Coast"),
               structure_path = "/Users/mac/bin/structure", k=4, qsort=FALSE, reps = 1,
               clumpp_path = "/Users/mac/github/CLUMPP_MacOSX.1.1.2/CLUMPP", 
               iterations=1000000, burnin=10000000)

ggsave("outputs/208/called-snps-k4.jpeg")
```
