---
title: "210-network"
output: html_document
date: "2023-09-14"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

Phylogenetic network 


```{r}
library(phytools)
library(tidyverse)
library(ggtree)
library(tanggle)
library(phangorn)
library(viridis)
library(ggpubr)
library(ape)
library(snpR)
```

Need an alignment. 

```{r}
m188<-read_csv("meta/rad+wgs.csv")
m188$Pop<-factor(m188$Pop, levels=c("AUW","Northern Territory","AUE",
                                                             "Queensland","PNG","Papua New Guinea",
                                                             "INA","Indonesia","MAL","THA","Thailand","Cambodia",
                                                               "Vietnam","Philippines","India Eastern Coast",
                                                               "India Western Coast"))
m188<-m188 %>% mutate(`Data Type` = ifelse(Pop %in% c("AUW","AUE","PNG","INA","MAL","THA"),"RADseq","WGS"))
write_tsv(m188 %>% select(Run), file="meta/rad+wgs.names", col_names = FALSE)
```

In 209 I have some called SNPS


```{sh, eval=FALSE}
bcftools reheader -s meta/rad+wgs.names outputs/209/188-plink.vcf.gz | bcftools view -Ov > outputs/210/188-plink-renamed.vcf
 ~/github/mccloud-rrt/vcf2phylip.py -i 188-plink-renamed.vcf 
 
 iqtree -s 188-plink-renamed.min4.phy -T AUTO -st DNA -m GTR+ASC -bb 1000 --redo
 iqtree -s 188-plink-renamed.min4.phy.varsites.phy -T AUTO -st DNA -m GTR+ASC -bb 1000 --redo

```

```{r}
dat<-read.dna(file="outputs/210/188-plink-renamed.min4.phy")
write.nexus.data(dat, file="outputs/210/188-plink.nex")
```


```{r}
net1<-read.nexus.networx("outputs/210/188-plink-network.nex")
```

```{r}
gb<-ggsplitnet(net1)  
gb$data<-left_join(gb$data, m188, by=c("label"="Run")) 

gb + 
  geom_tippoint(aes(shape=Lineage, fill=Pop), cex=4) +
  scale_shape_manual(values = c(21,23,24)) +
  scale_fill_viridis_d(option="viridis") +
  guides(fill = guide_legend(override.aes = list(pch = 22))) 

```


Let's do this with just the WGS data

```{r}
m2<-read_csv("meta/58-Indo-split.csv")
m2$Region<-factor(m2$Region, levels=c("Northern Territory","Queensland","Papua New Guinea",
                                              "Indonesia-K","Indonesia-SJ","Indonesia-SU",
                                      "Philippines","Vietnam","Cambodia","Thailand",
                                              "India Eastern Coast","India Western Coast"))
m2 <-m2 %>% mutate(Lineage=ifelse(Region %in% c("Northern Territory","Queensland","Papua New Guinea"),"AUS+NG",
                                                ifelse(Region %in% c("India Eastern Coast","India Western Coast"), "IND",
                                                       "SEA")))
bamlist<-read_csv("bamlists/downsample-58.bamlist", col_names = "Downsample")

m2<-bind_cols(m2, bamlist)
m58<-m2
```

```{sh, eval=FALSE}
bcftools +prune -l 0.30 -w 10000 outputs/108/renamed.vcf.gz > outputs/210/pruned-03.vcf

 ~/github/mccloud-rrt/vcf2phylip.py -i pruned.vcf 
 ~/github/mccloud-rrt/vcf2phylip.py -i pruned-03.vcf 

```

```{r}
dat<-read.dna(file="outputs/210/pruned.min4.phy")
write.nexus.data(dat, file="outputs/210/pruned.nex")

```

```{sh, eval=FALSE}
iqtree -s pruned.min4.phy -st DNA -m GTR+ASC -bb 1000 --redo
iqtree -s pruned.min4.phy.varsites.phy -T AUTO -st DNA -m MFP+ASC -bb 10000 --redo
```

```{r}
net<-read.nexus.networx("outputs/210/pruned-network.nex")
```

```{r}
g<-ggsplitnet(net)  
g$data<-left_join(g$data, m2, by=c("label"="Run")) 

g + 
  geom_tippoint(aes(shape=Lineage, fill=Region), cex=4, alpha=1.00) +
  scale_shape_manual(values = c(21,23,24)) +
  scale_fill_viridis_d(option="H") +
  guides(fill = guide_legend(override.aes = list(pch = 22))) 

ggsave("outputs/210/wgs-network.jpeg")

```

Cophylogram with mtDNA tree?
```{r}
tree<-read.tree("data/mtdna/new-coi.afasta.contree")
#tree<-read.tree("data/coi/trim.phy.contree")
#tree<-read.tree("data/coi/new-coi-ref-seqs.afasta.contree")
t2<-midpoint.root(tree)
t3<-as.polytomy(t2, feature='node.label', fun=function(x) as.numeric(x) < 75)

t<-t3

t<-ggtree(t)

t$data$Bootstrap<-as.numeric(t$data$label)

d <- t$data
d <- d[!d$isTip,]
d$label <- as.numeric(d$label)
d <- d[d$label >= 90,]

e <- t$data
e <- e[!e$isTip,]
e$label <- as.numeric(e$label)
e <- e[e$label < 90,]
e <- e[e$label >= 75,]
```

```{r}
u<-t %<+% m58 + #bind_rows(m58, rm) +
  geom_point(data=e,  fill="gray50", cex=3, alpha=1, pch=22) +
  geom_point(data=d,  fill="black", cex=3, alpha=1, pch=22) +
  geom_tippoint(aes(x=x+0.002,fill=Region, shape=Lineage), cex=3) + 
  geom_tiplab(aes(label=Region, x=x+0.01), align = FALSE, size=3) +
  #geom_text(data=t$data %>% filter(isTip==TRUE) %>% filter(label %in% Run), aes(label=label, x=x+0.01), size=3) +
  scale_shape_manual(values=c(21,23,24)) +
  guides(fill = guide_legend(override.aes = list(pch = 22))) +
  xlim(0,.1) +
  scale_fill_viridis_d(option="H") +
  theme(legend.position = "none") +
  geom_treescale()

u
```
```{r}
ind<-m58 %>% filter(Lineage=="IND")
tree<-read.tree("outputs/210/pruned.min4.phy.varsites.phy.contree")
t2<-root.phylo(tree,outgroup = ind$Run)
t3<-as.polytomy(t2, feature='node.label', fun=function(x) as.numeric(x) < 75)

t<-t3

t<-ggtree(t)

t$data$Bootstrap<-as.numeric(t$data$label)

d <- t$data
d <- d[!d$isTip,]
d$label <- as.numeric(d$label)
d <- d[d$label >= 90,]

e <- t$data
e <- e[!e$isTip,]
e$label <- as.numeric(e$label)
e <- e[e$label < 90,]
e <- e[e$label >= 75,]
```

```{r}
u<-t %<+% m58 + #bind_rows(m58, rm) +
  geom_point(data=e,  fill="gray50", cex=3, alpha=1, pch=22) +
  geom_point(data=d,  fill="black", cex=3, alpha=1, pch=22) +
  geom_tippoint(aes(x=x+0.002,fill=Region, shape=Lineage), cex=3) + 
  geom_tiplab(aes(label=Region, x=x+0.01), align = FALSE, size=3) +
  #geom_text(data=t$data %>% filter(isTip==TRUE) %>% filter(label %in% Run), aes(label=label, x=x+0.01), size=3) +
  scale_shape_manual(values=c(21,23,24)) +
  guides(fill = guide_legend(override.aes = list(pch = 22))) +
  xlim(0,.5) +
  scale_fill_viridis_d(option="H") +
  theme(legend.position = "none") +
  geom_treescale(x = 0)

u

ggsave("outputs/210/concatenated-tree-58inds.pdf", width=6, height=9)
```
Now, we can draw up cophylogeny plots. Here is a way with ggtree https://arftrhmn.net/how-to-make-cophylogeny/

```{r}
m8<-tree<-read.tree("data/mtdna/new-coi.afasta.contree")
m8<-midpoint.root(m8)
m8<-as.polytomy(m8, feature='node.label', fun=function(x) as.numeric(x) < 75)

m9<-read.tree("outputs/210/pruned.min4.phy.varsites.phy.contree")
m9<-root.phylo(m9,outgroup = ind$Run)
m9<-as.polytomy(m9, feature='node.label', fun=function(x) as.numeric(x) < 75)

ggtree(m9) + geom_nodelab(aes(label=node))

t8<-ggtree(m8) %<+% m58 +
  geom_tippoint(aes(fill=Region, shape=Lineage), cex=3) + 
  scale_fill_viridis_d(option="H") +
  theme(legend.position = "none") +
  scale_shape_manual(values=c(21,23,24)) 

t9<-ggtree(m9) %>% ggtree::rotate(68)

d8 <- t8$data
d9 <- t9$data

d8$tree <-'t8'
d9$tree <-'t9'

d9$x <- max(d9$x) - d9$x + max(d8$x) +  max(d8$x)*5
d10<-d9 %>% left_join(m58, by=c("label"="Run")) %>% filter(isTip==TRUE)

pp <- t8 + geom_tree(data=d9)

#set up df for lines
dd <- bind_rows(d8, d9) %>% 
  filter(isTip == TRUE)
dd1 <- as_tibble(dd)

pp + geom_line(data=dd1, aes(x=x, y=y, group=label), color="grey50") +
  geom_point(data=d10,
             aes(x=x, y=y, fill=Region, shape=Lineage), cex=3)+
    scale_fill_viridis_d(option="H") +
  theme(legend.position = "none") +
  scale_shape_manual(values=c(21,23,24))
  #ggtitle("mtDNA to SNPs comparison")

#  geom_treescale()
ggsave("outputs/210/tanglegram.jpeg")
```

## Examining Philippines, Indonesia-K
```{r}
m38<-m2 %>% filter(!Region %in% c("Vietnam","Cambodia","Indonesia-SJ","Indonesia-SU","Thailand") )
write_csv(m38, file="meta/38.csv")
write_tsv(m38 %>% select(Downsample), file="bamlists/38-downsample.bamlist", col_names = FALSE)
write_tsv(m38 %>% select(Path), file="bamlists/38.bamlist", col_names = FALSE)
write_tsv(m38 %>% select(Run), file="bamlists/38.names", col_names = FALSE)

```


```{sh, eval=FALSE}
srun -t 72:00:00 -p high --mem=32G --nodes=1 --ntasks-per-node=1 --cpus-per-task=12 $HOME/angsd/angsd -nthreads 24 \
-minInd 35 -bam bamlists/38.bamlist -ref genome/GCF_001640805.2_TLL_Latcal_v3_genomic.fna \
-rf genome/lates-lgs.txt -out outputs/210/snps-wgs  \
-minMaf 0.05 -minMapQ 20 -minQ 20 -GL 1 -doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 \
-doGeno 2 -doPost 1 -postCutoff 0.9 -doPlink 2  > outputs/210/snps-wgs.out 2> outputs/210/snps-wgs.err &

srun -p high -t 16:00:00 --mem=32G --nodes=1 $HOME/angsd/angsd -P 12  \
-bam bamlists/38-downsample.bamlist -rf genome/lates-lgs.txt \
-anc  genome/GCF_001640805.2_TLL_Latcal_v3_genomic.fna \
-minInd 34 -minMapQ 20 -minQ 20 -GL 1 -doGLF 2 \
-doMajorMinor 1 -doPost 1 -doMaf 1 -SNP_pval 1e-6 \
-minMaf 0.05 \
-out outputs/210/38-gls-90 > outputs/210/38-gls-90.out 2> outputs/210/38-gls-90.err &

srun -p high -t 04:00:00 --mem=32G --nodes=1 $HOME/angsd/misc/NGSadmix -P 12 -likes outputs/210/38-gls-90.beagle.gz -K 2 -o outputs/210/38-K2-gls &
srun -p high -t 05:00:00 --mem=32G --nodes=1 $HOME/angsd/misc/NGSadmix -P 12 -likes outputs/210/38-gls-90.beagle.gz -K 3 -o outputs/210/38-K3-gls &
srun -p high -t 05:00:00 --mem=32G --nodes=1 $HOME/angsd/misc/NGSadmix -P 12 -likes outputs/210/38-gls-90.beagle.gz -K 4 -o outputs/210/38-K4-gls &
srun -p high -t 05:00:00 --mem=32G --nodes=1 $HOME/angsd/misc/NGSadmix -P 12 -likes outputs/210/38-gls-90.beagle.gz -K 5 -o outputs/210/38-K5-gls &
```

4593584 GLS

2335358 snps
```{sh, eval=FALSE}
plink --tped snps-wgs.tped --tfam snps-wgs.tfam  --out plink-binary --recode --allow-extra-chr --noweb
plink --ped plink-binary.ped --map plink-binary.map --recode vcf --allow-extra-chr -out plink
bgzip plink.vcf 
tabix plink.vcf.gz

#renaming vcf
bcftools reheader --samples bamlists/38.names -o outputs/210/renamed.vcf.gz outputs/210/plink.vcf.gz

bcftools +prune -l 0.30 -w 10000 outputs/210/renamed.vcf.gz > outputs/210/38-pruned.vcf

## locally
 ~/github/mccloud-rrt/vcf2phylip.py -i 38-pruned.vcf 

```

6727 variants after pruning -l 0.2, using l-.3 for 20008

```{r}
dat<-read.dna(file="outputs/210/38-pruned.min4.phy")
write.nexus.data(dat, file="outputs/210/38-pruned.nex")

```

```{sh, eval=FALSE}
iqtree -s 38-pruned.min4.phy -st DNA -m GTR+ASC -bb 1000 --redo
iqtree -s 38-pruned.min4.phy.varsites.phy -T AUTO -st DNA -m MFP+ASC -bb 10000 --redo
```
1474 sites variable according to iqtree with -l 0.2 6339 with -l 0.3

```{r}
net38<-read.nexus.networx("outputs/210/38-pruned-network.nex")
```


```{r}
g<-ggsplitnet(net38)  
g$data<-left_join(g$data, m2, by=c("label"="Run")) 

g + 
  geom_tippoint(aes(shape=Lineage, fill=Region), cex=4, alpha=1.00) +
  scale_shape_manual(values = c(21,23,24)) +
  scale_fill_viridis_d(option="H") +
  guides(fill = guide_legend(override.aes = list(pch = 22))) 

ggsave("outputs/210/wgs-38-network.jpeg")

```


```{r}
tree<-read.tree("outputs/210/38-pruned.min4.phy.varsites.phy.contree")
t2<-tree
t3<-as.polytomy(t2, feature='node.label', fun=function(x) as.numeric(x) < 75)
t3<-midpoint.root(t3)

t<-t3

t<-ggtree(t)

t$data$Bootstrap<-as.numeric(t$data$label)

d <- t$data
d <- d[!d$isTip,]
d$label <- as.numeric(d$label)
d <- d[d$label >= 90,]

e <- t$data
e <- e[!e$isTip,]
e$label <- as.numeric(e$label)
e <- e[e$label < 90,]
e <- e[e$label >= 75,]
```

```{r}
u<-t %<+% m58 + #bind_rows(m58, rm) +
  geom_point(data=e,  fill="gray50", cex=3, alpha=1, pch=22) +
  geom_point(data=d,  fill="black", cex=3, alpha=1, pch=22) +
  geom_tippoint(aes(x=x+0.002,fill=Region, shape=Lineage), cex=3) + 
  geom_tiplab(aes(label=Region, x=x+0.01), align = FALSE, size=3) +
  #geom_text(data=t$data %>% filter(isTip==TRUE) %>% filter(label %in% Run), aes(label=label, x=x+0.01), size=3) +
  scale_shape_manual(values=c(21,23,24)) +
  guides(fill = guide_legend(override.aes = list(pch = 22))) +
  xlim(0,.5) +
  scale_fill_viridis_d(option="H") +
  theme(legend.position = "none") +
  geom_treescale(x = 0)

u

ggsave("outputs/210/concatenated-tree.pdf", width=6, height=9)
```



Admixture   
```{r, echo=FALSE}
PlotAdmix<- function(file, meta) {

q<-read_delim(file, delim=" ", col_names=FALSE)
#Make generic colnames

nums<-1:length(colnames(q))
mynames<-paste0("Q",nums)

qs<-length(colnames(q))-1

colnames(q)<-mynames

#Last col empty
q<-q[1:length(colnames(q))-1]

#Bind met and arrange 
df<-bind_cols(q, meta) %>% arrange(Region) %>% mutate(Index=1:n())
df$Region<-factor(df$Region, levels=unique(df$Region))

rdf<-df %>% dplyr::select(Region, Index, colnames(q) ) %>% gather(key=Ancestry, value=Q, 3:(3+length(colnames(q))-1))

#Make names for structure-like plot
labels<-rdf %>% group_by(Region) %>% mutate(Start=min(Index), Stop=max(Index)) %>% 
  select(Region,Start,Stop) %>% unique() %>% 
  mutate(Position=round((Start+Stop)/2)) %>% ungroup() %>% unique()

#Plot
ggplot(rdf) + 
  geom_col(aes(x=Index,y=Q, fill=Ancestry), color="NA", size = 0, width = 1) +
  geom_segment(data=labels, x = labels$Start - 0.5, y=0, xend = labels$Start-0.5, yend=1, alpha=0.9, size=0.25) +
  geom_segment(data=labels, x = labels$Stop[length(labels$Stop)]  + 0.5, y=0, 
               xend= labels$Stop[length(labels$Stop)] + 0.5, yend=1,  alpha=0.9,
               size=0.25) +
  geom_segment(x=0+0.5, xend= labels$Stop[length(labels$Stop)]+0.5, y=1, yend=1, alpha=0.9, size=0.25) +
  geom_segment(x=0+0.5, xend= labels$Stop[length(labels$Stop)]+0.5, y=0, yend=0, alpha=0.9, size=0.25) +
  ylim(-0.1,1.01) +
  xlim(-0.1, labels$Stop[length(labels$Stop)]+1) +
  theme(panel.background = element_blank()) +
  xlab("") +
  theme(legend.position = "") +
  scale_x_continuous(breaks=labels$Position, labels=labels$Region) +
  theme(axis.text.x = element_text(angle=45, hjust=1)) +
  scale_fill_viridis_d(option="magma")

}
```

```{r}
PlotAdmix("outputs/210/38-K2-gls.qopt", m38)
```

```{r}
PlotAdmix("outputs/210/38-K3-gls.qopt", m38)
```


```{r}
PlotAdmix("outputs/210/38-K4-gls.qopt", m38)
```


```{r}
mydat <- import.snpR.data("outputs/210/38-pruned.vcf", sample.meta = m38 %>% select(Run,Region,Lineage))
mydat@sample.meta$Region<-factor(mydat@sample.meta$Region, levels=c("Northern Territory","Queensland","Papua New Guinea","Indonesia-K","Philippines","India Eastern Coast","India Western Coast"))
```

```{r}
plot_clusters(mydat, facets="Region",
              viridis.option = "H")
```


```{r}
plot_structure(mydat, facet = "Region", 
               facet.order = c("Northern Territory","Queensland","Papua New Guinea","Indonesia-K","Philippines","India Eastern Coast","India Western Coast"),
              admixture_path  = "/Users/mac/github/dist/admixture_macosx-1.3.0/admixture", k=2, qsort=FALSE, reps = 1)
```

```{r}
plot_structure(mydat, facet = "Region", 
               facet.order = c("Northern Territory","Queensland","Papua New Guinea","Indonesia-K","Philippines","India Eastern Coast","India Western Coast"),
              admixture_path  = "/Users/mac/github/dist/admixture_macosx-1.3.0/admixture", k=3, qsort=FALSE, reps = 1)
```

```{r}
plot_structure(mydat, facet = "Region", 
               facet.order = c("Northern Territory","Queensland","Papua New Guinea","Indonesia-K","Philippines","India Eastern Coast","India Western Coast"),
              admixture_path  = "/Users/mac/github/dist/admixture_macosx-1.3.0/admixture", k=4, qsort=FALSE, reps = 1)
```
```{sh, eval=FALSE}
#removing individuals with missing data
bcftools stats -s - pruned-03.vcf | grep -E ^PSC | cut -f3,14 > missing.dat
```
F_Missing < 0.1 doesn't removing any snps

```{r}
missing<-read_tsv(file="outputs/210/missing.datt", col_names = c("Run","Missing")) %>% mutate(Proportion=Missing/73546)
missing2<-missing %>% arrange(-Proportion) %>% filter(Proportion > 0.07)
missing2$Run
```

```{sh, eval=FALSE}
bcftools view -s ^SRR3165594,SRR3183255,SRR3165613,SRR3165612,SRR3183256,SRR3165631,SRR3165633,SRR3165620 -O z pruned-03.vcf > prune-03-filtered.vcf 
```
```{r}
mydat <- import.snpR.data("outputs/210/prune-03-filtered.vcf", sample.meta = m2 %>% select(Run,Region,Lineage) %>% filter(! Run %in% missing2$Run))
```


```{r}
plot_clusters(mydat, facets="Region",
              viridis.option = "H")
```


```{r}
plot_structure(mydat, facet = "Lineage", 
               facet.order = c("AUS+NG","SEA","IND"),
              admixture_path  = "/Users/mac/github/dist/admixture_macosx-1.3.0/admixture", k=2,
               reps = 1)
```

```{r}
plot_structure(mydat, facet = "Lineage", 
               facet.order = c("AUS+NG","SEA","IND"),
              admixture_path  = "/Users/mac/github/dist/admixture_macosx-1.3.0/admixture", k=3,
               reps = 1)
```

```{r}
plot_structure(mydat, facet = "Lineage", 
               facet.order = c("AUS+NG","SEA","IND"),
              admixture_path  = "/Users/mac/github/dist/admixture_macosx-1.3.0/admixture", k=4, 
              
               reps = 1)
```

```{r}
plot_structure(mydat, facet = "Region", 
               facet.order = c("Northern Territory","Queensland","Papua New Guinea",
               "Indonesia-K","Indonesia-SJ","Cambodia","Philippines",
               "Thailand","Vietnam","India Eastern Coast","India Western Coast"),
              admixture_path  = "/Users/mac/github/dist/admixture_macosx-1.3.0/admixture", k=3, 
              
               reps = 1)
```

```{r}
plot_structure(mydat, facet = "Region", 
               facet.order = c("Northern Territory","Queensland","Papua New Guinea",
               "Indonesia-K","Indonesia-SJ","Cambodia","Philippines",
               "Thailand","Vietnam","India Eastern Coast","India Western Coast"),
              admixture_path  = "/Users/mac/github/dist/admixture_macosx-1.3.0/admixture", k=4, 
              
               reps = 1)
```

```{r}
plot_structure(mydat, facet = "Region", 
               facet.order = c("Northern Territory","Queensland","Papua New Guinea",
               "Indonesia-K","Indonesia-SJ","Cambodia","Philippines",
               "Thailand","Vietnam","India Eastern Coast","India Western Coast"),
              admixture_path  = "/Users/mac/github/dist/admixture_macosx-1.3.0/admixture", k=5, 
              
               reps = 1)
```
```{r}
plot_structure(mydat, facet = "Region", 
               facet.order = c("Northern Territory","Queensland","Papua New Guinea",
               "Indonesia-K","Indonesia-SJ","Cambodia","Philippines",
               "Thailand","Vietnam","India Eastern Coast","India Western Coast"),
              admixture_path  = "/Users/mac/github/dist/admixture_macosx-1.3.0/admixture", k=6, 
              
               reps = 1)
```