---
title: "400-additional-data"
output: html_document
date: "2023-11-27"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(tidyverse)
library(ggtree)
```

Adding in three more samples.
SRS19173540, SRS19136325 from bangladesh in data/bangladesh

 srun -p high -t 12:00:00 --mem=24GB fastq-dump --outdir split --skip-technical --read-filter pass --dumpbase --split-3 --gzip --clip SRR26402930  
 
  srun -p high -t 12:00:00 --mem=24GB fastq-dump --outdir split --skip-technical --read-filter pass --dumpbase --split-3 --gzip --clip SRR26358744   
 
Lates japonicus, in data/japonicus
wget https://sra-pub-run-odp.s3.amazonaws.com/sra/DRR391968/DRR391968

(base) maccamp@farm:~/lates-wgs/data/japonicus$ srun -p high -t 12:00:00 --mem=24GB fastq-dump --outdir split --skip-technical --read-filter pass --dumpbase --split-3 --gzip --clip DRR391968     

## Need to align to reference and compute metrics. 

Also at some point retrieve mtDNA seqs.

can use doAlign-zipped.sh