---
title: "604.1-ld"
output: html_document
date: "2024-02-08"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```


```{r}
library(tidyverse)
library(ggrepel)
library(pcadapt)
library(adegenet)
library(vcfR)
library(snpR)
library(ggpubr)
```

in 604/vcf
gunzip -c NC_066852.1.vcf.gz | wc -l
  101136
gunzip -c NC_066852.1.vcf.gz | grep "#" > header.txt
gunzip -c NC_066852.1.vcf.gz | grep -v "#" | awk 'BEGIN{i=0}{i++;if (i%100==0) print}' > NC_066852.1-thinned.vcf
cat header.txt NC_066852.1-thinned.vcf > NC_066852.1-thinned.wheader.vcf
gunzip -c NC_066837.1.vcf.gz | grep -v "#" | awk 'BEGIN{i=0}{i++;if (i%100==0) print}' > NC_066837.1-thinned.vcf
cat header.txt NC_066837.1-thinned.vcf > NC_066837.1-thinned.wheader.vcf

gunzip -c NC_066835.1.vcf.gz | grep -v "#" | awk 'BEGIN{i=0}{i++;if (i%100==0) print}' > NC_066835.1-thinned.vcf
cat header.txt NC_066835.1-thinned.vcf > NC_066835.1-thinned.wheader.vcf


wc -l NC_066852.1-thinned.vcf 
2021 NC_066852.1-thinned.vcf
1010 at 100 
plink --vcf NC_066852.1-thinned.wheader.vcf --r2 inter-chr --ld-window-r2 0.3 --out NC_066852.1-thinned.ldf --allow-extra-chr --double-id
plink --vcf NC_066837.1-thinned.wheader.vcf --r2 inter-chr --ld-window-r2 0.3 --out NC_066837.1-thinned.ldf --allow-extra-chr --double-id
plink --vcf NC_066835.1-thinned.wheader.vcf --r2 inter-chr --ld-window-r2 0.3 --out NC_066835.1-thinned.ldf --allow-extra-chr --double-id


## High LD


```{r}
lc20<-read.delim("outputs/604/vcf/NC_066852.1-thinned.ldf.ld",sep="",stringsAsFactors=FALSE) %>% as_tibble() %>% arrange(R2) %>%
  filter(R2>.5)

ggplot(lc20) +
  geom_point(aes(x=BP_A, y=BP_B, color=R2), alpha=0.5) +
  scale_color_gradient(low="khaki1", high="red") + 
  theme_bw() +
  theme(panel.grid=element_blank()) +
  coord_equal()
```



```{r}
lc05<-read.delim("outputs/604/vcf/NC_066837.1-thinned.ldf.ld",sep="",stringsAsFactors=FALSE) %>% as_tibble() %>% arrange(R2) %>%
  filter(R2>.5)

ggplot(lc05) +
  geom_point(aes(x=BP_A, y=BP_B, color=R2), alpha=0.5) +
  scale_color_gradient(low="khaki1", high="red") + 
  theme_bw() +
  theme(panel.grid=element_blank()) +
  coord_equal()
```




```{r}
lc03<-read.delim("outputs/604/vcf/NC_066835.1-thinned.ldf.ld",sep="",stringsAsFactors=FALSE) %>% as_tibble() %>% arrange(R2) %>%
  filter(R2>.5)

ggplot(lc03) +
  geom_point(aes(x=BP_A, y=BP_B, color=R2), alpha=0.5) +
  scale_color_gradient(low="khaki1", high="red") + 
  theme_bw() +
  theme(panel.grid=element_blank()) +
  coord_equal()
```
