---
title: "902-copy-number-variation"
output: html_document
date: "2024-08-05"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(tidyverse)
```

Should be easily able to calculate depth (samtools depth -a ) and create a depth raster.

Queensland
India (east coast and west)
Indonesia (K, SU, SJ)

Need to normalize. Divide by average depth?

1 2 3 = 6/3=2, 1/2, 1, 3/2 = 3
1 1 1 = 3/3=1, 1/1 + 1/1 +1/1 = 3


```{r}
msub<-read_csv("~/github/lates-wgs/meta/58-Indo-split.csv") %>% 
  filter(Region %in% c("Queensland","India Eastern Coast","India Western Coast","Indonesia-K",
                       "Indonesia-SJ","Indonesia-SU"))

msub %>% select(Run) %>% write_tsv("outputs/902/runs.tsv", col_names = FALSE)
```

```{r}
commands<-msub %>% mutate(Command=paste0("samtools depth -a ", Path, " | awk '{print $1, $2, $3, $3/",Coverage, ", ",Coverage,","," \042",Run, "\042}' ", " | grep NC ",  ">", " outputs/902/",Run,".coverage"))

commands %>% select(Command) %>% write_tsv("902-coverage.sh", col_names = FALSE)
```

Removing double quotes after the fact.

module load parallel
 
srun -p high --time 2:00:00 --nodes=1 --ntasks-per-node=1 --cpus-per-task=18 parallel -j 18 < 902-coverage.sh

Combine into a tidy format.

Chrom Pos Depth Individual
~ X Z Y

These are so big, perhaps I can write a script to visualize them on the cluster.  I can also reduce the size with a sliding window: https://shearnrylan.wordpress.com/2016/05/30/sliding-window-in-awk/

awk -v OFS="\t" 'BEGIN{window=100;slide=50} { if(NR==1) print "coord",$3 } {mod=NR%window; if(NR<=window){count++}else{sum-=array[mod];sum+=$3;array[mod]=$3;} (NR%slide)==0{print NR,sum/count/$5}' test1000

Should produce the same numbers for depth

awk -v OFS="\t" 'BEGIN{window=100;slide=50} { if(NR==1) print "coord",$3,$4 } {mod=NR%window; if(NR<=window){count++}else{sum-=array[mod];sum2-=array2[mod]}sum+=$3;sum2+=$4;array[mod]=$3;array2[mod]=$4;} (NR%slide)==0{print $1,$6,NR,sum/count/$5,sum2/count}' test1000


Printing out: Individual, Chrom,Window, average depth over window, normalized depth
awk -v OFS="\t" 'BEGIN{window=100;slide=50} { if(NR==1) print "coord",$3,$3 } {mod=NR%window; if(NR<=window){count++}else{sum-=array[mod];sum2-=array2[mod]}sum+=$3;sum2+=$3;array[mod]=$3;array2[mod]=$3;} (NR%slide)==0{print $6,$1,NR,sum/count,sum2/count/$5}' test1000

probably need to do this per chrom for each individual, then combine.

```{sh, eval=FALSE}
grep NC_066833.1 SRR3165594.coverage | awk -v OFS="\t" 'BEGIN{window=10000;slide=5000} { if(NR==1) print "Individual","Chrom","Window","Avg","DepthNorm" } {mod=NR%window; if(NR<=window){count++}else{sum-=array[mod];sum2-=array2[mod]}sum+=$3;sum2+=$3;array[mod]=$3;array2[mod]=$3;} (NR%slide)==0{print $6,$1,NR,sum/count,sum2/count/$5}' > NC_066833.1-SRR3165594.window

grep NC_066833.1 SRR3165595.coverage | awk -v OFS="\t" 'BEGIN{window=10000;slide=5000} { if(NR==1) print "Individual","Chrom","Window","Avg","DepthNorm" } {mod=NR%window; if(NR<=window){count++}else{sum-=array[mod];sum2-=array2[mod]}sum+=$3;sum2+=$3;array[mod]=$3;array2[mod]=$3;} (NR%slide)==0{print $6,$1,NR,sum/count,sum2/count/$5}' > NC_066833.1-SRR3165595.window

grep NC_066833.1 SRR3165629.coverage | awk -v OFS="\t" 'BEGIN{window=10000;slide=5000} { if(NR==1) print "Individual","Chrom","Window","Avg","DepthNorm" } {mod=NR%window; if(NR<=window){count++}else{sum-=array[mod];sum2-=array2[mod]}sum+=$3;sum2+=$3;array[mod]=$3;array2[mod]=$3;} (NR%slide)==0{print $6,$1,NR,sum/count,sum2/count/$5}' > NC_066833.1-SRR3165629.window

grep NC_066833.1 SRR3165630.coverage | awk -v OFS="\t" 'BEGIN{window=10000;slide=5000} { if(NR==1) print "Individual","Chrom","Window","Avg","DepthNorm" } {mod=NR%window; if(NR<=window){count++}else{sum-=array[mod];sum2-=array2[mod]}sum+=$3;sum2+=$3;array[mod]=$3;array2[mod]=$3;} (NR%slide)==0{print $6,$1,NR,sum/count,sum2/count/$5}' > NC_066833.1-SRR3165630.window
```




```{r}
files<-list.files(path="outputs/902/", pattern="NC_066833.1*", full.names = TRUE)

depth<-lapply(files, read_tsv)
depth<-bind_rows(depth) %>% left_join(msub, by=c("Individual"="Run"))
```

```{r}
ggplot(depth) + 
  geom_raster(aes(x=Window, y=Individual, fill=DepthNorm)) +
  scale_fill_viridis_c(option="plasma") + 
  facet_grid(Region~Chrom, scales="free_y",) +
  theme_bw()
  
```



Calculate sliding windows all chroms

```{sh, eval=FALSE}
cat ../../meta/lates-lgs.txt | while read line; do cat runs.tsv | while read run; do echo grep $line $run.coverage; paste command ; echo $line-$run.window;
done; done;



```

maybe paste from file?