---
title: "range-map"
output: html_document
date: "2023-08-27"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Using aquamaps data 
Mapping parameters for Lates calcarifer (Barramundi)

"Cite AquaMaps itself as: Kaschner, K., Kesner-Reyes, K., Garilao, C., Segschneider, J., Rius-Barile, J. Rees, T., & Froese, R. (2019, October). AquaMaps: Predicted range maps for aquatic species. Retrieved from https://www.aquamaps.org."


Mapping parameters for Lates calcarifer (Barramundi)

"Cite AquaMaps itself as: Kaschner, K., Kesner-Reyes, K., Garilao, C., Segschneider, J., Rius-Barile, J. Rees, T., & Froese, R. (2019, October). AquaMaps: Predicted range maps for aquatic species. Retrieved from https://www.aquamaps.org."

Map type: Computer-generated,
Map Option: In FAO and Bounding Box
FAOAreas: 51 |  57 |  61 |  71,
Bounding Box (NSWE): ,49,-26,56,155

Pelagic: False,
Layer used to generate probabilities: Surface,

Species Envelope (HSPEN):
 ,Used,Min,Pref Min (10th),Pref Max (90th),Max
Depth (m),1,10,13,26,40
Temperature (∞C),1,18.4,24.95,28.89,33.09
Salinity (psu),1,14.69,30.58,35.35,36.79
Primary Production (mgC∑m-3∑day-1) ,1,1.08,4.88,23.5,211.48
Sea Ice Concentration (0-1 fraction),1,-1,0,0,0
Dissolved Bottom Oxygen (mmol∑m-3),0,26.46,175.51,212.39,285.31
Distance to Land (km),0,0,3,97,620
 

Map data (HSPEC) for predicted occurrences (n = 3456): 

"To get individual probabilities (i.e. Depth, Temperature, Salinity, Primary Production, Sea Ice Concentration, Distance to Land):"
1. Click on the Create-Your-Own-Map at the bottom left part of the species map page.
2. Click on the Regenerate Map Data and View Map button then click OK.
3. In the resulting User-Specified Map for the species click on the Download data (as csv) link.
4. Select HSPEC then Submit.

Occurrence cells used for creating environmental envelope (n = 231)   
Plot type locality
Plot sample locations

```{r}
library(tidyverse)
library(ggmap)
require(maps)
library(ggrepel)
```

```{r}
range<-read_csv("outputs/range-map/1693178727.csv")
range$`Overall Probability`<-as.numeric(range$`Overall Probability`)
range
```


```{r}
ggplot() +
geom_raster(data=range, aes(x=`Center Long`, y=`Center Lat`, fill=`Overall Probability`),alpha=0.75) +
  scale_fill_gradient(low="yellow", high="red")
```


```{r}

world <- borders("world", colour="black", fill="black",
                 xlim=c(-180,180), ylim=c(-90,90))# create a layer of borders
data<-as_tibble(world$data)
map<-ggplot(data)+geom_polygon(aes(x=long,y=lat,group=group), fill="burlywood3", 
                              color="burlywood3",size=0.2)+
  coord_fixed(1.3)+
  theme(axis.title.x=element_blank(), axis.text.x=element_blank(), 
        axis.ticks.x=element_blank())+
  theme(axis.title.y=element_blank(), axis.text.y=element_blank(), 
        axis.ticks.y=element_blank())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background =  element_rect(fill="cornflowerblue"))

mp1 <- fortify(map(fill=TRUE, plot=FALSE))
mp2 <- mp1
mp2$long <- mp2$long + 360
mp2$group <- mp2$group + max(mp2$group) + 1
mp <- rbind(mp1, mp2)
```


```{r}
map2<-ggplot() + 
  geom_polygon(data=mp,aes(x=long,y=lat,group=group), fill="grey", 
               color="black",size=0.2)+
  coord_fixed(1.3)+
  theme_bw() +
   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background =  element_rect(fill="white"))+
  coord_fixed(ratio=1.3, xlim = c(-0, 360), ylim=c(-90,90))
map2
```
theme(axis.title.x=element_blank(), axis.text.x=element_blank(), 
        axis.ticks.x=element_blank())+
  theme(axis.title.y=element_blank(), axis.text.y=element_blank(), 
        axis.ticks.y=element_blank())+

```{r}
long<-c(79.3,127.04,146.64,140.93,104.87,103.64,101.15,130.83,145.78,80,73.83)
lat<-c(10.4,-13.38,-18.41,-9.42,-1.66,3.35,12.62,-12.52,-16.92,15,15.26)
text<-c("Type Location", "AUW","AUE","PNG","INA","MAL","THA","NT","QLD","INDE","INDW")
color<-c("purple","blue","blue","blue","blue","blue","blue","green","green","green","green")
shape<-c(22,21,21,21,24,24,24,21,21,23,23)
ddf<-cbind(long,lat,text,color,shape) %>% as_tibble()
ddf$long<-as.numeric(ddf$long)
ddf$lat<-as.numeric(ddf$lat)
ddf$shape<-as.numeric(ddf$shape)
ddf

loc<-ddf[1,]
write_tsv(ddf, file="outputs/range-map/points.tsv")
```
```{r}
points<-read_tsv("outputs/range-map/points-edited.tsv")
points$Lineage<-factor(points$Lineage, levels=c("AUS+NG","SEA","IND"))

ggplot() + geom_point(data=points, aes(x=long, y=lat, fill=DataType, shape=Lineage), cex=2) +
  scale_shape_manual(values=c(21,24,23)) +
  scale_fill_viridis_d() +
  guides(fill = guide_legend(override.aes = list(pch = 22))) 


```

```{r}
points2<-points %>% filter(DataType=="WGS")
map2 +
  geom_raster(data=range, aes(x=`Center Long`, y=`Center Lat`, fill=`Overall Probability`),alpha=0.75) +
  scale_fill_gradient(low="yellow", high="red")+
  geom_point(data=points2, aes(x=long, y=lat), fill=points2$color, shape=points2$shape, cex=2) +
  geom_point(data=loc, aes(x=long, y=lat), fill=loc$color, shape=loc$shape, cex=2) +
  geom_text_repel(data=loc, aes(x=long, y=lat, label=text), size=2, fontface="bold") +
  coord_cartesian(xlim =c(30,180), ylim=c(-45,45)) +
  xlab("\nLongitude") +
  ylab("Latitude\n") +
  theme(axis.title = element_text(size=18, face="bold")) 
ggsave("outputs/range-map/range-map.jpeg")
```
